---
title: "behavioral analysis"
author: "Christopher"
date: "30 7 2024"
output:
  html_document:
    code_folding: hide
    toc: true
    toc_float: true
    toc_depth: 4
    theme: flatly
---



```{r load_package, message = FALSE, warning = FALSE}
library(lme4)
library(readxl)
library(tidyverse)
library(data.table)
library(tidyverse)
library(afex)
library(broom)
library(apa)
library(kableExtra)
library(lmerTest)
library(pbkrtest)
library(effects)
library(visreg)
library(sjPlot)
library(broom.mixed)
library(pander)
library(mediation)
library(multcomp)
library(multcompView)
library(magrittr)
library(multipanelfigure)
library(ggbeeswarm)
library(lsmeans)
library(BayesFactor)
library(ggpubr)
library(gpairs)
library(DescTools)
library(cowplot)
library(ggpol)
library(psych)

source('C:/Users/psy05cvd/Dropbox/work/R-statistics/general_functions/RainCloudPlots/tutorial_R/R_rainclouds.R')





# broad cluster
# CSD based normalized to pre-cue baseline in %
# 
DATAPath1 = "data_in/behavior_events.csv"
DATAPath2 = "data_in/behavior_FAs.csv"





options(scipen=1, digits=5)
```
<style type="text/css">
.main-container {
  max-width: 1800px !important;
  margin-left: auto;
  margin-right: auto;
}
</style>


## Prepare data  
<br>  

1.  Read in data: 
    + `r DATAPath1`
    + `r DATAPath1`
    
<br>  

```{r load_data,results = "hide", fig.show = "hide", warning = FALSE}
# read in data
DataIn1 <- read_csv(DATAPath1)
DataIn2 <- read_csv(DATAPath2)
head(DataIn1)
str(DataIn1)
head(DataIn2)
str(DataIn2)

```



1.  Prepare new dataset(s)...
<br>  

```{r prepare_data1, results = "hide", fig.show = "hide", warning = FALSE}
DATA_Trials <- DataIn1%>%
  filter(eventtype=="target")


```

## Illustrate behavioral data

<br>  

```{r plot_data_avg, results = "hide",  fig.height=6, fig.width=7, warning = FALSE}

dat2plot <- DATA_Trials %>%
  group_by(participant, colorlum)%>%
  summarise(
    RT_Mean=mean(RT,na.rm=TRUE),
    RT_STD=sd(RT,na.rm=TRUE),
    Hitrate=(sum(response=='hit')/n())*100,
    Hitrate_adj1 = ifelse((sum(response=='hit')/n())>0,
                         min(c(sum(response=='hit')/n(), 1-(.5/n()))),
                         .5/n()), # according to Stanislaw H, Todorov N, Behav Res Meth (1999) 31, 137-149, "1/2N rule" or
    Hitrate_adj2 = (sum(response=='hit')+0.5)/(n()+1)) # loglinear approach (Hautus, 1995)
dat2plot1a = DataIn1%>%
  filter(eventtype=="distractor") %>%
  group_by(participant, colorlum)%>%
  summarise(
    FArate=(sum(response=='FA_proper')/n())*100,
    FArate_adj1 = ifelse((sum(response=='FA_proper')/n())>0,
                         min(c(sum(response=='FA_proper')/n(), 1-(.5/n()))),
                         .5/n()), # according to Stanislaw H, Todorov N, Behav Res Meth (1999) 31, 137-149, "1/2N rule" or
    FArate_adj2 = (sum(response=='FA_proper')+0.5)/(n()+1)) # loglinear approach (Hautus, 1995))
dat2plot <- merge(dat2plot,dat2plot1a) %>% # adjust for HR and FR of 0 or 1
  mutate(
    d_prime = qnorm(Hitrate_adj1)-qnorm(FArate_adj1),
    c = -0.5*(qnorm(Hitrate_adj1)+qnorm(FArate_adj1))
  )


dat2plot2 <- DataIn2 %>%
  mutate(`FA_all`= FA + `FA_proper`)%>%
  # dplyr::select(-FA)%>%
  dplyr::select(-FA_all)%>%
  pivot_longer(c(-subject ),names_to = "FA_type", values_to = "number")%>%
  filter(FA_type=='FA_proper' | FA_type=='FA')

theme_set(theme_bw())
plot1 <- ggplot(dat2plot, aes(x = 1, y = RT_Mean)) +
  # geom_hline(yintercept=0, show.legend = FALSE) +
  geom_beeswarm(cex=4.5, size = 5,alpha=0.4)+
  stat_summary(fun.y=mean, aes(ymin=..y.., ymax=..y..), geom='errorbar', width=0.9, size=1.5) +
  # scale_fill_manual("attended color", values=c("darkcyan", "darkgreen", "darkorange")) +
  # scale_color_manual("attended color", values=c("darkcyan", "darkgreen", "darkorange")) +
  ylab(expression(paste("reaction time in ms")))+
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())

plot2 <- ggplot(dat2plot, aes(x = 1, y = Hitrate)) +
  # geom_hline(yintercept=0, show.legend = FALSE) +
  geom_beeswarm(cex=4.5, size = 5,alpha=0.4)+
  stat_summary(fun.y=mean, aes(ymin=..y.., ymax=..y..), geom='errorbar', width=0.9, size=1.5) +
  # scale_fill_manual("attended color", values=c("darkcyan", "darkgreen", "darkorange")) +
  # scale_color_manual("attended color", values=c("darkcyan", "darkgreen", "darkorange"))
  ylab(expression(paste("hit rate in %")))+
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())

plot3 <- ggplot(dat2plot2, aes(x = FA_type, y = number, color = FA_type)) +
  # geom_hline(yintercept=0, show.legend = FALSE) +
  geom_beeswarm(cex=3.5, size = 5,alpha=0.4)+
  stat_summary(fun.y=mean, aes(ymin=..y.., ymax=..y..), geom='errorbar', width=0.9, size=1.5) +
  scale_fill_manual("FA type", values=c("grey40", "black"),labels = c("to other","to distractor")) +
  scale_color_manual("FA type", values=c("grey40", "black"),labels = c("to other","to distractor")) +
  ylab(expression(paste("number of False Alarms")))+
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())

plot4 <- ggplot(dat2plot, aes(x = 1, y = d_prime)) +
  # geom_hline(yintercept=0, show.legend = FALSE) +
  geom_beeswarm(cex=4.5, size = 5,alpha=0.4)+
  stat_summary(fun.y=mean, aes(ymin=..y.., ymax=..y..), geom='errorbar', width=0.9, size=1.5) +
  # scale_fill_manual("attended color", values=c("darkcyan", "darkgreen", "darkorange")) +
  # scale_color_manual("attended color", values=c("darkcyan", "darkgreen", "darkorange"))
  ylab(expression(paste("dprime")))+
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())


# cowplot::plot_grid(plot1, plot2, plot3, ncol = 3,labels = "AUTO")
plotttitle <- ggdraw() + draw_label("behavioral measures", fontface='bold')
plotplots <- ggarrange(plot1, plot2, plot3, plot4, ncol = 4, align = "h", widths=c(2,2,5,2))
ggarrange(plotttitle, plotplots, nrow = 2, heights=c(0.2, 1))







## for publication
theme_set(theme_bw())
plot1 <- ggplot(dat2plot, aes(x = colorlum, y = RT_Mean, color =colorlum,)) +
  # geom_hline(yintercept=0, show.legend = FALSE) +
  geom_beeswarm(cex=4.5, size = 5,alpha=0.4)+
  stat_summary(fun.y=mean, aes(ymin=..y.., ymax=..y..), geom='errorbar', width=0.9, size=1.5) +
  scale_fill_brewer(palette = "Dark2")+
  scale_color_brewer(palette = "Dark2")+
  # scale_fill_manual("attended color", values=c("darkcyan", "darkgreen", "darkorange")) +
  # scale_color_manual("attended color", values=c("darkcyan", "darkgreen", "darkorange")) +
  ylab(expression(paste("reaction time in ms")))+
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())+
  scale_y_continuous(limits=c(400, 775))

plot1b <- ggplot(dat2plot, aes(x = 1, y = RT_Mean, color =colorlum, fill = colorlum)) +
  geom_flat_violin(position = position_nudge(x = .1, y = 0), adjust = 1.0, trim = FALSE, alpha = 0.8)+
  # scale_fill_manual(values=c("grey40"))+
  scale_fill_brewer(palette = "Dark2")+
  # scale_color_manual(values=c("grey40"))+
  scale_color_brewer(palette = "Dark2")+
  theme(axis.title.y=element_blank(),
         axis.text.y=element_blank(),
         axis.ticks.y=element_blank())+
  theme(axis.title.x=element_blank(),
         axis.text.x=element_blank(),
         axis.ticks.x=element_blank())+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+
  scale_y_continuous(limits=c(400, 775))

plot2 <- ggplot(dat2plot, aes(x = colorlum, y = Hitrate, color =colorlum)) +
  # geom_hline(yintercept=0, show.legend = FALSE) +
  geom_beeswarm(cex=4.5, size = 5,alpha=0.4)+
  stat_summary(fun.y=mean, aes(ymin=..y.., ymax=..y..), geom='errorbar', width=0.9, size=1.5) +
  scale_fill_brewer(palette = "Dark2")+
  scale_color_brewer(palette = "Dark2")+
    # scale_fill_manual("attended color", values=c("darkcyan", "darkgreen", "darkorange")) +
  # scale_color_manual("attended color", values=c("darkcyan", "darkgreen", "darkorange"))
  ylab(expression(paste("hit rate in %")))+
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())+
  scale_y_continuous(limits=c(50, 100))

plot2b <- ggplot(dat2plot, aes(x = 1, y = Hitrate,  color =colorlum, fill = colorlum)) +
  geom_flat_violin(position = position_nudge(x = .1, y = 0), adjust = 1.0, trim = FALSE, alpha = 0.8)+
  # scale_fill_manual(values=c("grey40"))+
  scale_fill_brewer(palette = "Dark2")+
  # scale_color_manual(values=c("grey40"))+
  scale_color_brewer(palette = "Dark2")+
  theme(axis.title.y=element_blank(),
         axis.text.y=element_blank(),
         axis.ticks.y=element_blank())+
  theme(axis.title.x=element_blank(),
         axis.text.x=element_blank(),
         axis.ticks.x=element_blank())+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+
  scale_y_continuous(limits=c(50, 100))

  

# cowplot::plot_grid(plot1, plot2, plot3, ncol = 3,labels = "AUTO")
plotttitle <- ggdraw() + draw_label("behavioral measures", fontface='bold')
plotplots <- ggarrange(plot1, plot1b,plot2, plot2b, ncol = 4,common.legend = TRUE,align = "h", widths=c(3,2,3,2))

savefig <- multi_panel_figure(columns = 1, rows = 1, panel_label_type = "none", width = 5, height = 6, unit = "in")
saveplot <- ggarrange(plotttitle, plotplots, nrow = 2, heights=c(0.2, 1))

savefig %<>%
  fill_panel(saveplot, column = 1, row = 1)
savefig
# save_multi_panel_figure(savefig, "hits_reactiontimes.eps")


## for publication
theme_set(theme_bw())
plot1 <- ggplot(dat2plot, aes(x = colorlum, y = RT_Mean, color =colorlum)) +
  # geom_hline(yintercept=0, show.legend = FALSE) +
  geom_beeswarm(cex=4.5, size = 5,alpha=0.4)+
  stat_summary(fun.y=mean, aes(ymin=..y.., ymax=..y..), geom='errorbar', width=0.9, size=1.5) +
  scale_fill_brewer(palette = "Dark2")+
  scale_color_brewer(palette = "Dark2")+
  # scale_fill_manual("attended color", values=c("darkcyan", "darkgreen", "darkorange")) +
  # scale_color_manual("attended color", values=c("darkcyan", "darkgreen", "darkorange")) +
  ylab(expression(paste("reaction time in ms")))+
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())+
  scale_y_continuous(limits=c(400, 775))

plot1b <- ggplot(dat2plot, aes(x = 1, y = RT_Mean, color =colorlum, fill = colorlum)) +
  geom_flat_violin(position = position_nudge(x = .1, y = 0), adjust = 1.0, trim = FALSE, alpha = 0.8)+
  # scale_fill_manual(values=c("grey40"))+
  scale_fill_brewer(palette = "Dark2")+
  # scale_color_manual(values=c("grey40"))+
  scale_color_brewer(palette = "Dark2")+
  theme(axis.title.y=element_blank(),
         axis.text.y=element_blank(),
         axis.ticks.y=element_blank())+
  theme(axis.title.x=element_blank(),
         axis.text.x=element_blank(),
         axis.ticks.x=element_blank())+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+
  scale_y_continuous(limits=c(400, 775))

plot2 <- ggplot(dat2plot, aes(x = colorlum, y = d_prime, color =colorlum)) +
  # geom_hline(yintercept=0, show.legend = FALSE) +
  geom_beeswarm(cex=4.5, size = 5,alpha=0.4)+
  stat_summary(fun.y=mean, aes(ymin=..y.., ymax=..y..), geom='errorbar', width=0.9, size=1.5) +
  scale_fill_brewer(palette = "Dark2")+
  scale_color_brewer(palette = "Dark2")+
  # scale_fill_manual("attended color", values=c("darkcyan", "darkgreen", "darkorange")) +
  # scale_color_manual("attended color", values=c("darkcyan", "darkgreen", "darkorange"))
  ylab(expression(paste("dprime")))+
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())+
  scale_y_continuous(limits=c(0.8, 3.8))

plot2b <- ggplot(dat2plot, aes(x = 1, y = d_prime, color =colorlum, fill = colorlum)) +
  geom_flat_violin(position = position_nudge(x = .1, y = 0), adjust = 1.0, trim = FALSE, alpha = 0.8)+
  # scale_fill_manual(values=c("grey40"))+
  scale_fill_brewer(palette = "Dark2")+
  # scale_color_manual(values=c("grey40"))+
  scale_color_brewer(palette = "Dark2")+
  theme(axis.title.y=element_blank(),
         axis.text.y=element_blank(),
         axis.ticks.y=element_blank())+
  theme(axis.title.x=element_blank(),
         axis.text.x=element_blank(),
         axis.ticks.x=element_blank())+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+
  scale_y_continuous(limits=c(0.8, 3.8))

  

# cowplot::plot_grid(plot1, plot2, plot3, ncol = 3,labels = "AUTO")
plotttitle <- ggdraw() + draw_label("behavioral measures", fontface='bold')
plotplots <- ggarrange(plot1, plot1b,plot2, plot2b, ncol = 4,common.legend = TRUE,align = "h", widths=c(3,2,3,2))

savefig <- multi_panel_figure(columns = 1, rows = 1, panel_label_type = "none", width = 5, height = 6, unit = "in")
saveplot <- ggarrange(plotttitle, plotplots, nrow = 2, heights=c(0.2, 1))

savefig %<>%
  fill_panel(saveplot, column = 1, row = 1)
savefig
# save_multi_panel_figure(savefig, "dprime_reactiontimes.eps")
  

```


## Display behavioral data numerically

<br>  

```{r disp_data_avg, warning = FALSE}
dat2plot <- DATA_Trials %>%
  group_by(colorlum, participant )%>%
  summarise(
    RT_Mean=mean(RT,na.rm=TRUE),
    RT_STD=sd(RT,na.rm=TRUE),
    Hitrate=(sum(response=='hit')/n())*100,
    Hitrate_adj1 = ifelse((sum(response=='hit')/n())>0,
                         min(c(sum(response=='hit')/n(), 1-(.5/n()))),
                         .5/n()), # according to Stanislaw H, Todorov N, Behav Res Meth (1999) 31, 137-149, "1/2N rule" or
    Hitrate_adj2 = (sum(response=='hit')+0.5)/(n()+1)) # loglinear approach (Hautus, 1995)

dat2plot1a = DataIn1%>%
  filter(eventtype=="distractor") %>%
  group_by(colorlum, participant)%>%
  summarise(
    FArate=(sum(response=='FA_proper')/n())*100,
    FArate_adj1 = ifelse((sum(response=='FA_proper')/n())>0,
                         min(c(sum(response=='FA_proper')/n(), 1-(.5/n()))),
                         .5/n()), # according to Stanislaw H, Todorov N, Behav Res Meth (1999) 31, 137-149, "1/2N rule" or
    FArate_adj2 = (sum(response=='FA_proper')+0.5)/(n()+1)) # loglinear approach (Hautus, 1995))

dat2plot <- merge(dat2plot,dat2plot1a) %>% # adjust for HR and FR of 0 or 1
  mutate(
    d_prime = qnorm(Hitrate_adj1)-qnorm(FArate_adj1),
    c = -0.5*(qnorm(Hitrate_adj1)+qnorm(FArate_adj1))
  )

dat2plot  %>%
  group_by(colorlum)%>%
  summarise(N = n(), mean_RT = mean(RT_Mean), std_RT = sd(RT_Mean), mean_Hitrate = mean(Hitrate), std_Hitrate = sd(Hitrate),
            mean_FArate = mean(FArate), std_FArate = sd(FArate), mean_dprime = mean(d_prime), std_dprime = sd(d_prime)) %>%
  kable(escape = F, digits = c(3,3,3,3,3,3,3,3,3,3), caption = c("descriptives of behavioral measures")) %>%
  kable_styling("striped", full_width = T, bootstrap_options = c("striped", "hover", "condensed", "responsive",font_size = 8))

```


## Correlation between behavioral data

<br>  

```{r corr1, results = "hide",  fig.height=3.5, fig.width=3, warning = FALSE}
# def.cormethod ="pearson"
def.cormethod ="spearman"
num.iter = 10000

dat2plot <- DATA_Trials %>%
  group_by(participant, colorlum)%>%
  summarise(
    RT_Mean=mean(RT,na.rm=TRUE),
    RT_STD=sd(RT,na.rm=TRUE),
    Hitrate=(sum(response=='hit')/n())*100,
    Hitrate_adj1 = ifelse((sum(response=='hit')/n())>0,
                          min(c(sum(response=='hit')/n(), 1-(.5/n()))),
                          .5/n()), # according to Stanislaw H, Todorov N, Behav Res Meth (1999) 31, 137-149, "1/2N rule" or
    Hitrate_adj2 = (sum(response=='hit')+0.5)/(n()+1)) # loglinear approach (Hautus, 1995)
dat2plot1a = DataIn1%>%
  filter(eventtype=="distractor") %>%
  group_by(participant, colorlum)%>%
  summarise(
    FArate=(sum(response=='FA_proper')/n())*100,
    FArate_adj1 = ifelse((sum(response=='FA_proper')/n())>0,
                         min(c(sum(response=='FA_proper')/n(), 1-(.5/n()))),
                         .5/n()), # according to Stanislaw H, Todorov N, Behav Res Meth (1999) 31, 137-149, "1/2N rule" or
    FArate_adj2 = (sum(response=='FA_proper')+0.5)/(n()+1)) # loglinear approach (Hautus, 1995))
dat2plot <- merge(dat2plot,dat2plot1a) %>% # adjust for HR and FR of 0 or 1
  mutate(
    d_prime = qnorm(Hitrate_adj1)-qnorm(FArate_adj1),
    c = -0.5*(qnorm(Hitrate_adj1)+qnorm(FArate_adj1))
  )

corrdata = data.frame(x=dat2plot$d_prime, y=dat2plot$RT_Mean)

corrRho1 = SpearmanRho(x = corrdata$x, y = corrdata$y, conf.level = .95)
cbf1 = correlationBF(corrdata$x, corrdata$y, rscale = "medium",iterations=num.iter)
plot1<-ggscatter(corrdata, x = "x", y = "y", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = def.cormethod, size = 3, alpha = 0.6,
          add.params = list(fill = "lightgray"),
          ggtheme = theme_classic(),
          xlab = "dprime", ylab = "RT",
          title = sprintf("Rho: %1.3f CI[%1.3f %1.3f]; BF: %1.3f",corrRho1[[1]],corrRho1[[2]],corrRho1[[3]],extractBF(cbf1)[[1]]))+
  font("title", size = 8)



plotttitle <- ggdraw() + draw_label("Spearman Rank Correlations\nall experiments", fontface='bold', size=12)
ggarrange(plotttitle, plot1,nrow = 2, heights=c(0.2, 1))

dat2plot_t <- dat2plot %>%
  filter(colorlum=='offset_to_bckgrd')
corrdata = data.frame(x=dat2plot_t$d_prime, y=dat2plot_t$RT_Mean)

corrRho1 = SpearmanRho(x = corrdata$x, y = corrdata$y, conf.level = .95)
cbf1 = correlationBF(corrdata$x, corrdata$y, rscale = "medium",iterations=num.iter)
plot1<-ggscatter(corrdata, x = "x", y = "y", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = def.cormethod, size = 3, alpha = 0.6,
          add.params = list(fill = "lightgray"),
          ggtheme = theme_classic(),
          xlab = "dprime", ylab = "RT",
          title = sprintf("Rho: %1.3f CI[%1.3f %1.3f]; BF: %1.3f",corrRho1[[1]],corrRho1[[2]],corrRho1[[3]],extractBF(cbf1)[[1]]))+
  font("title", size = 8)



plotttitle <- ggdraw() + draw_label("Spearman Rank Correlations\nluminance offset", fontface='bold', size=12)
ggarrange(plotttitle, plot1,nrow = 2, heights=c(0.2, 1))

# do the same analysis for the other conditions
dat2plot_t <- dat2plot %>%
  filter(colorlum=='isolum__to_bckgrd')
corrdata = data.frame(x=dat2plot_t$d_prime, y=dat2plot_t$RT_Mean)

corrRho1 = SpearmanRho(x = corrdata$x, y = corrdata$y, conf.level = .95)
cbf1 = correlationBF(corrdata$x, corrdata$y, rscale = "medium",iterations=num.iter)
plot1<-ggscatter(corrdata, x = "x", y = "y", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = def.cormethod, size = 3, alpha = 0.6,
          add.params = list(fill = "lightgray"),
          ggtheme = theme_classic(),
          xlab = "dprime", ylab = "RT",
          title = sprintf("Rho: %1.3f CI[%1.3f %1.3f]; BF: %1.3f",corrRho1[[1]],corrRho1[[2]],corrRho1[[3]],extractBF(cbf1)[[1]]))+
  font("title", size = 8)



plotttitle <- ggdraw() + draw_label("Spearman Rank Correlations\nisoluminant", fontface='bold', size=12)
ggarrange(plotttitle, plot1,nrow = 2, heights=c(0.2, 1))

```

<br>  

```{r corr2, results = "hide",  fig.height=8, fig.width=8, warning = FALSE}
# def.cormethod ="pearson"
def.cormethod ="spearman"
num.iter = 10000


dat2plot <- DATA_Trials %>%
  group_by(participant)%>%
  summarise(RT_Mean=mean(RT,na.rm=TRUE),RT_STD=sd(RT,na.rm=TRUE),Hitrate=(sum(response=='hit')/n())*100)

dat2plot2 <- DataIn2 %>%
  mutate(`FA_all`= FA + `FA_proper`)%>%
  # dplyr::select(-FA)%>%
  dplyr::select(-FA_all)%>%
  rename(participant=subject)

dat2plot_all <- merge(dat2plot,dat2plot2)

corrdata = data.frame(x=dat2plot_all$Hitrate, y=dat2plot_all$RT_Mean)

corrRho1 = SpearmanRho(x = corrdata$x, y = corrdata$y, conf.level = .95)
cbf1 = correlationBF(corrdata$x, corrdata$y, rscale = "medium",iterations=num.iter)
plot1<-ggscatter(corrdata, x = "x", y = "y", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = def.cormethod, size = 3, alpha = 0.6,
          add.params = list(fill = "lightgray"),
          ggtheme = theme_classic(),
          xlab = "Hit rate", ylab = "RT",
          title = sprintf("Rho: %1.3f CI[%1.3f %1.3f]; BF: %1.3f",corrRho1[[1]],corrRho1[[2]],corrRho1[[3]],extractBF(cbf1)[[1]]))+
  font("title", size = 8)

corrdata = data.frame(x=dat2plot_all$FA_proper, y=dat2plot_all$RT_Mean)

corrRho2 = SpearmanRho(x = corrdata$x, y = corrdata$y, conf.level = .95)
cbf2 = correlationBF(corrdata$x, corrdata$y, rscale = "medium",iterations=num.iter)
plot2<-ggscatter(corrdata, x = "x", y = "y", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = def.cormethod, size = 3, alpha = 0.6,
          add.params = list(fill = "lightgray"),
          ggtheme = theme_classic(),
          xlab = "FA proper", ylab = "RT",
          title = sprintf("Rho: %1.3f CI[%1.3f %1.3f]; BF: %1.3f",corrRho2[[1]],corrRho2[[2]],corrRho2[[3]],extractBF(cbf2)[[1]]))+
  font("title", size = 8)

corrdata = data.frame(x=dat2plot_all$FA, y=dat2plot_all$RT_Mean)

corrRho3 = SpearmanRho(x = corrdata$x, y = corrdata$y, conf.level = .95)
cbf3 = correlationBF(corrdata$x, corrdata$y, rscale = "medium",iterations=num.iter)
plot3<-ggscatter(corrdata, x = "x", y = "y", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = def.cormethod, size = 3, alpha = 0.6,
          add.params = list(fill = "lightgray"),
          ggtheme = theme_classic(),
          xlab = "FA", ylab = "RT",
          title = sprintf("Rho: %1.3f CI[%1.3f %1.3f]; BF: %1.3f",corrRho3[[1]],corrRho3[[2]],corrRho3[[3]],extractBF(cbf3)[[1]]))+
  font("title", size = 8)

corrdata = data.frame(x=dat2plot_all$FA_proper, y=dat2plot_all$Hitrate)

corrRho4 = SpearmanRho(x = corrdata$x, y = corrdata$y, conf.level = .95)
cbf4 = correlationBF(corrdata$x, corrdata$y, rscale = "medium",iterations=num.iter)
plot4<-ggscatter(corrdata, x = "x", y = "y", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = def.cormethod, size = 3, alpha = 0.6,
          add.params = list(fill = "lightgray"),
          ggtheme = theme_classic(),
          xlab = "FA proper", ylab = "Hit rate",
          title = sprintf("Rho: %1.3f CI[%1.3f %1.3f]; BF: %1.3f",corrRho4[[1]],corrRho4[[2]],corrRho4[[3]],extractBF(cbf4)[[1]]))+
  font("title", size = 8)

corrdata = data.frame(x=dat2plot_all$FA, y=dat2plot_all$Hitrate)

corrRho5 = SpearmanRho(x = corrdata$x, y = corrdata$y, conf.level = .95)
cbf5 = correlationBF(corrdata$x, corrdata$y, rscale = "medium",iterations=num.iter)
plot5<-ggscatter(corrdata, x = "x", y = "y", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = def.cormethod, size = 3, alpha = 0.6,
          add.params = list(fill = "lightgray"),
          ggtheme = theme_classic(),
          xlab = "FA", ylab = "Hit rate",
          title = sprintf("Rho: %1.3f CI[%1.3f %1.3f]; BF: %1.3f",corrRho5[[1]],corrRho5[[2]],corrRho5[[3]],extractBF(cbf5)[[1]]))+
  font("title", size = 8)

corrdata = data.frame(x=dat2plot_all$FA, y=dat2plot_all$FA_proper)

corrRho6 = SpearmanRho(x = corrdata$x, y = corrdata$y, conf.level = .95)
cbf6 = correlationBF(corrdata$x, corrdata$y, rscale = "medium",iterations=num.iter)
plot6<-ggscatter(corrdata, x = "x", y = "y", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = def.cormethod, size = 3, alpha = 0.6,
          add.params = list(fill = "lightgray"),
          ggtheme = theme_classic(),
          xlab = "FA", ylab = "FA proper",
          title = sprintf("Rho: %1.3f CI[%1.3f %1.3f]; BF: %1.3f",corrRho6[[1]],corrRho6[[2]],corrRho6[[3]],extractBF(cbf6)[[1]]))+
  font("title", size = 8)

plotttitle <- ggdraw() + draw_label("Spearman Rank Correlations between behavioral measures", fontface='bold', size=12)
plotplots <- ggarrange(plot1, plot2, plot3, plot4, plot5, plot6, ncol = 3, nrow = 2)
ggarrange(plotttitle, ggarrange(plot1, plot2, plot3, ncol = 3), ggarrange("", plot4, plot5, ncol = 3), ggarrange("", "", plot6, ncol = 3),
          nrow = 4, heights=c(0.2, 1, 1, 1))


  


```

## Statistical analysis

### ANOVA models
### linear mixed models

#### test RT, Hitrate and dprime between background luminance values

**RT** ~ **luminance**

<br> 

```{r lme_RT_lum, fig.show = "hide", warning = FALSE, fig.height=4, fig.width=10}
dat2plot2 <- DataIn2 %>%
  mutate(`FA_all`= FA + `FA_proper`)%>%
  # dplyr::select(-FA)%>%
  dplyr::select(-FA_all)%>%
  pivot_longer(c(-subject ),names_to = "FA_type", values_to = "number")%>%
  filter(FA_type=='FA_proper' | FA_type=='FA')


dat2plot <- DATA_Trials %>%
  group_by(participant,colorlum)%>%
  summarise(RT_Mean=mean(RT,na.rm=TRUE),RT_STD=sd(RT,na.rm=TRUE),Hitrate=(sum(response=='hit')/n())*100)

dat2plot2 <- DataIn2 %>%
  mutate(`FA_all`= FA + `FA_proper`)%>%
  # dplyr::select(-FA)%>%
  dplyr::select(-FA_all)%>%
  rename(participant=subject)

dat2plot_all <- merge(dat2plot,dat2plot2) %>%
  mutate(
    d_prime = qnorm(Hitrate/100)-qnorm(FA_proper_rate),
    c = -0.5*(qnorm(Hitrate/100)+qnorm(FA_proper_rate))
  )



# # statisticical analysis ANOVA
# StatsOut <- dat2plot_all %>%
#   aov_ez(id="participant", dv = "RT_Mean", data = ., between = c("colorlum"), include_aov = afex_options("include_aov"))
# 
# StatsOut%>%
#   .$anova %>%
#   mutate(factor = rownames(.))%>%
#   mutate(
#     `Pr(>F)` = cell_spec(ifelse(round(`Pr(>F)`,4)<.001,"< .001",round(`Pr(>F)`,4)),
#                         color = ifelse(is.nan(`Pr(>F)`),"blue", ifelse(`Pr(>F)` < .05, "green", "red")),
#                         bold = ifelse(is.nan(`Pr(>F)`),F, ifelse(`Pr(>F)` < .05, T,F)),
#                         align = "center")
#   ) %>%
#   dplyr::select(`num Df`, `den Df`, MSE, `F`, ges, `Pr(>F)`) %>%
#   kable(escape = F, digits = c(3,3,3,3,3,3,3,3,3), caption = c("ANOVA | dv = RT in ms")) %>%
#   kable_styling("striped", full_width = T, bootstrap_options = c("striped", "hover", "condensed", "responsive",font_size = 6))


# RT
dat2plot_all %>%
  nest() %>%
  mutate(
    stats = map(data, ~ broom::tidy(t.test(RT_Mean ~ colorlum, data = ., paired = FALSE))),
    t_test_bf = map(data, ~ extractBF(ttestBF(formula = RT_Mean ~ colorlum, data = ., iterations = num.iter, rscale = sqrt(2)/2))),
    meanval = map(data, ~ .x %>%
                    group_by(colorlum) %>%
                    summarise(
                      mean_RT_Mean = mean(RT_Mean, na.rm = TRUE),
                      std_RT_Mean = sd(RT_Mean, na.rm = TRUE)
                    ) %>%
                    pivot_wider(names_from = colorlum, 
                                values_from = c(mean_RT_Mean, std_RT_Mean), 
                                names_sep = "_")
    ),
    cohens_d = map(data, ~ rstatix::cohens_d(RT_Mean ~ colorlum, data = ., paired = FALSE))
  ) %>%
  unnest(cols = c(stats, cohens_d, t_test_bf, meanval))%>%
  mutate(BF10 = bf, BF01 = 1/bf, 
         M_RT_iso = mean_RT_Mean_isolum__to_bckgrd,
         SD_RT_iso = std_RT_Mean_isolum__to_bckgrd,
         M_RT_off = mean_RT_Mean_offset_to_bckgrd,
         SD_RT_off = std_RT_Mean_offset_to_bckgrd,
         diff=estimate,
         CohensD = effsize, t.value=statistic, df = parameter)%>%
  dplyr::select(M_RT_iso, SD_RT_iso, M_RT_off, SD_RT_off, diff, t.value, df, p.value, CohensD, BF10, BF01)%>%
  # mutate(p.value = p.adjust(p.value, method="holm")) %>% # none, holm
  # mutate(p.value = p.adjust(p.value, method="none")) %>% # none, holm
  ungroup()%>%
  mutate(
    p.value = cell_spec(ifelse(round(p.value,4)<.001,"< .001",round(p.value,4)), 
                        color = ifelse(is.nan(p.value),"blue", ifelse(p.value < .05, "green", "red")),
                        bold = ifelse(is.nan(p.value),F, ifelse(p.value < .05, T,F)),
                        align = "center")
  ) %>%
  kable(escape = F, digits = c(3,3,3,3,3,3,3,3,3), 
        caption = c("RT | modulation by stimulus display group (isolum vs lum offset) | t-tests of difference")) %>%
  kable_styling("striped", full_width = T, bootstrap_options = c("striped", "hover", "condensed", "responsive",font_size = 8))
```

**Hitrate** ~ **luminance**

<br> 

```{r lme_HR_lum, fig.show = "hide", warning = FALSE, fig.height=4, fig.width=10}
# Hitrate
dat2plot_all %>%
  nest() %>%
  mutate(
    stats = map(data, ~ broom::tidy(t.test(Hitrate ~ colorlum, data = ., paired = FALSE))),
    t_test_bf = map(data, ~ extractBF(ttestBF(formula = Hitrate ~ colorlum, data = ., iterations = num.iter, rscale = sqrt(2)/2))),
    meanval = map(data, ~ .x %>%
                    group_by(colorlum) %>%
                    summarise(
                      mean_HR_Mean = mean(Hitrate, na.rm = TRUE),
                      std_HR_Mean = sd(Hitrate, na.rm = TRUE)
                    ) %>%
                    pivot_wider(names_from = colorlum, 
                                values_from = c(mean_HR_Mean, std_HR_Mean), 
                                names_sep = "_")
    ),
    cohens_d = map(data, ~ rstatix::cohens_d(Hitrate ~ colorlum, data = ., paired = FALSE))
  ) %>%
  unnest(cols = c(stats, cohens_d, t_test_bf, meanval))%>%
  mutate(BF10 = bf, BF01 = 1/bf, 
         M_HR_iso = mean_HR_Mean_isolum__to_bckgrd,
         SD_HR_iso = std_HR_Mean_isolum__to_bckgrd,
         M_HR_off = mean_HR_Mean_offset_to_bckgrd,
         SD_HR_off = std_HR_Mean_offset_to_bckgrd,
         diff=estimate,
         CohensD = effsize, t.value=statistic, df = parameter)%>%
  dplyr::select(M_HR_iso, SD_HR_iso, M_HR_off, SD_HR_off, diff, t.value, df, p.value, CohensD, BF10, BF01)%>%
  # mutate(p.value = p.adjust(p.value, method="holm")) %>% # none, holm
  # mutate(p.value = p.adjust(p.value, method="none")) %>% # none, holm
  ungroup()%>%
  mutate(
    p.value = cell_spec(ifelse(round(p.value,4)<.001,"< .001",round(p.value,4)), 
                        color = ifelse(is.nan(p.value),"blue", ifelse(p.value < .05, "green", "red")),
                        bold = ifelse(is.nan(p.value),F, ifelse(p.value < .05, T,F)),
                        align = "center")
  ) %>%
  kable(escape = F, digits = c(3,3,3,3,3,3,3,3,3), 
        caption = c("Hitrate | modulation by stimulus display group (isolum vs lum offset) | t-tests of difference")) %>%
  kable_styling("striped", full_width = T, bootstrap_options = c("striped", "hover", "condensed", "responsive",font_size = 8))
```

**FArate** ~ **luminance**

<br> 

```{r lme_FAR_lum, fig.show = "hide", warning = FALSE, fig.height=4, fig.width=10}
# FArate
dat2plot_all %>%
  nest() %>%
  mutate(
    stats = map(data, ~ broom::tidy(t.test(FA_proper_rate ~ colorlum, data = ., paired = FALSE))),
    t_test_bf = map(data, ~ extractBF(ttestBF(formula = FA_proper_rate ~ colorlum, data = ., iterations = num.iter, rscale = sqrt(2)/2))),
    meanval = map(data, ~ .x %>%
                    group_by(colorlum) %>%
                    summarise(
                      mean_FAR_Mean = mean(FA_proper_rate, na.rm = TRUE),
                      std_FAR_Mean = sd(FA_proper_rate, na.rm = TRUE)
                    ) %>%
                    pivot_wider(names_from = colorlum, 
                                values_from = c(mean_FAR_Mean, std_FAR_Mean), 
                                names_sep = "_")
    ),
    cohens_d = map(data, ~ rstatix::cohens_d(FA_proper_rate ~ colorlum, data = ., paired = FALSE))
  ) %>%
  unnest(cols = c(stats, cohens_d, t_test_bf, meanval))%>%
  mutate(BF10 = bf, BF01 = 1/bf, 
         M_FAR_iso = mean_FAR_Mean_isolum__to_bckgrd,
         SD_FAR_iso = std_FAR_Mean_isolum__to_bckgrd,
         M_FAR_off = mean_FAR_Mean_offset_to_bckgrd,
         SD_FAR_off = std_FAR_Mean_offset_to_bckgrd,
         diff=estimate,
         CohensD = effsize, t.value=statistic, df = parameter)%>%
  dplyr::select(M_FAR_iso, SD_FAR_iso, M_FAR_off, SD_FAR_off, diff, t.value, df, p.value, CohensD, BF10, BF01)%>%
  # mutate(p.value = p.adjust(p.value, method="holm")) %>% # none, holm
  # mutate(p.value = p.adjust(p.value, method="none")) %>% # none, holm
  ungroup()%>%
  mutate(
    p.value = cell_spec(ifelse(round(p.value,4)<.001,"< .001",round(p.value,4)), 
                        color = ifelse(is.nan(p.value),"blue", ifelse(p.value < .05, "green", "red")),
                        bold = ifelse(is.nan(p.value),F, ifelse(p.value < .05, T,F)),
                        align = "center")
  ) %>%
  kable(escape = F, digits = c(3,3,3,3,3,3,3,3,3), 
        caption = c("FA-rate | modulation by stimulus display group (isolum vs lum offset) | t-tests of difference")) %>%
  kable_styling("striped", full_width = T, bootstrap_options = c("striped", "hover", "condensed", "responsive",font_size = 8))


```

**d-prime** ~ **luminance**

<br> 

```{r lme_dprime_lum, fig.show = "hide", warning = FALSE, fig.height=4, fig.width=10}
# d-prime
dat2plot_all %>%
  nest() %>%
  mutate(
    stats = map(data, ~ broom::tidy(t.test(d_prime ~ colorlum, data = ., paired = FALSE))),
    t_test_bf = map(data, ~ extractBF(ttestBF(formula = d_prime ~ colorlum, data = ., iterations = num.iter, rscale = sqrt(2)/2))),
    meanval = map(data, ~ .x %>%
                    group_by(colorlum) %>%
                    summarise(
                      mean_d_Mean = mean(d_prime, na.rm = TRUE),
                      std_d_Mean = sd(d_prime, na.rm = TRUE)
                    ) %>%
                    pivot_wider(names_from = colorlum, 
                                values_from = c(mean_d_Mean, std_d_Mean), 
                                names_sep = "_")
    ),
    cohens_d = map(data, ~ rstatix::cohens_d(d_prime ~ colorlum, data = ., paired = FALSE))
  ) %>%
  unnest(cols = c(stats, cohens_d, t_test_bf, meanval))%>%
  mutate(BF10 = bf, BF01 = 1/bf, 
         M_d_iso = mean_d_Mean_isolum__to_bckgrd,
         SD_d_iso = std_d_Mean_isolum__to_bckgrd,
         M_d_off = mean_d_Mean_offset_to_bckgrd,
         SD_d_off = std_d_Mean_offset_to_bckgrd,
         diff=estimate,
         CohensD = effsize, t.value=statistic, df = parameter)%>%
  dplyr::select(M_d_iso, SD_d_iso, M_d_off, SD_d_off, diff, t.value, df, p.value, CohensD, BF10, BF01)%>%
  # mutate(p.value = p.adjust(p.value, method="holm")) %>% # none, holm
  # mutate(p.value = p.adjust(p.value, method="none")) %>% # none, holm
  ungroup()%>%
  mutate(
    p.value = cell_spec(ifelse(round(p.value,4)<.001,"< .001",round(p.value,4)), 
                        color = ifelse(is.nan(p.value),"blue", ifelse(p.value < .05, "green", "red")),
                        bold = ifelse(is.nan(p.value),F, ifelse(p.value < .05, T,F)),
                        align = "center")
  ) %>%
  kable(escape = F, digits = c(3,3,3,3,3,3,3,3,3), 
        caption = c("d-prime | modulation by stimulus display group (isolum vs lum offset) | t-tests of difference")) %>%
  kable_styling("striped", full_width = T, bootstrap_options = c("striped", "hover", "condensed", "responsive",font_size = 8))
```

**c criterion** ~ **luminance**

<br> 

```{r lme_c_lum, fig.show = "hide", warning = FALSE, fig.height=4, fig.width=10}
# d-prime
dat2plot_all %>%
  nest() %>%
  mutate(
    stats = map(data, ~ broom::tidy(t.test(c ~ colorlum, data = ., paired = FALSE))),
    t_test_bf = map(data, ~ extractBF(ttestBF(formula = c ~ colorlum, data = ., iterations = num.iter, rscale = sqrt(2)/2))),
    meanval = map(data, ~ .x %>%
                    group_by(colorlum) %>%
                    summarise(
                      mean_c_Mean = mean(c, na.rm = TRUE),
                      std_c_Mean = sd(c, na.rm = TRUE)
                    ) %>%
                    pivot_wider(names_from = colorlum,
                                values_from = c(mean_c_Mean, std_c_Mean),
                                names_sep = "_")
    ),
    cohens_d = map(data, ~ rstatix::cohens_d(c ~ colorlum, data = ., paired = FALSE))
  ) %>%
  unnest(cols = c(stats, cohens_d, t_test_bf, meanval))%>%
  mutate(BF10 = bf, BF01 = 1/bf, 
         M_c_iso = mean_c_Mean_isolum__to_bckgrd,
         SD_c_iso = std_c_Mean_isolum__to_bckgrd,
         M_c_off = mean_c_Mean_offset_to_bckgrd,
         SD_c_off = std_c_Mean_offset_to_bckgrd,
         diff=estimate,
         CohensD = effsize, t.value=statistic, df = parameter)%>%
  dplyr::select(M_c_iso, SD_c_iso, M_c_off, SD_c_off, diff, t.value, df, p.value, CohensD, BF10, BF01)%>%
  # mutate(p.value = p.adjust(p.value, method="holm")) %>% # none, holm
  # mutate(p.value = p.adjust(p.value, method="none")) %>% # none, holm
  ungroup()%>%
  mutate(
    p.value = cell_spec(ifelse(round(p.value,4)<.001,"< .001",round(p.value,4)), 
                        color = ifelse(is.nan(p.value),"blue", ifelse(p.value < .05, "green", "red")),
                        bold = ifelse(is.nan(p.value),F, ifelse(p.value < .05, T,F)),
                        align = "center")
  ) %>%
  kable(escape = F, digits = c(3,3,3,3,3,3,3,3,3), 
        caption = c("criterion | modulation by stimulus display group (isolum vs lum offset) | t-tests of difference")) %>%
  kable_styling("striped", full_width = T, bootstrap_options = c("striped", "hover", "condensed", "responsive",font_size = 8))
```

