---
title: "FFT_SSVEP_analysis"
author: "Christopher"
date: "2 4 2026"
output:
  html_document:
    code_folding: hide
    toc: true
    toc_float: true
    toc_depth: 4
    theme: flatly
---

Modelling of ~~raw~~ [*CSD based*] amplitude values from fft-based data
via linear mixed models
via standard anova models

```{r load_package, message = FALSE, warning = FALSE}
library(lme4)
library(readxl)
library(tidyverse)
library(data.table)
library(tidyverse)
library(afex)
library(broom)
library(apa)
library(kableExtra)
library(lmerTest)
library(pbkrtest)
library(effects)
library(visreg)
library(sjPlot)
library(broom.mixed)
library(pander)
library(mediation)
library(multcomp)
library(multcompView)
library(magrittr)
library(multipanelfigure)
library(ggbeeswarm)
library(lsmeans)
library(BayesFactor)
library(ggpubr)
library(gpairs)
library(DescTools)
library(cowplot)
library(ggpol)
library(logspline)

library(effectsize)

source('C:/Dropboxdata/Dropbox/work/R-statistics/general_functions/RainCloudPlots/tutorial_R/R_rainclouds.R')
source('C:/Dropboxdata/Dropbox/work/R-statistics/general_functions/RainCloudPlots/tutorial_R/R_rainclouds.R')

source('C:/Dropboxdata/Dropbox/work/R-statistics/examples/Bayesian_rank-based_hypothesis_testing/rankBasedCommonFunctions.R')
source('C:/Dropboxdata/Dropbox/work/R-statistics/examples/Bayesian_rank-based_hypothesis_testing/rankSumSampler.R') # Wilcoxon rank sum function
source('C:/Dropboxdata/Dropbox/work/R-statistics/examples/Bayesian_rank-based_hypothesis_testing/signRankSampler.R') # Wilcoxon signed-rank function
source('C:/Dropboxdata/Dropbox/work/R-statistics/examples/Bayesian_rank-based_hypothesis_testing/spearmanSampler.R')# Spearman's rho function






#!!!!!!! relevant
# broad cluster | larger central cluster as in Tango study | peri both clusters but smaller
# CSD based normalized to pre-cue baseline in %
# for changed experiment starting with participant 22: isoluminant stimuli and lower flicker frequencies
DATAPath = "data_in/FFT_Amp_data_CenterTangoStudyPeriSmall_05-23-2025_11-56.csv"
# DATAPath = "data_in/"
t_baseline = c(-1000, 0)


#!!!!!!!

# 


options(scipen=1, digits=7)
```
<style type="text/css">
.main-container {
max-width: 1800px !important;
margin-left: auto;
margin-right: auto;
}
</style>


## Prepare data  
<br>  

1.  Read in data: 
+ `r DATAPath`
+ with pre-cue  [`r toString(t_baseline)`] ms

<br>  

```{r load_data,results = "hide", fig.show = "hide", warning = FALSE}
sub_sample = c(0)
# sub_sample = as.factor(c(26,30, 31,37, 38)) # no ssvep people discarded
sub_sample = as.factor(c(42)) # low trial number


# read in data
DataIn <- read.csv(DATAPath, sep = ";") %>%
  mutate(subjects = as.factor(subjects))%>%
  filter(!subjects %in% sub_sample)
head(DataIn)
str(DataIn)
```




## Statistical analysis



### Central Stimuli analysis

**modulation** ~ **COLOR ATTENTION** x **PERI STIM CONDITION**

- linear mixed models
- post hoc contrast via emmeans

<br> 

```{r Stat central stimuli analysisIIb, message=FALSE, warning=FALSE, include=TRUE,fig.height=3, fig.width=3.5}
dat2plot <- DataIn %>%
  filter(RDK_position2=="center", RDK_colorlum=="isolum__to_bckgrd") %>%
  mutate(condition_label = case_when(
    condition %in% c(1,2) ~ "peri_AttUnatt",
    condition %in% c(3,4) ~ "peri_AttIrrel",
    condition %in% c(5,6) ~ "peri_UnattIrrel"
  ))%>%
  group_by(subjects, time, RDK_isattended, condition_label)%>%
  summarise(amplitude_evoked=mean(amplitude_evoked), modulation_evoked=mean(modulation_evoked))%>%
  filter(time != '[1 2] ')

# post cue anova
lmmmodel2 <- dat2plot %>%
  filter(time == '[0.5 1.5] ')%>%
  mixed(
    modulation_evoked ~ RDK_isattended * condition_label + (1 | subjects),
    data = .,
    method = "KR",  # Kenward-Roger approximation for p-values
    return = "afex_aov",  # ensures compatibility with emmeans
  )

# compute generalized eta squared
eta_tab <- effectsize::eta_squared(lmmmodel2, generalized = TRUE, partial = FALSE) %>%
  as.data.frame() %>%
  dplyr::select(Parameter, Eta2_partial)


lmmmodel2 %>%
  anova()%>%
  tidy()%>%
  left_join(eta_tab, by = c("term" = "Parameter")) %>%
  mutate(
    `p.value` = cell_spec(ifelse(round(`p.value`,4)<.001,"< .001",round(`p.value`,4)), 
                        color = ifelse(is.nan(`p.value`),"blue", ifelse(`p.value` < .05, "green", "red")),
                        bold = ifelse(is.nan(`p.value`),F, ifelse(`p.value` < .05, T,F)),
                        align = "center")
  ) %>%
  dplyr::select(term, num.Df, den.Df, statistic, Eta2_partial, `p.value`) %>%
  kbl(escape = F, digits = c(5,5,5,5,5,5,5,5,5), 
      caption = c("Mixed Model Anova Table (Type 3 tests, KR-method) | central SSVEP post-cue modulations")) %>%
  kable_styling("striped", full_width = T, bootstrap_options = c("striped", "hover", "condensed", "responsive",font_size = 8))






# Display estimated marginal means of pre-cue amplitudes for the model
emmeans(lmmmodel2, ~  condition_label*RDK_isattended) %>%
  tidy() %>%
  dplyr::select(condition_label,RDK_isattended,estimate,std.error,df)%>%
  dplyr::arrange(condition_label)%>%
  dplyr::rename(emmean = estimate, SE = std.error)%>%
  kbl(escape = F, digits = c(5,5,5,5,5,5,5,5,5), 
      caption = c("EMMEANs for LMM (Type 3 tests, KR-method) | central SSVEP post-cue modulations")) %>%
  kable_styling("striped", full_width = T, bootstrap_options = c("striped", "hover", "condensed", "responsive",font_size = 8))


#display main effects via emmeans
# Main effect of RDK_isattended
emm_ATT_lmm <- as.data.frame(emmeans(lmmmodel2, ~ RDK_isattended))

# Main effect of condition_label
emm_Pericondition_lmm <- as.data.frame(emmeans(lmmmodel2, ~ condition_label))

# RDK_isattended plot
# add some more range to the y axis to allow for some more space for error bars and contrasts
y_range <- range(c(emm_ATT_lmm$lower.CL, emm_ATT_lmm$upper.CL))
y_extension <- diff(y_range) * 0.20

saveplot <- ggplot(emm_ATT_lmm, aes(x = RDK_isattended, y = emmean, fill = RDK_isattended)) +
  geom_col(position = position_dodge(), width = 0.6) +
  geom_errorbar(aes(ymin = lower.CL, ymax = upper.CL), width = 0.2) +
  labs(title = "Main Effect of RDK_isattended",
       y = "Estimated Marginal Means (95% CI)", x = "RDK_isattended") +
  theme_light() +
  scale_fill_manual(values=c("steelblue2", "#F03F3F"))+
  scale_color_manual(values=c("steelblue2", "#F03F3F"))+
  scale_y_continuous(limits = c(y_range[1], y_range[2] + y_extension)) +
  theme(axis.text.x = element_blank())

savefig <- multi_panel_figure(columns = 1, rows = 1, panel_label_type = "none", width = 3.5, height = 3, unit = "in")
savefig %<>%
  fill_panel(saveplot, column = 1, row = 1)
savefig
# save_multi_panel_figure(savefig, "figures/FFT_Center_MargMeans_ATTENTION.eps")


# condition_label plot
ggplot(emm_Pericondition_lmm, aes(x = condition_label, y = emmean, fill = condition_label)) +
  geom_col(position = position_dodge(), width = 0.6) +
  geom_errorbar(aes(ymin = lower.CL, ymax = upper.CL), width = 0.2) +
  labs(title = "No Main Effect of condition_label",
       y = "Estimated Marginal Means (95% CI)", x = "Condition Label") +
  theme_light() +
  scale_fill_brewer(palette = "Dark2")+
  scale_color_brewer(palette = "Dark2")+
  theme(axis.text.x = element_blank())

#post hoc contrasts identity
post_hocs.RDK_isattended_id <- emmeans(lmmmodel2, c("RDK_isattended"), contr = "identity",adjust = "FDR") # adjust = holm
post_hocs.condition_label_id <- emmeans(lmmmodel2, c("condition_label"), contr = "identity",adjust = "FDR") # adjust = holm

# report data for post_hoc attention
post_hocs.RDK_isattended_id%>%
  .$contrasts %>%
  tidy()%>%
  dplyr::rename(t.ratio=statistic, p.value=adj.p.value)%>%
  mutate(
    p.value = cell_spec(ifelse(round(p.value,4)<.001,"< .001",round(p.value,4)), 
                        color = ifelse(is.nan(p.value),"blue", ifelse(p.value < .05, "green", "red")),
                        bold = ifelse(is.nan(p.value),F, ifelse(p.value < .05, T,F)),
                        align = "left")
  ) %>% # mutate(CohensD = `t.ratio`/sqrt(df+1))%>%
  mutate(`CohensD` =
           summary(eff_size(post_hocs.RDK_isattended_id,
                            sigma = sqrt(mean(sigma(lmmmodel2$full_model)^2)), # RMS of sigma()
                            edf = df.residual(lmmmodel2$full_model), method = "identity"))$effect.size,
         `lowCI` =
           summary(eff_size(post_hocs.RDK_isattended_id,
                            sigma = sqrt(mean(sigma(lmmmodel2$full_model)^2)), # RMS of sigma()
                            edf = df.residual(lmmmodel2$full_model), method = "identity"))$lower.CL,
         `highCI` =
           summary(eff_size(post_hocs.RDK_isattended_id,
                            sigma = sqrt(mean(sigma(lmmmodel2$full_model)^2)), # RMS of sigma()
                            edf = df.residual(lmmmodel2$full_model), method = "identity"))$upper.CL
  )%>%
  kbl(escape = F, digits = c(3,3,3,3,3,3,3,3,3), 
      caption = c("estimated marginal means | by PERI_CON | dv = central SSVEP modulation | FDR corrected")) %>%
  kable_styling("striped", full_width = T, bootstrap_options = c("striped", "hover", "condensed", "responsive",font_size = 8))


# report data for post_hoc condition_label
post_hocs.condition_label_id%>%
  .$contrasts %>%
  tidy()%>%
  dplyr::rename(t.ratio=statistic, p.value=adj.p.value)%>%
  mutate(
    p.value = cell_spec(ifelse(round(p.value,4)<.001,"< .001",round(p.value,4)), 
                        color = ifelse(is.nan(p.value),"blue", ifelse(p.value < .05, "green", "red")),
                        bold = ifelse(is.nan(p.value),F, ifelse(p.value < .05, T,F)),
                        align = "left")
  ) %>% # mutate(CohensD = `t.ratio`/sqrt(df+1))%>%
  mutate(`CohensD` =
           summary(eff_size(post_hocs.condition_label_id,
                            sigma = sqrt(mean(sigma(lmmmodel2$full_model)^2)), # RMS of sigma()
                            edf = df.residual(lmmmodel2$full_model), method = "identity"))$effect.size,
         `lowCI` =
           summary(eff_size(post_hocs.condition_label_id,
                            sigma = sqrt(mean(sigma(lmmmodel2$full_model)^2)), # RMS of sigma()
                            edf = df.residual(lmmmodel2$full_model), method = "identity"))$lower.CL,
         `highCI` =
           summary(eff_size(post_hocs.condition_label_id,
                            sigma = sqrt(mean(sigma(lmmmodel2$full_model)^2)), # RMS of sigma()
                            edf = df.residual(lmmmodel2$full_model), method = "identity"))$upper.CL
  )%>%
  kbl(escape = F, digits = c(3,3,3,3,3,3,3,3,3), 
      caption = c("estimated marginal means | by PERI_CON | dv = central SSVEP modulation | FDR corrected")) %>%
  kable_styling("striped", full_width = T, bootstrap_options = c("striped", "hover", "condensed", "responsive",font_size = 8))




#post hoc contrasts paired
post_hocs.RDK_isattended <- emmeans(lmmmodel2, c("RDK_isattended"), contr = "pairwise",adjust = "FDR") # adjust = holm
post_hocs.condition_label <- emmeans(lmmmodel2, c("condition_label"), contr = "pairwise",adjust = "FDR") # adjust = holm


summary(post_hocs.RDK_isattended$contrasts) %>%
  mutate(
    p.value = cell_spec(ifelse(round(p.value,4)<.001,"< .001",round(p.value,4)), 
                        color = ifelse(is.nan(p.value),"blue", ifelse(p.value < .05, "green", "red")),
                        bold = ifelse(is.nan(p.value),F, ifelse(p.value < .05, T,F)),
                        align = "left")
  ) %>%
  # mutate(CohensD = `t.ratio`/sqrt(df+1))%>%
  mutate(`CohensD` =
           summary(eff_size(post_hocs.RDK_isattended,
                            sigma = sqrt(mean(sigma(lmmmodel2$full_model)^2)), # RMS of sigma()
                            # sigma = sigma(lmmmodel2$full_model), # RMS of sigma()
                            edf = df.residual(lmmmodel2$full_model), method = "pairwise"))$effect.size,
         `lowCI` =
           summary(eff_size(post_hocs.RDK_isattended,
                            sigma = sqrt(mean(sigma(lmmmodel2$full_model)^2)), # RMS of sigma()
                            edf = df.residual(lmmmodel2$full_model), method = "pairwise"))$lower.CL,
         `highCI` =
           summary(eff_size(post_hocs.RDK_isattended,
                            sigma = sqrt(mean(sigma(lmmmodel2$full_model)^2)), # RMS of sigma()
                            edf = df.residual(lmmmodel2$full_model), method = "pairwise"))$upper.CL
  )%>%
  kbl(escape = F, digits = c(3,3,3,3,3,3,3,3,3), 
        caption = c("contrasts for estimated marginal means |by ATTENTION | dv = central SSVEP modulation | corrected: FDR")) %>%
  kable_styling("striped", full_width = T, bootstrap_options = c("striped", "hover", "condensed", "responsive",font_size = 8))


summary(post_hocs.condition_label$contrasts) %>%
  mutate(
    p.value = cell_spec(ifelse(round(p.value,4)<.001,"< .001",round(p.value,4)), 
                        color = ifelse(is.nan(p.value),"blue", ifelse(p.value < .05, "green", "red")),
                        bold = ifelse(is.nan(p.value),F, ifelse(p.value < .05, T,F)),
                        align = "left")
  ) %>%
  # mutate(CohensD = `t.ratio`/sqrt(df+1))%>%
  mutate(`CohensD` =
           summary(eff_size(post_hocs.condition_label,
                            sigma = sqrt(mean(sigma(lmmmodel2$full_model)^2)), # RMS of sigma()
                            edf = df.residual(lmmmodel2$full_model), method = "pairwise"))$effect.size,
         `lowCI` =
           summary(eff_size(post_hocs.condition_label,
                            sigma = sqrt(mean(sigma(lmmmodel2$full_model)^2)), # RMS of sigma()
                            edf = df.residual(lmmmodel2$full_model), method = "pairwise"))$lower.CL,
         `highCI` =
           summary(eff_size(post_hocs.condition_label,
                            sigma = sqrt(mean(sigma(lmmmodel2$full_model)^2)), # RMS of sigma()
                            edf = df.residual(lmmmodel2$full_model), method = "pairwise"))$upper.CL
  )%>%
  kbl(escape = F, digits = c(3,3,3,3,3,3,3,3,3), 
        caption = c("contrasts for estimated marginal means |by PERI CON | dv = central SSVEP modulation | corrected: FDR")) %>%
  kable_styling("striped", full_width = T, bootstrap_options = c("striped", "hover", "condensed", "responsive",font_size = 8))

# pairs(emmeans(aovmodel2, ~ RDK_isattended))
# pairs(emmeans(aovmodel2, ~ condition_label))

```




### Peripheral Stimuli analysis


**modulation** ~ **COLOR ATTENTION** x **PERI STIM CONDITION**

- linear mixed models
- post hoc contrast via emmeans

<br> 

```{r Stat perii stimuli analysisIIb, message=FALSE, warning=FALSE, include=TRUE,fig.height=3, fig.width=3.9}
dat2plot <- DataIn %>%
  filter(RDK_position2!="center", RDK_colorlum=="isolum__to_bckgrd") %>%
  mutate(condition_label = case_when(
    condition %in% c(1,2) ~ "peri_AttUnatt",
    condition %in% c(3,4) ~ "peri_AttIrrel",
    condition %in% c(5,6) ~ "peri_UnattIrrel"
  ))%>%
  group_by(subjects, time, RDK_isattended, condition_label)%>%
  summarise(amplitude_evoked=mean(amplitude_evoked), modulation_evoked=mean(modulation_evoked))%>%
  filter(time != '[1 2] ')

# post cue LMM
lmmmodel2 <- dat2plot %>%
  filter(time == '[0.5 1.5] ')%>%
  mixed(
    modulation_evoked ~ RDK_isattended * condition_label + (1 | subjects),
    data = .,
    method = "KR",  # Kenward-Roger approximation for p-values
    return = "afex_aov"  # ensures compatibility with emmeans
  )

# summary(lmmmodel2$full_model)

# compute generalized eta squared
eta_tab <- effectsize::eta_squared(lmmmodel2, generalized = TRUE, partial = FALSE) %>%
  as.data.frame() %>%
  dplyr::select(Parameter, Eta2_partial)

# Display estimated marginal means of pre-cue amplitudes for the model
emmeans(lmmmodel2, ~  condition_label*RDK_isattended) %>%
  tidy() %>%
  dplyr::select(condition_label,RDK_isattended,estimate,std.error,df)%>%
  dplyr::arrange(condition_label)%>%
  dplyr::rename(emmean = estimate, SE = std.error)%>%
  kbl(escape = F, digits = c(5,5,5,5,5,5,5,5,5), 
      caption = c("EMMEANs for LMM (Type 3 tests, KR-method) | peripheral SSVEP post-cue modulations")) %>%
  kable_styling("striped", full_width = T, bootstrap_options = c("striped", "hover", "condensed", "responsive",font_size = 8))

lmmmodel2 %>%
  anova()%>%
  tidy()%>%
  left_join(eta_tab, by = c("term" = "Parameter")) %>%
  mutate(
    `p.value` = cell_spec(ifelse(round(`p.value`,4)<.001,"< .001",round(`p.value`,4)), 
                        color = ifelse(is.nan(`p.value`),"blue", ifelse(`p.value` < .05, "green", "red")),
                        bold = ifelse(is.nan(`p.value`),F, ifelse(`p.value` < .05, T,F)),
                        align = "center")
  ) %>%
  dplyr::select(term, num.Df, den.Df, statistic, Eta2_partial, `p.value`) %>%
  kbl(escape = F, digits = c(5,5,5,5,5,5,5,5,5), 
      caption = c("Mixed Model Anova Table (Type 3 tests, KR-method) | peripheral SSVEP post-cue modulations")) %>%
  kable_styling("striped", full_width = T, bootstrap_options = c("striped", "hover", "condensed", "responsive",font_size = 8))



#display main effects via emmeans
# Main effect of RDK_isattended
emm_ATT_lmm <- as.data.frame(emmeans(lmmmodel2, ~ RDK_isattended))

# Main effect of condition_label
emm_Pericondition_lmm <- as.data.frame(emmeans(lmmmodel2, ~ condition_label))

# RDK_isattended plot
# add some more range to the y axis to allow for some more space for error bars and contrasts
y_range <- range(c(emm_ATT_lmm$lower.CL, emm_ATT_lmm$upper.CL))
y_extension <- diff(y_range) * 0.40

saveplot <- ggplot(emm_ATT_lmm, aes(x = RDK_isattended, y = emmean, fill = RDK_isattended)) +
  geom_col(position = position_dodge(), width = 0.6) +
  geom_errorbar(aes(ymin = lower.CL, ymax = upper.CL), width = 0.2) +
  labs(title = "Main Effect of RDK_isattended",
       y = "Estimated Marginal Means (95% CI)", x = "RDK_isattended") +
  theme_light() +
  scale_fill_manual(values=c("#F1831A", "#293C4A", "#198A83"))+
  scale_color_manual(values=c("#F1831A", "#293C4A", "#198A83"))+
  scale_y_continuous(limits = c(y_range[1], y_range[2] + y_extension)) +
  theme(axis.text.x = element_blank())

savefig <- multi_panel_figure(columns = 1, rows = 1, panel_label_type = "none", width = 3.9, height = 3, unit = "in")
savefig %<>%
  fill_panel(saveplot, column = 1, row = 1)
savefig
# save_multi_panel_figure(savefig, "figures/FFT_Peri_MargMeans_ATTENTION.eps")


# condition_label plot
ggplot(emm_Pericondition_lmm, aes(x = condition_label, y = emmean, fill = condition_label)) +
  geom_col(position = position_dodge(), width = 0.6) +
  geom_errorbar(aes(ymin = lower.CL, ymax = upper.CL), width = 0.2) +
  labs(title = "No Main Effect of condition_label",
       y = "Estimated Marginal Means (95% CI)", x = "Condition Label") +
  theme_light() +
  scale_fill_brewer(palette = "Dark2")+
  scale_color_brewer(palette = "Dark2")+
  theme(axis.text.x = element_blank())

# firs test identity contrasts
#post hoc contrasts
post_hocs.RDK_isattended_id <- emmeans(lmmmodel2, c("RDK_isattended"), contr = "identity",adjust = "FDR") # adjust = FDr
post_hocs.condition_label_id <- emmeans(lmmmodel2, c("condition_label"), contr = "identity",adjust = "FDR") # adjust = FDR

# report data for post_hoc attention
post_hocs.RDK_isattended_id%>%
  .$contrasts %>%
  tidy()%>%
  dplyr::rename(t.ratio=statistic, p.value=adj.p.value)%>%
  mutate(
    p.value = cell_spec(ifelse(round(p.value,4)<.001,"< .001",round(p.value,4)), 
                        color = ifelse(is.nan(p.value),"blue", ifelse(p.value < .05, "green", "red")),
                        bold = ifelse(is.nan(p.value),F, ifelse(p.value < .05, T,F)),
                        align = "left")
  ) %>% # mutate(CohensD = `t.ratio`/sqrt(df+1))%>%
  mutate(`CohensD` =
           summary(eff_size(post_hocs.RDK_isattended_id,
                            sigma = sqrt(mean(sigma(lmmmodel2$full_model)^2)), # RMS of sigma()
                            edf = df.residual(lmmmodel2$full_model), method = "identity"))$effect.size,
         `lowCI` =
           summary(eff_size(post_hocs.RDK_isattended_id,
                            sigma = sqrt(mean(sigma(lmmmodel2$full_model)^2)), # RMS of sigma()
                            edf = df.residual(lmmmodel2$full_model), method = "identity"))$lower.CL,
         `highCI` =
           summary(eff_size(post_hocs.RDK_isattended_id,
                            sigma = sqrt(mean(sigma(lmmmodel2$full_model)^2)), # RMS of sigma()
                            edf = df.residual(lmmmodel2$full_model), method = "identity"))$upper.CL
  )%>%
  kbl(escape = F, digits = c(3,3,3,3,3,3,3,3,3), 
      caption = c("estimated marginal means | by ATTENTION | dv = peripheral SSVEP modulation | FDR corrected")) %>%
  kable_styling("striped", full_width = T, bootstrap_options = c("striped", "hover", "condensed", "responsive",font_size = 8))

# report data for post_hoc condition_label
post_hocs.condition_label_id%>%
  .$contrasts %>%
  tidy()%>%
  dplyr::rename(t.ratio=statistic, p.value=adj.p.value)%>%
  mutate(
    p.value = cell_spec(ifelse(round(p.value,4)<.001,"< .001",round(p.value,4)), 
                        color = ifelse(is.nan(p.value),"blue", ifelse(p.value < .05, "green", "red")),
                        bold = ifelse(is.nan(p.value),F, ifelse(p.value < .05, T,F)),
                        align = "left")
  ) %>% # mutate(CohensD = `t.ratio`/sqrt(df+1))%>%
  mutate(`CohensD` =
           summary(eff_size(post_hocs.condition_label_id,
                            sigma = sqrt(mean(sigma(lmmmodel2$full_model)^2)), # RMS of sigma()
                            edf = df.residual(lmmmodel2$full_model), method = "identity"))$effect.size,
         `lowCI` =
           summary(eff_size(post_hocs.condition_label_id,
                            sigma = sqrt(mean(sigma(lmmmodel2$full_model)^2)), # RMS of sigma()
                            edf = df.residual(lmmmodel2$full_model), method = "identity"))$lower.CL,
         `highCI` =
           summary(eff_size(post_hocs.condition_label_id,
                            sigma = sqrt(mean(sigma(lmmmodel2$full_model)^2)), # RMS of sigma()
                            edf = df.residual(lmmmodel2$full_model), method = "identity"))$upper.CL
  )%>%
  kbl(escape = F, digits = c(3,3,3,3,3,3,3,3,3), 
      caption = c("estimated marginal means | by PERI_CON | dv = peripheral SSVEP modulation | FDR corrected")) %>%
  kable_styling("striped", full_width = T, bootstrap_options = c("striped", "hover", "condensed", "responsive",font_size = 8))



#post hoc contrasts
post_hocs.RDK_isattended <- emmeans(lmmmodel2, c("RDK_isattended"), contr = "pairwise",adjust = "FDR") # adjust = holm
post_hocs.condition_label <- emmeans(lmmmodel2, c("condition_label"), contr = "pairwise",adjust = "FDR") # adjust = holm

summary(post_hocs.RDK_isattended$contrasts) %>%
  mutate(
    p.value = cell_spec(ifelse(round(p.value,4)<.001,"< .001",round(p.value,4)), 
                        color = ifelse(is.nan(p.value),"blue", ifelse(p.value < .05, "green", "red")),
                        bold = ifelse(is.nan(p.value),F, ifelse(p.value < .05, T,F)),
                        align = "left")
  ) %>%
  # mutate(CohensD = `t.ratio`/sqrt(df+1))%>%
  mutate(`CohensD` =
           summary(eff_size(post_hocs.RDK_isattended,
                            sigma = sqrt(mean(sigma(lmmmodel2$full_model)^2)), # RMS of sigma()
                            edf = df.residual(lmmmodel2$full_model), method = "pairwise"))$effect.size,
         `lowCI` =
           summary(eff_size(post_hocs.RDK_isattended,
                            sigma = sqrt(mean(sigma(lmmmodel2$full_model)^2)), # RMS of sigma()
                            edf = df.residual(lmmmodel2$full_model), method = "pairwise"))$lower.CL,
         `highCI` =
           summary(eff_size(post_hocs.RDK_isattended,
                            sigma = sqrt(mean(sigma(lmmmodel2$full_model)^2)), # RMS of sigma()
                            edf = df.residual(lmmmodel2$full_model), method = "pairwise"))$upper.CL
  )%>%
  kbl(escape = F, digits = c(3,3,3,3,3,3,3,3,3), 
        caption = c("contrasts for estimated marginal means | by ATTENTION | dv = peripheral SSVEP modulation | corrected: FDR")) %>%
  kable_styling("striped", full_width = T, bootstrap_options = c("striped", "hover", "condensed", "responsive",font_size = 8))

summary(post_hocs.condition_label$contrasts) %>%
  mutate(
    p.value = cell_spec(ifelse(round(p.value,4)<.001,"< .001",round(p.value,4)), 
                        color = ifelse(is.nan(p.value),"blue", ifelse(p.value < .05, "green", "red")),
                        bold = ifelse(is.nan(p.value),F, ifelse(p.value < .05, T,F)),
                        align = "left")
  ) %>%
  # mutate(CohensD = `t.ratio`/sqrt(df+1))%>%
  mutate(`CohensD` =
           summary(eff_size(post_hocs.condition_label,
                            sigma = sqrt(mean(sigma(lmmmodel2$full_model)^2)), # RMS of sigma()
                            edf = df.residual(lmmmodel2$full_model), method = "pairwise"))$effect.size,
         `lowCI` =
           summary(eff_size(post_hocs.condition_label,
                            sigma = sqrt(mean(sigma(lmmmodel2$full_model)^2)), # RMS of sigma()
                            edf = df.residual(lmmmodel2$full_model), method = "pairwise"))$lower.CL,
         `highCI` =
           summary(eff_size(post_hocs.condition_label,
                            sigma = sqrt(mean(sigma(lmmmodel2$full_model)^2)), # RMS of sigma()
                            edf = df.residual(lmmmodel2$full_model), method = "pairwise"))$upper.CL
  )%>%
  kbl(escape = F, digits = c(3,3,3,3,3,3,3,3,3), 
        caption = c("contrasts for estimated marginal means | by PERI_CON | dv = peripheral SSVEP modulation | corrected: FDR")) %>%
  kable_styling("striped", full_width = T, bootstrap_options = c("striped", "hover", "condensed", "responsive",font_size = 8))




# pairs(emmeans(aovmodel2, ~ RDK_isattended))
# pairs(emmeans(aovmodel2, ~ condition_label))
```


## Additional post-hoc analysis

direct contrast of unattended colors in periphery when presented with attended vs irrelevant color
t-test and Bayesian t-test

```{r Stat perip stimuli II, message=FALSE, warning=FALSE, include=TRUE}
dat2plot <- DataIn %>%
  filter(RDK_position2=="peri") %>%
  filter(RDK_ispresented=="presented")%>%
  filter(RDK_colorlum=="isolum__to_bckgrd")%>%
  group_by(subjects, time, RDK_isattended2)%>%
  summarise(amplitude_evoked=mean(amplitude_evoked), modulation_evoked=mean(modulation_evoked))%>%
  filter(time == '[0.5 1.5] ')


dat2plot %>%
  dplyr::select(-amplitude_evoked)%>%
  pivot_wider(names_from = "RDK_isattended2", values_from = "modulation_evoked")%>%
  mutate(`notattended-attMINUSirre` = `not attended + attended` -`not attended + irrelevant`)%>%
  dplyr::select(-c(`attended + irrelevant`:`not attended + irrelevant`))%>%
  pivot_longer(cols=`notattended-attMINUSirre`, names_to = "contrast", values_to = "amplitude")%>%
  group_by(contrast)%>%
  nest()%>%
  mutate(stats = map(data, ~broom::tidy(
    t.test(amplitude ~ 1, data = .)
  ))) %>%
  mutate(
    t_test_bf = map(data, ~{extractBF(ttestBF(x = .$amplitude, data = .,iterations=num.iter,rscale = sqrt(2)/2))})
  )%>%
  mutate(meanval = map(data, ~ mean(.x$amplitude))) %>%
  mutate(std = map(data, ~ sd(.x$amplitude))) %>%
  ungroup()%>%
  dplyr::select(-data) %>%
  ungroup()%>%
  unnest(cols = c(stats, t_test_bf, meanval, std))%>%
  mutate(BF10 = bf, BF01 = 1/bf)%>%
  dplyr::select( contrast, meanval, std,  statistic, parameter, p.value, BF10, BF01)%>%
  mutate(p.value = p.adjust(p.value, method="fdr")) %>% # none, holm
  # mutate(p.value = p.adjust(p.value, method="none")) %>% # none, holm
  ungroup()%>%
  mutate(CohensD = `statistic`/sqrt(parameter +1))%>%
  mutate(
    p.value = cell_spec(ifelse(round(p.value,4)<.001,"< .001",round(p.value,4)), 
                        color = ifelse(is.nan(p.value),"blue", ifelse(p.value < .05, "green", "red")),
                        bold = ifelse(is.nan(p.value),F, ifelse(p.value < .05, T,F)),
                        align = "center")
  ) %>%
  kbl(escape = F, digits = c(3,3,3,3,3,3,3,3,3), caption = c("peripheral SSVEP | modulation | contrasts fdr-corrected")) %>%
  kable_styling("striped", full_width = T, bootstrap_options = c("striped", "hover", "condensed", "responsive",font_size = 8))

```


## Additional post-hoc analysis II

show different pre-cue and post-cue amplitude values for central stimuli

```{r amplitudes, message=FALSE, warning=FALSE, include=TRUE, fig.height=4, fig.width=6}
dat2plot <- DataIn %>%
  filter(RDK_position2=="center", RDK_colorlum=="isolum__to_bckgrd") %>%
  mutate(condition_label = case_when(
    condition %in% c(1,2) ~ "Att+Unatt",
    condition %in% c(3,4) ~ "Att+Diff",
    condition %in% c(5,6) ~ "Unatt+Diff"
  ))%>%
  group_by(subjects, time, RDK_isattended, condition_label)%>%
  summarise(amplitude_evoked=mean(amplitude_evoked), modulation_evoked=mean(modulation_evoked))%>%
  filter(time != '[1 2] ')

# set overall limits?
# set limits
yax_limits <- c( min(dat2plot$amplitude_evoked), max(dat2plot$amplitude_evoked))
yax_limits <- round(yax_limits + c(-1, 1)*diff(yax_limits)*0.1)
yax_limits <- yax_limits + c(-1, 1)*diff(yax_limits)*0.1

plot1 <- dat2plot %>%
  filter(time == '[-1 0] ')%>%
  ggplot(., aes(x = RDK_isattended, y = amplitude_evoked, color =RDK_isattended)) +
  # geom_hline(yintercept=0, show.legend = FALSE) +
  geom_beeswarm(cex=3, size = 3, shape=21,fill="grey40", alpha=1)+
  stat_summary(fun.y=mean, aes(ymin=..y.., ymax=..y..), geom='errorbar', width=0.9, size=1.5) +
  scale_fill_manual(values=c("#F03F3F", "steelblue2"))+
  scale_color_manual(values=c("#F03F3F", "steelblue2"))+
  ylab(expression(paste("amplitude in ", mu, "V/m²")))+
  facet_grid(.~condition_label) +
  theme_bw()+
  theme(axis.title.x=element_blank(),
         axis.text.x=element_blank(),
         axis.ticks.x=element_blank())+
  ggtitle("pre-cue time window") +
  scale_y_continuous(limits=yax_limits)

plot2 <- dat2plot %>%
  filter(time == '[0.5 1.5] ')%>%
  ggplot(., aes(x = RDK_isattended, y = amplitude_evoked, color =RDK_isattended)) +
  # geom_hline(yintercept=0, show.legend = FALSE) +
  geom_beeswarm(cex=3, size = 3, shape=21,fill="grey40", alpha=1)+
  stat_summary(fun.y=mean, aes(ymin=..y.., ymax=..y..), geom='errorbar', width=0.9, size=1.5) +
  scale_fill_manual(values=c("#F03F3F", "steelblue2"))+
  scale_color_manual(values=c("#F03F3F", "steelblue2"))+
  ylab(expression(paste("amplitude in ", mu, "V/m²")))+
  facet_grid(.~condition_label) +
  theme_bw()+
  theme(axis.title.x=element_blank(),
         axis.text.x=element_blank(),
         axis.ticks.x=element_blank())+
  ggtitle("post-cue time window")+
  scale_y_continuous(limits=yax_limits)


# cowplot::plot_grid(plot1, plot2, plot3, ncol = 3,labels = "AUTO")
plotttitle <- ggdraw() + draw_label("SSVEP amplitudes", fontface='bold')
plotplots <- ggarrange(plot1, plot2, ncol = 2,common.legend = TRUE,align = "h", widths=c(1,1))

savefig <- multi_panel_figure(columns = 1, rows = 1, panel_label_type = "none", width = 6, height = 4, unit = "in")
saveplot <- ggarrange(plotttitle, plotplots, nrow = 2, heights=c(0.2, 1))

savefig %<>%
  fill_panel(saveplot, column = 1, row = 1)
savefig

ggsave(filename = "figures/SSVEP_Amps_Central.eps", width = 6, height = 4,plot = print(savefig))
```

## Additional post-hoc analysis III

show different pre-cue and post-cue amplitude values for peripheral stimuli

```{r amplitudes, message=FALSE, warning=FALSE, include=TRUE, fig.height=4, fig.width=4}
dat2plot <- DataIn %>%
  filter(RDK_position2=="peri", RDK_colorlum=="isolum__to_bckgrd") %>%
  group_by(subjects, time, RDK_isattended)%>%
  summarise(amplitude_evoked=mean(amplitude_evoked), modulation_evoked=mean(modulation_evoked))%>%
  filter(time != '[1 2] ')

# set overall limits?
# set limits
yax_limits <- c( min(dat2plot$amplitude_evoked), max(dat2plot$amplitude_evoked))
yax_limits <- round(yax_limits + c(-1, 1)*diff(yax_limits)*0.1)
yax_limits <- yax_limits + c(-1, 1)*diff(yax_limits)*0.1

plot1 <- dat2plot %>%
  filter(time == '[-1 0] ')%>%
  ggplot(., aes(x = RDK_isattended, y = amplitude_evoked, color =RDK_isattended)) +
  # geom_hline(yintercept=0, show.legend = FALSE) +
  geom_beeswarm(cex=3, size = 3, shape=21,fill="grey40", alpha=1)+
  stat_summary(fun.y=mean, aes(ymin=..y.., ymax=..y..), geom='errorbar', width=0.9, size=1.5) +
  scale_fill_manual(values=c("#F03F3F", "#293C4A","steelblue2"))+
  scale_color_manual(values=c("#F03F3F", "#293C4A","steelblue2"))+
  ylab(expression(paste("amplitude in ", mu, "V/m²")))+
  # facet_grid(.~condition_label) +
  theme_bw()+
  theme(axis.title.x=element_blank(),
         axis.text.x=element_blank(),
         axis.ticks.x=element_blank())+
  ggtitle("pre-cue window") +
  scale_y_continuous(limits=yax_limits)

plot2 <- dat2plot %>%
  filter(time == '[0.5 1.5] ')%>%
  ggplot(., aes(x = RDK_isattended, y = amplitude_evoked, color =RDK_isattended)) +
  # geom_hline(yintercept=0, show.legend = FALSE) +
  geom_beeswarm(cex=3, size = 3, shape=21,fill="grey40", alpha=1)+
  stat_summary(fun.y=mean, aes(ymin=..y.., ymax=..y..), geom='errorbar', width=0.9, size=1.5) +
  scale_fill_manual(values=c("#F03F3F", "#293C4A","steelblue2"))+
  scale_color_manual(values=c("#F03F3F", "#293C4A","steelblue2"))+
  ylab(expression(paste("amplitude in ", mu, "V/m²")))+
  # facet_grid(.~condition_label) +
  theme_bw()+
  theme(axis.title.x=element_blank(),
         axis.text.x=element_blank(),
         axis.ticks.x=element_blank())+
  ggtitle("post-cue window")+
  scale_y_continuous(limits=yax_limits)


# cowplot::plot_grid(plot1, plot2, plot3, ncol = 3,labels = "AUTO")
plotttitle <- ggdraw() + draw_label("SSVEP amplitudes", fontface='bold')
plotplots <- ggarrange(plot1, plot2, ncol = 2,common.legend = TRUE,align = "h", widths=c(1,1))

savefig <- multi_panel_figure(columns = 1, rows = 1, panel_label_type = "none", width = 4, height = 4, unit = "in")
saveplot <- ggarrange(plotttitle, plotplots, nrow = 2, heights=c(0.2, 1))

savefig %<>%
  fill_panel(saveplot, column = 1, row = 1)
savefig

```
## Additional post-hoc analysis IIIb

show different pre-cue and post-cue amplitude values for peripheral stimuli

```{r amplitudes, message=FALSE, warning=FALSE, include=TRUE, fig.height=4, fig.width=6}
dat2plot <- DataIn %>%
  mutate(condition2 = case_when(
    condition %in% c(1,2) ~ "Att+Unatt",
    condition %in% c(3,4) ~ "Att+Diff",
    condition %in% c(5,6) ~ "Unatt+Diff"
  )) %>%
  filter(RDK_position2=="peri") %>%
  filter(RDK_ispresented=="presented")%>%
  group_by(subjects, time, RDK_isattended, RDK_colorlum, condition2)%>%
  summarise(amplitude_evoked=mean(amplitude_evoked), modulation_evoked=mean(modulation_evoked))%>%
  filter(RDK_colorlum == 'isolum__to_bckgrd')
# set overall limits?
# set limits
yax_limits <- c( min(dat2plot$amplitude_evoked), max(dat2plot$amplitude_evoked))
yax_limits <- round(yax_limits + c(-1, 1)*diff(yax_limits)*0.1)
yax_limits <- yax_limits + c(-1, 1)*diff(yax_limits)*0.1


theme_set(theme_bw())
plot1 <- dat2plot %>%
  filter(time == '[-1 0] ')%>%
  ggplot(., aes(x = RDK_isattended, y = amplitude_evoked, fill = RDK_isattended)) +
  # geom_hline(yintercept=0, show.legend = FALSE) +
  # geom_line(aes(group = interaction(subjects,time)),colour = "grey60",alpha = 1,size =0.5) +
  geom_beeswarm(aes(color = RDK_isattended, x = RDK_isattended,
                    group = RDK_isattended), cex=3, size = 3,alpha=1,fill="grey40",shape=21)+
  # geom_point(aes(color = RDK_isattended, x = interaction(time,RDK_isattended),
  #                   group = RDK_isattended), size = 4,alpha=0.4)+
  stat_summary(fun.y=mean, aes(ymin=..y.., ymax=..y.., color =RDK_isattended), geom='errorbar', width=0.9, size=1.5) +
  theme(axis.title.x=element_blank(),
         axis.text.x=element_blank(),
         axis.ticks.x=element_blank())+
  # theme(legend.position="bottom") +
  facet_grid(.~condition2)+
  ylab(expression(paste("amplitude in ", mu, "V/m²")))+
  # scale_fill_manual(values=c("#F1831A", "#293C4A", "#198A83"))+
  # scale_color_manual(values=c("#F1831A", "#293C4A", "#198A83"))+
  scale_fill_manual(values=c("#F03F3F", "#293C4A","steelblue2"))+
  scale_color_manual(values=c("#F03F3F", "#293C4A","steelblue2"))+
  ggtitle("pre-cue time window") +
  scale_y_continuous(limits=yax_limits)

plot2 <- dat2plot %>%
  filter(time == '[0.5 1.5] ')%>%
  ggplot(., aes(x = RDK_isattended, y = amplitude_evoked, fill = RDK_isattended)) +
  # geom_hline(yintercept=0, show.legend = FALSE) +
  # geom_line(aes(group = interaction(subjects,time)),colour = "grey60",alpha = 1,size =0.5) +
  geom_beeswarm(aes(color = RDK_isattended, x = RDK_isattended,
                    group = RDK_isattended), cex=3, size = 3,alpha=1,fill="grey40",shape=21)+
  # geom_point(aes(color = RDK_isattended, x = interaction(time,RDK_isattended),
  #                   group = RDK_isattended), size = 4,alpha=0.4)+
  stat_summary(fun.y=mean, aes(ymin=..y.., ymax=..y.., color =RDK_isattended), geom='errorbar', width=0.9, size=1.5) +
  # scale_x_discrete("RDK_isattended", breaks=waiver(), labels = rep(c(""),1,3)) +
  theme(axis.title.x=element_blank(),
         axis.text.x=element_blank(),
         axis.ticks.x=element_blank())+
  # theme(legend.position="bottom") +
  facet_grid(.~condition2)+
  ylab(expression(paste("amplitude in ", mu, "V/m²")))+
  # scale_fill_manual(values=c("#F1831A", "#293C4A", "#198A83"))+
  # scale_color_manual(values=c("#F1831A", "#293C4A", "#198A83"))+
  scale_fill_manual(values=c("#F03F3F", "#293C4A","steelblue2"))+
  scale_color_manual(values=c("#F03F3F", "#293C4A","steelblue2"))+
  ggtitle("post-cue time window") +
  scale_y_continuous(limits=yax_limits)

plotttitle <- ggdraw() + draw_label("SSVEP amplitudes", fontface='bold')
plotplots <- ggarrange(plot1, plot2, ncol = 2,common.legend = TRUE,align = "h", widths=c(1,1))

savefig <- multi_panel_figure(columns = 1, rows = 1, panel_label_type = "none", width = 6, height = 4, unit = "in")
saveplot <- ggarrange(plotttitle, plotplots, nrow = 2, heights=c(0.2, 1))

savefig %<>%
  fill_panel(saveplot, column = 1, row = 1)
savefig

ggsave(filename = "figures/SSVEP_Amps_Periphery.eps", width = 6, height = 4,plot = print(savefig))
  
```


