---
title: "FFT_SSVEP_analysis"
author: "Christopher"
date: "2 7 2024"
output:
  html_document:
    code_folding: hide
    toc: true
    toc_float: true
    toc_depth: 4
    theme: flatly
---

Modelling of ~~raw~~ [*CSD based*] amplitude values from fft-based data
via linear mixed models
via standard anova models

```{r load_package, message = FALSE, warning = FALSE}
rm(list=ls()) # clear environment
library(lme4)
library(readxl)
library(tidyverse)
library(data.table)
library(tidyverse)
library(afex)
library(broom)
library(apa)
library(kableExtra)
library(lmerTest)
library(pbkrtest)
library(effects)
library(visreg)
library(sjPlot)
library(broom.mixed)
library(pander)
library(mediation)
library(multcomp)
library(multcompView)
library(magrittr)
library(multipanelfigure)
library(ggbeeswarm)
library(lsmeans)
library(BayesFactor)
library(ggpubr)
library(gpairs)
library(DescTools)
library(cowplot)
library(ggpol)
library(logspline)

library(brms)

library(bayestestR)

source('C:/Dropboxdata/Dropbox/work/R-statistics/general_functions/RainCloudPlots/tutorial_R/R_rainclouds.R')
source('C:/Dropboxdata/Dropbox/work/R-statistics/general_functions/RainCloudPlots/tutorial_R/R_rainclouds.R')

source('C:/Dropboxdata/Dropbox/work/R-statistics/examples/Bayesian_rank-based_hypothesis_testing/rankBasedCommonFunctions.R')
source('C:/Dropboxdata/Dropbox/work/R-statistics/examples/Bayesian_rank-based_hypothesis_testing/rankSumSampler.R') # Wilcoxon rank sum function
source('C:/Dropboxdata/Dropbox/work/R-statistics/examples/Bayesian_rank-based_hypothesis_testing/signRankSampler.R') # Wilcoxon signed-rank function
source('C:/Dropboxdata/Dropbox/work/R-statistics/examples/Bayesian_rank-based_hypothesis_testing/spearmanSampler.R')# Spearman's rho function




# broad cluster
# CSD based normalized to pre-cue baseline in %
#  
DATAPath = "data_in/FFT_Amp_data_largeclust_06-14-2024_13-19.csv"
t_baseline = c(-1000, 0)


# broad cluster | smaller central cluster
# CSD based normalized to pre-cue baseline in %
#  
# DATAPath = "data_in/FFT_Amp_data_largeclust_06-24-2024_15-43.csv"
# t_baseline = c(-1000, 0)


# broad cluster | smaller central cluster
# CSD based normalized to pre-cue baseline in %
# for changed experiment starting with participant 22: isoluminant stimuli and lower flicker frequencies
#  
DATAPath = "data_in/FFT_Amp_data_largeclust_allsubs_08-30-2024_11-21.csv"
t_baseline = c(-1000, 0)


# broad cluster | larger central cluster |
# peri: not correct!
# CSD based normalized to pre-cue baseline in %
# for changed experiment starting with participant 22: isoluminant stimuli and lower flicker frequencies
#  
# DATAPath = "data_in/FFT_Amp_data_pericenter_allsubs_07-02-2024_11-46.csv"
# t_baseline = c(-1000, 0)
# 
# broad cluster | very broad central cluster
# CSD based normalized to pre-cue baseline in %
# for changed experiment starting with participant 22: isoluminant stimuli and lower flicker frequencies
# # 
# DATAPath = "data_in/FFT_Amp_data_largecenterclust_allsubs_09-11-2024_14-45.csv"
# t_baseline = c(-1000, 0)



#!!!!!!! relevant
# broad cluster | larger central cluster as in Tango study | peri both clusters but smaller
# CSD based normalized to pre-cue baseline in %
# for changed experiment starting with participant 22: isoluminant stimuli and lower flicker frequencies
DATAPath = "data_in/FFT_Amp_data_CenterTangoStudyPeriSmall_05-23-2025_11-56.csv"
t_baseline = c(-1000, 0)

# broad cluster | larger central cluster as in Tango study | peri only center
# DATAPath = "data_in/FFT_Amp_data_TangoStudyPeriOnlyCenter_11-25-2024_14-17.csv"
# t_baseline = c(-1000, 0)

# # broad cluster | larger central cluster as in Tango study | peri only lateral | in this study shows gain for attended
# DATAPath = "data_in/FFT_Amp_data_TangoStudyPeriOnlyLateral_11-25-2024_14-17.csv"
# t_baseline = c(-1000, 0)


#!!!!!!!


# replication relevant
# broad cluster | larger central cluster as in Tango study | peri both clusters as in Tango study
# CSD based normalized to pre-cue baseline in %
# for changed experiment starting with participant 22: isoluminant stimuli and lower flicker frequencies
# DATAPath = "data_in/FFT_Amp_data_TangoStudy_05-23-2025_11-53.csv"
# t_baseline = c(-1000, 0)




options(scipen=1, digits=7)
```
<style type="text/css">
.main-container {
max-width: 1800px !important;
margin-left: auto;
margin-right: auto;
}
</style>


## Prepare data  
<br>  

1.  Read in data: 
+ `r DATAPath`
+ with pre-cue  [`r toString(t_baseline)`] ms

<br>  

```{r load_data,results = "hide", fig.show = "hide", warning = FALSE}
sub_sample = c(0)
# sub_sample = as.factor(c(26,30, 31,37, 38)) # no ssvep people discarded
sub_sample = as.factor(c(42)) # low trial number


# read in data
DataIn <- read.csv(DATAPath, sep = ";") %>%
  mutate(subjects = as.factor(subjects))%>%
  filter(!subjects %in% sub_sample)
head(DataIn)
str(DataIn)
```
## Illustrate SSVEP Data

### 1a  Illustrate Data as is | center RDKs

<br>  

```{r plot_data_st_center, results = "hide",  fig.height=3, fig.width=4, warning = FALSE}
#evoked raw#### for center
dat2plot <- DataIn %>%
  filter(RDK_position2=="center") %>%
  group_by(subjects, time, RDK_isattended, RDK_colorlum)%>%
  summarise(amplitude_evoked=mean(amplitude_evoked), modulation_evoked=mean(modulation_evoked), subtraction_evoked=mean(subtraction_evoked))

theme_set(theme_bw())
ggplot(dat2plot, aes(x = interaction(time,RDK_isattended), y = amplitude_evoked, fill = RDK_isattended)) +
  # geom_hline(yintercept=0, show.legend = FALSE) +
  geom_line(aes(group = interaction(subjects,RDK_isattended)),colour = "grey60",alpha = 0.5,size =0.5) +
  geom_beeswarm(aes(color = RDK_isattended, x = interaction(time,RDK_isattended),
                    group = RDK_isattended), cex=2, size = 3,alpha=1,fill="grey40",shape=21)+
  # geom_point(aes(color = condition, x = interaction(time,condition),
  #                   group = condition), size = 4,alpha=0.4)+
  stat_summary(fun.y=mean, aes(ymin=..y.., ymax=..y.., color =RDK_isattended), geom='errorbar', width=0.9, size=1.5) +
  scale_x_discrete("time windows in s", breaks=waiver(), labels = rep(c("[-1 0]","[0.5 1.5]","[1 2]"),1,6)) +
  facet_grid(.~RDK_colorlum)+
  theme(legend.position="bottom") +
  ylab(expression(paste("amplitude in muV/cm²")))+
  labs(title=sprintf("SSVEP amplitudes | evoked"),
       subtitle="collapsed across frequencies")+
  scale_fill_brewer(palette = "Dark2")+
  scale_color_brewer(palette = "Dark2")


theme_set(theme_bw())
ggplot(dat2plot, aes(x = interaction(time,RDK_isattended), y = modulation_evoked, fill = RDK_isattended)) +
  # geom_hline(yintercept=0, show.legend = FALSE) +
  geom_line(aes(group = interaction(subjects,RDK_isattended)),colour = "grey60",alpha = 0.5,size =0.5) +
  geom_beeswarm(aes(color = RDK_isattended, x = interaction(time,RDK_isattended),
                    group = RDK_isattended), cex=2, size = 3,alpha=1,fill="grey40",shape=21)+
  # geom_point(aes(color = condition, x = interaction(time,condition),
  #                   group = condition), size = 4,alpha=0.4)+
  stat_summary(fun.y=mean, aes(ymin=..y.., ymax=..y.., color =RDK_isattended), geom='errorbar', width=0.9, size=1.5) +
  scale_x_discrete("time windows in s", breaks=waiver(), labels = rep(c("[-1 0]","[0.5 1.5]","[1 2]"),1,6)) +
  facet_grid(.~RDK_colorlum)+
  theme(legend.position="bottom") +
  ylab(expression(paste("modulation in %")))+
  labs(title=sprintf("SSVEP amplitudes | evoked"),
       subtitle="collapsed across frequencies")+
  scale_fill_brewer(palette = "Dark2")+
  scale_color_brewer(palette = "Dark2")

theme_set(theme_bw())
ggplot(dat2plot, aes(x = interaction(time,RDK_isattended), y = subtraction_evoked, fill = RDK_isattended)) +
  # geom_hline(yintercept=0, show.legend = FALSE) +
  geom_line(aes(group = interaction(subjects,RDK_isattended)),colour = "grey60",alpha = 0.5,size =0.5) +
  geom_beeswarm(aes(color = RDK_isattended, x = interaction(time,RDK_isattended),
                    group = RDK_isattended), cex=2, size = 3,alpha=1,fill="grey40",shape=21)+
  # geom_point(aes(color = condition, x = interaction(time,condition),
  #                   group = condition), size = 4,alpha=0.4)+
  stat_summary(fun.y=mean, aes(ymin=..y.., ymax=..y.., color =RDK_isattended), geom='errorbar', width=0.9, size=1.5) +
  scale_x_discrete("time windows in s", breaks=waiver(), labels = rep(c("[-1 0]","[0.5 1.5]","[1 2]"),1,6)) +
  facet_grid(.~RDK_colorlum)+
  theme(legend.position="bottom") +
  ylab(expression(paste("amplitude diff in muV/cm²")))+
  labs(title=sprintf("SSVEP amplitudes | evoked"),
       subtitle="collapsed across frequencies")+
  scale_fill_brewer(palette = "Dark2")+
  scale_color_brewer(palette = "Dark2")
```
### 1b  Illustrate Data as is | center RDKs

plot differently

<br>  

```{r plot_data_st_center_2, results = "hide",  fig.height=5, fig.width=3.5, warning = FALSE}
#evoked raw#### for center

# set overall limits?
dat2plot <- DataIn %>%
  filter(RDK_position2=="center") %>%
  group_by(subjects, time, RDK_isattended, RDK_colorlum)%>%
  summarise(amplitude_evoked=mean(amplitude_evoked), modulation_evoked=mean(modulation_evoked))%>%
  filter(time=='[0.5 1.5] ')
# set limits
yax_limits <- c( min(dat2plot$modulation_evoked), max(dat2plot$modulation_evoked))
yax_limits <- round(yax_limits + c(-1, 1)*diff(yax_limits)*0.1)
yax_limits <- yax_limits + c(-1, 1)*diff(yax_limits)*0.1


dat2plot <- DataIn %>%
  filter(RDK_position2=="center") %>%
  group_by(subjects, time, RDK_isattended, RDK_colorlum)%>%
  summarise(amplitude_evoked=mean(amplitude_evoked), modulation_evoked=mean(modulation_evoked))%>%
  filter(time=='[0.5 1.5] ', RDK_colorlum == 'offset_to_bckgrd')

# set limits
# yax_limits <- c( min(dat2plot$modulation_evoked), max(dat2plot$modulation_evoked))
# yax_limits <- round(yax_limits + c(-1, 1)*diff(yax_limits)*0.1)
# yax_limits <- yax_limits + c(-1, 1)*diff(yax_limits)*0.2
# # yax_limits <- c(-27, 15)

theme_set(theme_bw())
plot1 <- ggplot(dat2plot, aes(x = RDK_isattended, y = modulation_evoked, fill = RDK_isattended)) +
  geom_hline(yintercept=0, show.legend = FALSE) +
  geom_line(aes(group = interaction(subjects,time)),colour = "grey60",alpha = 1,size =0.5) +
  geom_beeswarm(aes(color = RDK_isattended, x = RDK_isattended,
                    group = RDK_isattended), cex=3, size = 5,alpha=1,fill="grey40",shape=21)+
  # geom_point(aes(color = RDK_isattended, x = interaction(time,RDK_isattended),
  #                   group = RDK_isattended), size = 4,alpha=0.4)+
  stat_summary(fun.y=mean, aes(ymin=..y.., ymax=..y.., color =RDK_isattended), geom='errorbar', width=0.9, size=1.5) +
  scale_x_discrete("RDK_isattended", breaks=waiver(), labels = rep(c(""),1,2)) +
  # theme(legend.position="bottom") +
  ylab(expression(paste("amplitude modulation in %")))+
  scale_fill_manual(values=c("steelblue2", "#F03F3F"))+
  scale_color_manual(values=c("steelblue2", "#F03F3F"))+
  #  scale_fill_manual(values=c("#193A3D", "#F03F3F"))+
  # scale_color_manual(values=c("#193A3D", "#F03F3F"))+
  # scale_fill_manual(values=c(rgb2hex(0.0, 153.0, 204.0),rgb2hex(0.0, 77, 102.0)))+
  # scale_color_manual(values=c(rgb2hex(0.0, 153.0, 204.0),rgb2hex(0.0, 77, 102.0)))+
  theme(legend.position="none")+
  # scale_y_continuous(limits=c(-60, 140))
  scale_y_continuous(limits=yax_limits)


plot2 <- ggplot(dat2plot, aes(y = modulation_evoked, fill = RDK_isattended, x = 1)) +
  geom_flat_violin(aes(fill = RDK_isattended),position = position_nudge(x = .1, y = 0), 
                   adjust = 1.3, trim = FALSE, alpha = 1, colour = NA)+
  geom_hline(yintercept=0, show.legend = FALSE) +
  # scale_fill_manual(values=c("#193A3D", "#F03F3F"))+
  # scale_color_manual(values=c("#193A3D", "#F03F3F"))+
  scale_fill_manual(values=c("steelblue2", "#F03F3F"))+
  scale_color_manual(values=c("steelblue2", "#F03F3F"))+
  # scale_fill_manual(values=c(rgb2hex(0.0, 153.0, 204.0),rgb2hex(0.0, 77, 102.0)))+
  # scale_color_manual(values=c(rgb2hex(0.0, 153.0, 204.0),rgb2hex(0.0, 77, 102.0)))+
  theme(axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank())+
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+
  # scale_y_continuous(limits=c(-60, 140))
  scale_y_continuous(limits=yax_limits)



# cowplot::plot_grid(plot1, plot2, plot3, ncol = 3,labels = "AUTO")
plotttitle <- ggdraw() + 
  draw_label("SSVEP mod. | evoked \ncentral RDKs | luminance offset", fontface='bold', size = 10)
plotplots <- ggarrange(plot1, plot2,ncol = 2,common.legend = TRUE,align = "h", widths=c(3,1))

savefig <- multi_panel_figure(columns = 1, rows = 1, panel_label_type = "none", width = 3.5, height = 5, unit = "in")
saveplot <- ggarrange(plotttitle, plotplots, nrow = 2, heights=c(0.2, 1))

savefig %<>%
  fill_panel(saveplot, column = 1, row = 1)
savefig
# save_multi_panel_figure(savefig, "figures/FFT_BeeSwarm_Mod_ALPHA_COL_34subs.eps")




dat2plot <- DataIn %>%
  filter(RDK_position2=="center") %>%
  group_by(subjects, time, RDK_isattended, RDK_colorlum)%>%
  summarise(amplitude_evoked=mean(amplitude_evoked), modulation_evoked=mean(modulation_evoked))%>%
  filter(time=='[0.5 1.5] ', RDK_colorlum == 'isolum__to_bckgrd')


# set limits
# yax_limits <- c( min(dat2plot$modulation_evoked), max(dat2plot$modulation_evoked))
# yax_limits <- round(yax_limits + c(-1, 1)*diff(yax_limits)*0.1)
# yax_limits <- yax_limits + c(-1, 1)*diff(yax_limits)*0.2
# # yax_limits <- c(-27, 15)

theme_set(theme_bw())
plot1 <- ggplot(dat2plot, aes(x = RDK_isattended, y = modulation_evoked, fill = RDK_isattended)) +
  geom_hline(yintercept=0, show.legend = FALSE) +
  geom_line(aes(group = interaction(subjects,time)),colour = "grey60",alpha = 1,size =0.5) +
  geom_beeswarm(aes(color = RDK_isattended, x = RDK_isattended,
                    group = RDK_isattended), cex=3, size = 5,alpha=1,fill="grey40",shape=21)+
  # geom_point(aes(color = RDK_isattended, x = interaction(time,RDK_isattended),
  #                   group = RDK_isattended), size = 4,alpha=0.4)+
  stat_summary(fun.y=mean, aes(ymin=..y.., ymax=..y.., color =RDK_isattended), geom='errorbar', width=0.9, size=1.5) +
  scale_x_discrete("RDK_isattended", breaks=waiver(), labels = rep(c(""),1,2)) +
  # theme(legend.position="bottom") +
  ylab(expression(paste("amplitude modulation in %")))+
  scale_fill_manual(values=c("steelblue2", "#F03F3F"))+
  scale_color_manual(values=c("steelblue2", "#F03F3F"))+
  #  scale_fill_manual(values=c("#193A3D", "#F03F3F"))+
  # scale_color_manual(values=c("#193A3D", "#F03F3F"))+
  # scale_fill_manual(values=c(rgb2hex(0.0, 153.0, 204.0),rgb2hex(0.0, 77, 102.0)))+
  # scale_color_manual(values=c(rgb2hex(0.0, 153.0, 204.0),rgb2hex(0.0, 77, 102.0)))+
  theme(legend.position="none")+
  # scale_y_continuous(limits=c(-60, 140))
  scale_y_continuous(limits=yax_limits)


plot2 <- ggplot(dat2plot, aes(y = modulation_evoked, fill = RDK_isattended, x = 1)) +
  geom_flat_violin(aes(fill = RDK_isattended),position = position_nudge(x = .1, y = 0), 
                   adjust = 1.3, trim = FALSE, alpha = 1, colour = NA)+
  geom_hline(yintercept=0, show.legend = FALSE) +
  # scale_fill_manual(values=c("#193A3D", "#F03F3F"))+
  # scale_color_manual(values=c("#193A3D", "#F03F3F"))+
  scale_fill_manual(values=c("steelblue2", "#F03F3F"))+
  scale_color_manual(values=c("steelblue2", "#F03F3F"))+
  # scale_fill_manual(values=c(rgb2hex(0.0, 153.0, 204.0),rgb2hex(0.0, 77, 102.0)))+
  # scale_color_manual(values=c(rgb2hex(0.0, 153.0, 204.0),rgb2hex(0.0, 77, 102.0)))+
  theme(axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank())+
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+
  # scale_y_continuous(limits=c(-60, 140))
  scale_y_continuous(limits=yax_limits)



# cowplot::plot_grid(plot1, plot2, plot3, ncol = 3,labels = "AUTO")
plotttitle <- ggdraw() + 
  draw_label("SSVEP mod. | evoked \ncentral RDKs | isoluminant to background", fontface='bold', size = 10)
plotplots <- ggarrange(plot1, plot2,ncol = 2,common.legend = TRUE,align = "h", widths=c(3,1))

savefig <- multi_panel_figure(columns = 1, rows = 1, panel_label_type = "none", width = 3.5, height = 5, unit = "in")
saveplot <- ggarrange(plotttitle, plotplots, nrow = 2, heights=c(0.2, 1))

savefig %<>%
  fill_panel(saveplot, column = 1, row = 1)
savefig
# save_multi_panel_figure(savefig, "figures/FFT_BeeSwarm_Mod_ALPHA_COL_34subs.eps")



dat2plot <- DataIn %>%
  filter(RDK_position2=="center") %>%
  group_by(subjects, time, RDK_isattended, RDK_colorlum)%>%
  summarise(amplitude_evoked=mean(amplitude_evoked), modulation_evoked=mean(modulation_evoked), subtraction_evoked = mean(subtraction_evoked))%>%
  filter(time=='[0.5 1.5] ', RDK_colorlum == 'isolum__to_bckgrd')


# set limits
yax_limits <- c( min(dat2plot$subtraction_evoked), max(dat2plot$subtraction_evoked))
# yax_limits <- round(yax_limits + c(-1, 1)*diff(yax_limits)*0.1)
yax_limits <- yax_limits + c(-1, 1)*diff(yax_limits)*0.2
# # yax_limits <- c(-27, 15)

theme_set(theme_bw())
plot1 <- ggplot(dat2plot, aes(x = RDK_isattended, y = subtraction_evoked, fill = RDK_isattended)) +
  geom_hline(yintercept=0, show.legend = FALSE) +
  geom_line(aes(group = interaction(subjects,time)),colour = "grey60",alpha = 1,size =0.5) +
  geom_beeswarm(aes(color = RDK_isattended, x = RDK_isattended,
                    group = RDK_isattended), cex=3, size = 5,alpha=1,fill="grey40",shape=21)+
  # geom_point(aes(color = RDK_isattended, x = interaction(time,RDK_isattended),
  #                   group = RDK_isattended), size = 4,alpha=0.4)+
  stat_summary(fun.y=mean, aes(ymin=..y.., ymax=..y.., color =RDK_isattended), geom='errorbar', width=0.9, size=1.5) +
  scale_x_discrete("RDK_isattended", breaks=waiver(), labels = rep(c(""),1,2)) +
  # theme(legend.position="bottom") +
  ylab(expression(paste("amplitude diff in muV/cm²")))+
  scale_fill_manual(values=c("steelblue2", "#F03F3F"))+
  scale_color_manual(values=c("steelblue2", "#F03F3F"))+
  #  scale_fill_manual(values=c("#193A3D", "#F03F3F"))+
  # scale_color_manual(values=c("#193A3D", "#F03F3F"))+
  # scale_fill_manual(values=c(rgb2hex(0.0, 153.0, 204.0),rgb2hex(0.0, 77, 102.0)))+
  # scale_color_manual(values=c(rgb2hex(0.0, 153.0, 204.0),rgb2hex(0.0, 77, 102.0)))+
  theme(legend.position="none")+
  # scale_y_continuous(limits=c(-60, 140))
  scale_y_continuous(limits=yax_limits)


plot2 <- ggplot(dat2plot, aes(y = subtraction_evoked, fill = RDK_isattended, x = 1)) +
  geom_flat_violin(aes(fill = RDK_isattended),position = position_nudge(x = .1, y = 0), 
                   adjust = 1.3, trim = FALSE, alpha = 1, colour = NA)+
  geom_hline(yintercept=0, show.legend = FALSE) +
  # scale_fill_manual(values=c("#193A3D", "#F03F3F"))+
  # scale_color_manual(values=c("#193A3D", "#F03F3F"))+
  scale_fill_manual(values=c("steelblue2", "#F03F3F"))+
  scale_color_manual(values=c("steelblue2", "#F03F3F"))+
  # scale_fill_manual(values=c(rgb2hex(0.0, 153.0, 204.0),rgb2hex(0.0, 77, 102.0)))+
  # scale_color_manual(values=c(rgb2hex(0.0, 153.0, 204.0),rgb2hex(0.0, 77, 102.0)))+
  theme(axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank())+
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+
  # scale_y_continuous(limits=c(-60, 140))
  scale_y_continuous(limits=yax_limits)



# cowplot::plot_grid(plot1, plot2, plot3, ncol = 3,labels = "AUTO")
plotttitle <- ggdraw() + 
  draw_label("SSVEP diff. | evoked \ncentral RDKs | isoluminant to background", fontface='bold', size = 10)
plotplots <- ggarrange(plot1, plot2,ncol = 2,common.legend = TRUE,align = "h", widths=c(3,1))

savefig <- multi_panel_figure(columns = 1, rows = 1, panel_label_type = "none", width = 3.5, height = 5, unit = "in")
saveplot <- ggarrange(plotttitle, plotplots, nrow = 2, heights=c(0.2, 1))

savefig %<>%
  fill_panel(saveplot, column = 1, row = 1)
savefig
# save_multi_panel_figure(savefig, "figures/FFT_BeeSwarm_Mod_ALPHA_COL_34subs.eps")
```


### 2a  Illustrate Data as is | both subsets | general modulation

plot differently

<br>  

```{r plot_data_center_postcue, results = "hide",  fig.height=5, fig.width=3.5, warning = FALSE}
#evoked raw#### for center

# set overall limits?
dat2plot <- DataIn %>%
  filter(RDK_ispresented=="presented", RDK_position1=="center")%>%
  group_by(subjects, time, RDK_colorlum)%>%
  summarise(amplitude_evoked=mean(amplitude_evoked), modulation_evoked=mean(modulation_evoked))%>%
  filter(time == '[0.5 1.5] ')
# set limits
yax_limits <- c( min(dat2plot$modulation_evoked), max(dat2plot$modulation_evoked))
yax_limits <- round(yax_limits + c(-1, 1)*diff(yax_limits)*0.1)
yax_limits <- yax_limits + c(-1, 1)*diff(yax_limits)*0.1




theme_set(theme_bw())
plot1 <- ggplot(dat2plot, aes(x = RDK_colorlum, y = modulation_evoked, fill = RDK_colorlum)) +
  geom_hline(yintercept=0, show.legend = FALSE) +
  # geom_line(aes(group = interaction(subjects,time)),colour = "grey60",alpha = 1,size =0.5) +
  geom_beeswarm(aes(color = RDK_colorlum, x = RDK_colorlum,
                    group = RDK_colorlum), cex=3, size = 5,alpha=1,fill="grey60",shape=21)+
  # geom_point(aes(color = RDK_isattended, x = interaction(time,RDK_isattended),
  #                   group = RDK_isattended), size = 4,alpha=0.4)+
  stat_summary(fun.y=mean, aes(ymin=..y.., ymax=..y.., color =RDK_colorlum), geom='errorbar', width=0.9, size=1.5) +
  scale_x_discrete("RDK position", breaks=waiver(), labels = rep(c(""),1,2)) +
  # theme(legend.position="bottom") +
  ylab(expression(paste("amplitude modulation in %")))+
  scale_fill_manual(values=c("seagreen", "plum4"))+
  scale_color_manual(values=c("seagreen", "plum4"))+
  #  scale_fill_manual(values=c("#193A3D", "#F03F3F"))+
  # scale_color_manual(values=c("#193A3D", "#F03F3F"))+
  # scale_fill_manual(values=c(rgb2hex(0.0, 153.0, 204.0),rgb2hex(0.0, 77, 102.0)))+
  # scale_color_manual(values=c(rgb2hex(0.0, 153.0, 204.0),rgb2hex(0.0, 77, 102.0)))+
  theme(legend.position="none")+
  # scale_y_continuous(limits=c(-60, 140))
  scale_y_continuous(limits=yax_limits)


plot2 <- ggplot(dat2plot, aes(y = modulation_evoked, fill = RDK_colorlum, x = 1)) +
  geom_flat_violin(aes(fill = RDK_colorlum),position = position_nudge(x = .1, y = 0), 
                   adjust = 1.3, trim = FALSE, alpha = 1, colour = NA)+
  geom_hline(yintercept=0, show.legend = FALSE) +
  # scale_fill_manual(values=c("#193A3D", "#F03F3F"))+
  # scale_color_manual(values=c("#193A3D", "#F03F3F"))+
  scale_fill_manual(values=c("seagreen", "plum4"))+
  scale_color_manual(values=c("seagreen", "plum4"))+
  # scale_fill_manual(values=c(rgb2hex(0.0, 153.0, 204.0),rgb2hex(0.0, 77, 102.0)))+
  # scale_color_manual(values=c(rgb2hex(0.0, 153.0, 204.0),rgb2hex(0.0, 77, 102.0)))+
  theme(axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank())+
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+
  # scale_y_continuous(limits=c(-60, 140))
  scale_y_continuous(limits=yax_limits)



# cowplot::plot_grid(plot1, plot2, plot3, ncol = 3,labels = "AUTO")
plotttitle <- ggdraw() + 
  draw_label("SSVEP mod. | evoked \nacross cons | by stimuli brightness",
             fontface='bold', size = 10)
plotplots <- ggarrange(plot1, plot2,ncol = 2,common.legend = TRUE,align = "h", widths=c(3,1))

savefig <- multi_panel_figure(columns = 1, rows = 1, panel_label_type = "none", width = 3.5, height = 5, unit = "in")
saveplot <- ggarrange(plotttitle, plotplots, nrow = 2, heights=c(0.2, 1))

savefig %<>%
  fill_panel(saveplot, column = 1, row = 1)
savefig
# save_multi_panel_figure(savefig, "figures/FFT_BeeSwarm_Mod_ALPHA_COL_34subs.eps")
```



## Statistical analysis



### Central Stimuli

#### analysis I

**modulation** ~ **COLOR ATTENTION** x **COLOR LUMINANCE**

- mixed design
- t-test post-cue modulation against zero for attended and unattended color
- t-test difference of post-cue modulation for attended vs unattended color

<br> 

```{r Stat central stimuli analysisI, message=FALSE, warning=FALSE, include=TRUE, fig.height=4, fig.width=4.5}
dat2plot <- DataIn %>%
  filter(RDK_position2=="center") %>%
  group_by(subjects, time, RDK_isattended, RDK_colorlum)%>%
  summarise(amplitude_evoked=mean(amplitude_evoked), modulation_evoked=mean(modulation_evoked))%>%
  filter(time == '[0.5 1.5] ')%>%
  ungroup

aovmodel1 <- dat2plot%>%
  aov_ez(id="subjects", dv = "modulation_evoked", data = ., within = c("RDK_isattended"), between = c("RDK_colorlum"),
         include_aov = afex_options("include_aov"))


# display table anova effects
aovmodel1 %>%
  anova()%>%
  tidy()%>%
  mutate(
    `p.value` = cell_spec(ifelse(round(`p.value`,4)<.001,"< .001",round(`p.value`,4)), 
                        color = ifelse(is.nan(`p.value`),"blue", ifelse(`p.value` < .05, "green", "red")),
                        bold = ifelse(is.nan(`p.value`),F, ifelse(`p.value` < .05, T,F)),
                        align = "center")
  ) %>%
  dplyr::select(term, `num.Df`, `den.Df`, MSE, `statistic`, ges, `p.value`) %>%
  dplyr::rename(F=statistic)%>%
  kbl(escape = F, digits = c(5,5,5,5,5,5,5,5,5), caption = c("repeated measures ANOVA for central post-cue modulations")) %>%
  kable_styling("striped", full_width = T, bootstrap_options = c("striped", "hover", "condensed", "responsive",font_size = 8))


#display interaction
emm_ATTXLum <- as.data.frame(emmeans(aovmodel1, ~ RDK_isattended*RDK_colorlum))

# RDK_isattended plot
ggplot(emm_ATTXLum, aes(x = RDK_colorlum, y = emmean, fill = RDK_isattended)) +
  geom_col(position = position_dodge(), width = 0.6) +
  geom_errorbar(aes(ymin = lower.CL, ymax = upper.CL), 
                position = position_dodge(width = 0.6),
                width = 0.2) +
  labs(title = "Interaction: Attention × Luminance",
       y = "Estimated Marginal Means (95% CI)", x = "Color Luminance") +
  theme_minimal()+
  scale_fill_manual(values=c("steelblue2", "#F03F3F"))+
  scale_color_manual(values=c("steelblue2", "#F03F3F"))


#create emmeans object/grid
post_hocs.emmean <- emmeans(aovmodel1, c("RDK_isattended","RDK_colorlum")) # adjust = holm

# report data for post_hocs.RDK_isattended
post_hocs.emmean %>%
  kbl(escape = F, digits = c(3,3,3,3,3,3,3,3,3), 
      caption = c("estimated marginal means | by ATTENTION X LUMINANCE | dv = central SSVEP modulation")) %>%
  kable_styling("striped", full_width = T, bootstrap_options = c("striped", "hover", "condensed", "responsive",font_size = 8))

post_hocs.emmean %>%
contrast(method = "identity",adjust = "FDR")%>%
summary() %>%
  mutate(
    p.value = cell_spec(ifelse(round(p.value,4)<.001,"< .001",round(p.value,4)), 
                        color = ifelse(is.nan(p.value),"blue", ifelse(p.value < .05, "green", "red")),
                        bold = ifelse(is.nan(p.value),F, ifelse(p.value < .05, T,F)),
                        align = "left")
  ) %>%
  # mutate(CohensD = `t.ratio`/sqrt(df+1))%>%
  mutate(`CohensD` =
           summary(eff_size(contrast(post_hocs.emmean,method = "identity",adjust = "FDR"),
                            sigma = sqrt(mean(sigma(aovmodel1$lm)^2)), # RMS of sigma()
                            edf = df.residual(aovmodel1$lm), method = "identity"))$effect.size,
         `lowCI` =
           summary(eff_size(contrast(post_hocs.emmean,method = "identity",adjust = "FDR"),
                            sigma = sqrt(mean(sigma(aovmodel1$lm)^2)), # RMS of sigma()
                            edf = df.residual(aovmodel1$lm), method = "identity"))$lower.CL,
         `highCI` =
           summary(eff_size(contrast(post_hocs.emmean,method = "identity",adjust = "FDR"),
                            sigma = sqrt(mean(sigma(aovmodel1$lm)^2)), # RMS of sigma()
                            edf = df.residual(aovmodel1$lm), method = "identity"))$upper.CL
  )%>%
  kbl(escape = F, digits = c(3,3,3,3,3,3,3,3,3), 
        caption = c("estimated marginal means | by ATTENTION X LUMINANCE | dv = central SSVEP modulation | corrected: FDR")) %>%
  kable_styling("striped", full_width = T, bootstrap_options = c("striped", "hover", "condensed", "responsive",font_size = 8))

# planned comparison
# test by specifying the levels levels(post_hocs.emmean) as.data.frame(post_hocs.emmean)
list.contrasts <- list(
  "iso att vs unatt"=c(1, -1, 0, 0),
  "offset att vs unatt"=c(0, 0, 1, -1),
  "att iso vs offset"=c(1,0,-1,0),
  "unatt iso vs offset"=c(0, 1, 0, -1)
)



post_hocs.emmean %>%
  contrast(method = list.contrasts,adjust = "FDR") %>%
  summary() %>%
  mutate(
    p.value = cell_spec(ifelse(round(p.value,4)<.001,"< .001",round(p.value,4)), 
                        color = ifelse(is.nan(p.value),"blue", ifelse(p.value < .05, "green", "red")),
                        bold = ifelse(is.nan(p.value),F, ifelse(p.value < .05, T,F)),
                        align = "left")
  ) %>%
  # mutate(CohensD = `t.ratio`/sqrt(df+1))%>%
  mutate(`CohensD` =
           summary(eff_size(contrast(post_hocs.emmean, method = list.contrasts,adjust = "FDR"),
                            sigma = sqrt(mean(sigma(aovmodel1$lm)^2)), # RMS of sigma()
                            edf = df.residual(aovmodel1$lm), method = "identity"))$effect.size,
         `lowCI` =
           summary(eff_size(contrast(post_hocs.emmean, method = list.contrasts,adjust = "FDR"),
                            sigma = sqrt(mean(sigma(aovmodel1$lm)^2)), # RMS of sigma()
                            edf = df.residual(aovmodel1$lm), method = "identity"))$lower.CL,
         `highCI` =
           summary(eff_size(contrast(post_hocs.emmean, method = list.contrasts,adjust = "FDR"),
                            sigma = sqrt(mean(sigma(aovmodel1$lm)^2)), # RMS of sigma()
                            edf = df.residual(aovmodel1$lm), method = "identity"))$upper.CL
  )%>%
  kbl(escape = F, digits = c(3,3,3,3,3,3,3,3,3), 
        caption = c("estimated contrasts | by ATTENTION X LUMINANCE | dv = central SSVEP modulation | corrected: FDR")) %>%
  kable_styling("striped", full_width = T, bootstrap_options = c("striped", "hover", "condensed", "responsive",font_size = 8))
```




#### analysis II

**modulation** ~ **COLOR ATTENTION**

conventional analysis with anova and post-hoc t-tests implemented manually

- t-test post-cue modulation against zero for attended and unattended color
- t-test difference of post-cue modulation for attended vs unattended color

<br> 

```{r Stat central stimuli analysisII, message=FALSE, warning=FALSE, include=TRUE}
dat2plot <- DataIn %>%
  filter(RDK_position2=="center") %>%
  group_by(subjects, time, RDK_isattended, RDK_colorlum)%>%
  summarise(amplitude_evoked=mean(amplitude_evoked), modulation_evoked=mean(modulation_evoked))%>%
  filter(time == '[0.5 1.5] ')


aovmodel1 <- dat2plot%>%
  aov_ez(id="subjects", dv = "modulation_evoked", data = ., within = c("RDK_isattended"), between = c("RDK_colorlum"),
         include_aov = afex_options("include_aov"))


# display table anova effects
aovmodel1 %>%
  anova()%>%
  tidy()%>%
  mutate(
    `p.value` = cell_spec(ifelse(round(`p.value`,4)<.001,"< .001",round(`p.value`,4)), 
                        color = ifelse(is.nan(`p.value`),"blue", ifelse(`p.value` < .05, "green", "red")),
                        bold = ifelse(is.nan(`p.value`),F, ifelse(`p.value` < .05, T,F)),
                        align = "center")
  ) %>%
  dplyr::select(term, `num.Df`, `den.Df`, MSE, `statistic`, ges, `p.value`) %>%
  dplyr::rename(F=statistic)%>%
  kbl(escape = F, digits = c(5,5,5,5,5,5,5,5,5), caption = c("Mixed effects ANOVA model for central post-cue modulations")) %>%
  kable_styling("striped", full_width = T, bootstrap_options = c("striped", "hover", "condensed", "responsive",font_size = 8))


dat2plot %>%
  group_by(RDK_isattended, RDK_colorlum)%>%
  nest()%>%
  mutate(stats = map(data, ~broom::tidy(
    t.test(modulation_evoked ~ 1, data = .)
  ))) %>%
  mutate(
    t_test_bf = map(data, ~{extractBF(ttestBF(x = .$modulation_evoked, data = .,iterations=num.iter,rscale = sqrt(2)/2))})
  )%>%
  mutate(meanval = map(data, ~ mean(.x$modulation_evoked))) %>%
  mutate(std = map(data, ~ sd(.x$modulation_evoked))) %>%
  dplyr::select(-data) %>%
  unnest(cols = c(stats, t_test_bf, meanval, std))%>%
  mutate(BF10 = bf, BF01 = 1/bf)%>%
  dplyr::select(RDK_colorlum, RDK_isattended, meanval, std,  statistic, parameter, p.value, BF10, BF01)%>%
  ungroup()%>%
  # group_by(RDK_colorlum)%>%
  mutate(p.value = p.adjust(p.value, method="fdr")) %>% # none, holm
  # mutate(p.value = p.adjust(p.value, method="none")) %>% # none, holm
  ungroup()%>%
  mutate(CohensD = `statistic`/sqrt(parameter +1))%>%
  mutate(
    p.value = cell_spec(ifelse(round(p.value,4)<.001,"< .001",round(p.value,4)), 
                        color = ifelse(is.nan(p.value),"blue", ifelse(p.value < .05, "green", "red")),
                        bold = ifelse(is.nan(p.value),F, ifelse(p.value < .05, T,F)),
                        align = "center")
  ) %>%
  kbl(escape = F, digits = c(3,3,3,3,3,3,3,3,3), 
        caption = c("central SSVEP | modulation | t-tests for modulation agains zero | FDR-corrected")) %>%
  kable_styling("striped", full_width = T, bootstrap_options = c("striped", "hover", "condensed", "responsive",font_size = 8))



dat2plot %>%
  dplyr::select(-amplitude_evoked)%>%
  pivot_wider(names_from = "RDK_isattended", values_from = "modulation_evoked")%>%
  mutate(attendedMINUSunattended = `attended` -`not attended`)%>%
  group_by(time, RDK_colorlum)%>%
  nest()%>%
  mutate(stats = map(data, ~broom::tidy(
    t.test(attendedMINUSunattended ~ 1, data = .)
  ))) %>%
  mutate(
    t_test_bf = map(data, ~{extractBF(ttestBF(x = .$attendedMINUSunattended, data = .,iterations=num.iter,rscale = sqrt(2)/2))})
  )%>%
  mutate(meanval = map(data, ~ mean(.x$attendedMINUSunattended))) %>%
  mutate(std = map(data, ~ sd(.x$attendedMINUSunattended))) %>%
  ungroup()%>%
  dplyr::select(-data, -time) %>%
  unnest(cols = c(stats, t_test_bf, meanval, std))%>%
  mutate(BF10 = bf, BF01 = 1/bf)%>%
  dplyr::select(RDK_colorlum, meanval, std,  statistic, parameter, p.value, BF10, BF01)%>%
  ungroup()%>%
  mutate(p.value = p.adjust(p.value, method="fdr")) %>% # none, holm
  # mutate(p.value = p.adjust(p.value, method="none")) %>% # none, holm
  ungroup()%>%
  mutate(CohensD = `statistic`/sqrt(parameter +1))%>%
  mutate(
    p.value = cell_spec(ifelse(round(p.value,4)<.001,"< .001",round(p.value,4)), 
                        color = ifelse(is.nan(p.value),"blue", ifelse(p.value < .05, "green", "red")),
                        bold = ifelse(is.nan(p.value),F, ifelse(p.value < .05, T,F)),
                        align = "center")
  ) %>%
  kbl(escape = F, digits = c(3,3,3,3,3,3,3,3,3), caption = c("central SSVEP | modulation | attended - unattended ")) %>%
  kable_styling("striped", full_width = T, bootstrap_options = c("striped", "hover", "condensed", "responsive",font_size = 8))

```

#### analysis III

**modulation** ~ **COLOR ATTENTION**

Bayesian analysis via brms to allow inclusion of Bayes Factor estimation for mixed models

```{r Stat central stimuli analysisIII, message=FALSE, warning=FALSE, include=TRUE}
dat2plot <- DataIn %>%
  filter(RDK_position2=="center") %>%
  group_by(subjects, time, RDK_isattended, RDK_colorlum)%>%
  summarise(amplitude_evoked=mean(amplitude_evoked), modulation_evoked=mean(modulation_evoked))%>%
  filter(time == '[0.5 1.5] ')



# Fit the model
# (1 | subjects) accounts for the random intercept per subject
bayesian_model <- brm(
  formula = modulation_evoked ~ RDK_isattended * RDK_colorlum + (1 | subjects), 
  data = dat2plot,
  family = gaussian(),
  prior = set_prior("normal(0, 20)", class = "b"), # Optional: set your priors
  # prior = set_prior("cauchy(0, 0.707)", class = "b"), # medium prior
  chains = 4, iter = 2000, core = 4,
  file = "fit_full_slog.rds",
  save_pars = save_pars(all = TRUE),
  file_refit = "on_change",
  # file_refit = "always",
  # file_refit = "never",
)

# (2 | subjects) fit the prior model only
bayesian_prior_model <- brm(
  formula = modulation_evoked ~ RDK_isattended * RDK_colorlum + (1 | subjects), 
  data = dat2plot,
  family = gaussian(),
  prior = set_prior("normal(0, 20)", class = "b"), # Optional: set your priors
  # prior = set_prior("cauchy(0, 0.707)", class = "b"), # medium prior
  chains = 4, iter = 2000, core = 4,
  file = "fit_full_prior_slog.rds",
  save_pars = save_pars(all = TRUE),
  file_refit = "on_change",
  # file_refit = "always",
  # file_refit = "never",
  sample_prior = "only" # This ignores your actual DV values
)

# (3 | subjects) fit the null model only
bayesian_null_model <- brm(
  formula = modulation_evoked ~ 1 + (1 | subjects), 
  data = dat2plot,
  family = gaussian(),
  prior = set_prior("normal(0, 20)", class = "Intercept"), # Optional: set your priors
  # prior = set_prior("cauchy(0, 0.707)", class = "b"), # medium prior
  chains = 4, iter = 2000, core = 4,
  file = "fit_null_slog.rds",
  save_pars = save_pars(all = TRUE),
  file_refit = "on_change",
  # file_refit = "always",
  # file_refit = "never",
)


# report results for some designed contrasts
# create emmmgrid
bayesian_emm <- emmeans(bayesian_model, ~ RDK_isattended * RDK_colorlum)

# defined contrasts
list.contrasts <- list(
  "iso att vs unatt"=c(1, -1, 0, 0),
  "offset att vs unatt"=c(0, 0, 1, -1),
  "att iso vs offset"=c(1,0,-1,0),
  "unatt iso vs offset"=c(0, 1, 0, -1)
)

# compute contrasts
bayesian_contrasts<-bayesian_emm %>%
  contrast(method = list.contrasts)

bayesian_contrasts %>%
  summary() %>%
    kbl(escape = F, digits = c(3,3,3,3,3,3,3,3,3), 
        caption = c("estimated contrasts | by ATTENTION X LUMINANCE | dv = central SSVEP modulation | BRMs framework")) %>%
  kable_styling("striped", full_width = T, bootstrap_options = c("striped", "hover", "condensed", "responsive",font_size = 8))


# no calculate Bayes factors for these contrasts
# Force the calculation to look at the samples
prior_model <- unupdate(bayesian_model)
prior_emm <- emmeans(prior_model, ~ RDK_isattended * RDK_colorlum)
prior_emm_contrasts <- prior_emm %>%
  contrast(method = list.contrasts)

bayesian_contrasts_BF <- bayesfactor_parameters(bayesian_contrasts, prior = prior_emm_contrasts)

bayesian_contrasts_BF%>%
  as.data.frame() %>%
  mutate(BF10 = exp(log_BF), BF01 = 1/exp(log_BF)) %>%
  # Optional: Round to 2 decimal places unless it's very small
  mutate(BF = ifelse(BF > 1000, formatC(BF, format = "e", digits = 3), round(BF, 3))) %>%
  mutate(BF = ifelse(BF > 1000, formatC(BF, format = "e", digits = 3), round(BF, 3))) %>%
  dplyr::select(contrast, BF, -log_BF)%>%
    kbl(escape = F, digits = c(3,3,3,3,3,3,3,3,3), 
        caption = c("estimated contrasts | by ATTENTION X LUMINANCE | dv = central SSVEP modulation | BRMs framework")) %>%
  kable_styling("striped", full_width = T, bootstrap_options = c("striped", "hover", "condensed", "responsive",font_size = 8))




```


