---
title: "FFT_SSVEP_analysis"
author: "Christopher"
date: "2 7 2024"
output:
  html_document:
    code_folding: hide
    toc: true
    toc_float: true
    toc_depth: 4
    theme: flatly
---

Modelling of ~~raw~~ [*CSD based*] amplitude values from fft-based data
via linear mixed models
via standard anova models

```{r load_package, message = FALSE, warning = FALSE}
library(lme4)
library(readxl)
library(tidyverse)
library(data.table)
library(tidyverse)
library(afex)
library(broom)
library(apa)
library(kableExtra)
library(lmerTest)
library(pbkrtest)
library(effects)
library(visreg)
library(sjPlot)
library(broom.mixed)
library(pander)
library(mediation)
library(multcomp)
library(multcompView)
library(magrittr)
library(multipanelfigure)
library(ggbeeswarm)
library(lsmeans)
library(BayesFactor)
library(ggpubr)
library(gpairs)
library(DescTools)
library(cowplot)
library(ggpol)
library(logspline)

source('C:/Users/psy05cvd/Dropbox/work/R-statistics/general_functions/RainCloudPlots/tutorial_R/R_rainclouds.R')
source('C:/Users/psy05cvd/Dropbox/work/R-statistics/general_functions/RainCloudPlots/tutorial_R/R_rainclouds.R')

source('C:/Users/psy05cvd/Dropbox/work/R-statistics/examples/Bayesian_rank-based_hypothesis_testing/rankBasedCommonFunctions.R')
source('C:/Users/psy05cvd/Dropbox/work/R-statistics/examples/Bayesian_rank-based_hypothesis_testing/rankSumSampler.R') # Wilcoxon rank sum function
source('C:/Users/psy05cvd/Dropbox/work/R-statistics/examples/Bayesian_rank-based_hypothesis_testing/signRankSampler.R') # Wilcoxon signed-rank function
source('C:/Users/psy05cvd/Dropbox/work/R-statistics/examples/Bayesian_rank-based_hypothesis_testing/spearmanSampler.R')# Spearman's rho function




# broad cluster
# CSD based normalized to pre-cue baseline in %
#  
DATAPath = "data_in/FFT_Amp_data_largeclust_06-14-2024_13-19.csv"
t_baseline = c(-1000, 0)


# broad cluster | smaller central cluster
# CSD based normalized to pre-cue baseline in %
#  
# DATAPath = "data_in/FFT_Amp_data_largeclust_06-24-2024_15-43.csv"
# t_baseline = c(-1000, 0)


# broad cluster | smaller central cluster
# CSD based normalized to pre-cue baseline in %
# for changed experiment starting with participant 22: isoluminant stimuli and lower flicker frequencies
#  
DATAPath = "data_in/FFT_Amp_data_largeclust_allsubs_08-30-2024_11-21.csv"
t_baseline = c(-1000, 0)


# broad cluster | larger central cluster |
# peri: not correct!
# CSD based normalized to pre-cue baseline in %
# for changed experiment starting with participant 22: isoluminant stimuli and lower flicker frequencies
#  
# DATAPath = "data_in/FFT_Amp_data_pericenter_allsubs_07-02-2024_11-46.csv"
# t_baseline = c(-1000, 0)
# 
# broad cluster | very broad central cluster
# CSD based normalized to pre-cue baseline in %
# for changed experiment starting with participant 22: isoluminant stimuli and lower flicker frequencies
# # 
# DATAPath = "data_in/FFT_Amp_data_largecenterclust_allsubs_09-11-2024_14-45.csv"
# t_baseline = c(-1000, 0)



#!!!!!!! relevant
# broad cluster | larger central cluster as in Tango study | peri both clusters but smaller
# CSD based normalized to pre-cue baseline in %
# for changed experiment starting with participant 22: isoluminant stimuli and lower flicker frequencies
DATAPath = "data_in/FFT_Amp_data_CenterTangoStudyPeriSmall_05-23-2025_11-56.csv"
t_baseline = c(-1000, 0)

# broad cluster | larger central cluster as in Tango study | peri only center
# DATAPath = "data_in/FFT_Amp_data_TangoStudyPeriOnlyCenter_11-25-2024_14-17.csv"
# t_baseline = c(-1000, 0)

# # broad cluster | larger central cluster as in Tango study | peri only lateral | in this study shows gain for attended
# DATAPath = "data_in/FFT_Amp_data_TangoStudyPeriOnlyLateral_11-25-2024_14-17.csv"
# t_baseline = c(-1000, 0)


#!!!!!!!


# replication relevant
# broad cluster | larger central cluster as in Tango study | peri both clusters as in Tango study
# CSD based normalized to pre-cue baseline in %
# for changed experiment starting with participant 22: isoluminant stimuli and lower flicker frequencies
# DATAPath = "data_in/FFT_Amp_data_TangoStudy_05-23-2025_11-53.csv"
# t_baseline = c(-1000, 0)




options(scipen=1, digits=7)
```
<style type="text/css">
.main-container {
max-width: 1800px !important;
margin-left: auto;
margin-right: auto;
}
</style>


## Prepare data  
<br>  

1.  Read in data: 
+ `r DATAPath`
+ with pre-cue  [`r toString(t_baseline)`] ms

<br>  

```{r load_data,results = "hide", fig.show = "hide", warning = FALSE}
sub_sample = c(0)
# sub_sample = as.factor(c(26,30, 31,37, 38)) # no ssvep people discarded
sub_sample = as.factor(c(42)) # low trial number


# read in data
DataIn <- read.csv(DATAPath, sep = ";") %>%
  mutate(subjects = as.factor(subjects))%>%
  filter(!subjects %in% sub_sample)
head(DataIn)
str(DataIn)
```
## Illustrate SSVEP Data

### 1a  Illustrate Data as is | center RDKs

<br>  

```{r plot_data_st_center, results = "hide",  fig.height=3, fig.width=4, warning = FALSE}
#evoked raw#### for center
dat2plot <- DataIn %>%
  filter(RDK_position2=="center") %>%
  group_by(subjects, time, RDK_isattended, RDK_colorlum)%>%
  summarise(amplitude_evoked=mean(amplitude_evoked), modulation_evoked=mean(modulation_evoked), subtraction_evoked=mean(subtraction_evoked))

theme_set(theme_bw())
ggplot(dat2plot, aes(x = interaction(time,RDK_isattended), y = amplitude_evoked, fill = RDK_isattended)) +
  # geom_hline(yintercept=0, show.legend = FALSE) +
  geom_line(aes(group = interaction(subjects,RDK_isattended)),colour = "grey60",alpha = 0.5,size =0.5) +
  geom_beeswarm(aes(color = RDK_isattended, x = interaction(time,RDK_isattended),
                    group = RDK_isattended), cex=2, size = 3,alpha=1,fill="grey40",shape=21)+
  # geom_point(aes(color = condition, x = interaction(time,condition),
  #                   group = condition), size = 4,alpha=0.4)+
  stat_summary(fun.y=mean, aes(ymin=..y.., ymax=..y.., color =RDK_isattended), geom='errorbar', width=0.9, size=1.5) +
  scale_x_discrete("time windows in s", breaks=waiver(), labels = rep(c("[-1 0]","[0.5 1.5]","[1 2]"),1,6)) +
  facet_grid(.~RDK_colorlum)+
  theme(legend.position="bottom") +
  ylab(expression(paste("amplitude in muV/cm²")))+
  labs(title=sprintf("SSVEP amplitudes | evoked"),
       subtitle="collapsed across frequencies")+
  scale_fill_brewer(palette = "Dark2")+
  scale_color_brewer(palette = "Dark2")


theme_set(theme_bw())
ggplot(dat2plot, aes(x = interaction(time,RDK_isattended), y = modulation_evoked, fill = RDK_isattended)) +
  # geom_hline(yintercept=0, show.legend = FALSE) +
  geom_line(aes(group = interaction(subjects,RDK_isattended)),colour = "grey60",alpha = 0.5,size =0.5) +
  geom_beeswarm(aes(color = RDK_isattended, x = interaction(time,RDK_isattended),
                    group = RDK_isattended), cex=2, size = 3,alpha=1,fill="grey40",shape=21)+
  # geom_point(aes(color = condition, x = interaction(time,condition),
  #                   group = condition), size = 4,alpha=0.4)+
  stat_summary(fun.y=mean, aes(ymin=..y.., ymax=..y.., color =RDK_isattended), geom='errorbar', width=0.9, size=1.5) +
  scale_x_discrete("time windows in s", breaks=waiver(), labels = rep(c("[-1 0]","[0.5 1.5]","[1 2]"),1,6)) +
  facet_grid(.~RDK_colorlum)+
  theme(legend.position="bottom") +
  ylab(expression(paste("modulation in %")))+
  labs(title=sprintf("SSVEP amplitudes | evoked"),
       subtitle="collapsed across frequencies")+
  scale_fill_brewer(palette = "Dark2")+
  scale_color_brewer(palette = "Dark2")

theme_set(theme_bw())
ggplot(dat2plot, aes(x = interaction(time,RDK_isattended), y = subtraction_evoked, fill = RDK_isattended)) +
  # geom_hline(yintercept=0, show.legend = FALSE) +
  geom_line(aes(group = interaction(subjects,RDK_isattended)),colour = "grey60",alpha = 0.5,size =0.5) +
  geom_beeswarm(aes(color = RDK_isattended, x = interaction(time,RDK_isattended),
                    group = RDK_isattended), cex=2, size = 3,alpha=1,fill="grey40",shape=21)+
  # geom_point(aes(color = condition, x = interaction(time,condition),
  #                   group = condition), size = 4,alpha=0.4)+
  stat_summary(fun.y=mean, aes(ymin=..y.., ymax=..y.., color =RDK_isattended), geom='errorbar', width=0.9, size=1.5) +
  scale_x_discrete("time windows in s", breaks=waiver(), labels = rep(c("[-1 0]","[0.5 1.5]","[1 2]"),1,6)) +
  facet_grid(.~RDK_colorlum)+
  theme(legend.position="bottom") +
  ylab(expression(paste("amplitude diff in muV/cm²")))+
  labs(title=sprintf("SSVEP amplitudes | evoked"),
       subtitle="collapsed across frequencies")+
  scale_fill_brewer(palette = "Dark2")+
  scale_color_brewer(palette = "Dark2")
```
### 1b  Illustrate Data as is | center RDKs

plot differently

<br>  

```{r plot_data_st_center_2, results = "hide",  fig.height=5, fig.width=3.5, warning = FALSE}
#evoked raw#### for center

# set overall limits?
dat2plot <- DataIn %>%
  filter(RDK_position2=="center") %>%
  group_by(subjects, time, RDK_isattended, RDK_colorlum)%>%
  summarise(amplitude_evoked=mean(amplitude_evoked), modulation_evoked=mean(modulation_evoked))%>%
  filter(time=='[0.5 1.5] ')
# set limits
yax_limits <- c( min(dat2plot$modulation_evoked), max(dat2plot$modulation_evoked))
yax_limits <- round(yax_limits + c(-1, 1)*diff(yax_limits)*0.1)
yax_limits <- yax_limits + c(-1, 1)*diff(yax_limits)*0.1


dat2plot <- DataIn %>%
  filter(RDK_position2=="center") %>%
  group_by(subjects, time, RDK_isattended, RDK_colorlum)%>%
  summarise(amplitude_evoked=mean(amplitude_evoked), modulation_evoked=mean(modulation_evoked))%>%
  filter(time=='[0.5 1.5] ', RDK_colorlum == 'offset_to_bckgrd')

# set limits
# yax_limits <- c( min(dat2plot$modulation_evoked), max(dat2plot$modulation_evoked))
# yax_limits <- round(yax_limits + c(-1, 1)*diff(yax_limits)*0.1)
# yax_limits <- yax_limits + c(-1, 1)*diff(yax_limits)*0.2
# # yax_limits <- c(-27, 15)

theme_set(theme_bw())
plot1 <- ggplot(dat2plot, aes(x = RDK_isattended, y = modulation_evoked, fill = RDK_isattended)) +
  geom_hline(yintercept=0, show.legend = FALSE) +
  geom_line(aes(group = interaction(subjects,time)),colour = "grey60",alpha = 1,size =0.5) +
  geom_beeswarm(aes(color = RDK_isattended, x = RDK_isattended,
                    group = RDK_isattended), cex=3, size = 5,alpha=1,fill="grey40",shape=21)+
  # geom_point(aes(color = RDK_isattended, x = interaction(time,RDK_isattended),
  #                   group = RDK_isattended), size = 4,alpha=0.4)+
  stat_summary(fun.y=mean, aes(ymin=..y.., ymax=..y.., color =RDK_isattended), geom='errorbar', width=0.9, size=1.5) +
  scale_x_discrete("RDK_isattended", breaks=waiver(), labels = rep(c(""),1,2)) +
  # theme(legend.position="bottom") +
  ylab(expression(paste("amplitude modulation in %")))+
  scale_fill_manual(values=c("steelblue2", "#F03F3F"))+
  scale_color_manual(values=c("steelblue2", "#F03F3F"))+
  #  scale_fill_manual(values=c("#193A3D", "#F03F3F"))+
  # scale_color_manual(values=c("#193A3D", "#F03F3F"))+
  # scale_fill_manual(values=c(rgb2hex(0.0, 153.0, 204.0),rgb2hex(0.0, 77, 102.0)))+
  # scale_color_manual(values=c(rgb2hex(0.0, 153.0, 204.0),rgb2hex(0.0, 77, 102.0)))+
  theme(legend.position="none")+
  # scale_y_continuous(limits=c(-60, 140))
  scale_y_continuous(limits=yax_limits)


plot2 <- ggplot(dat2plot, aes(y = modulation_evoked, fill = RDK_isattended, x = 1)) +
  geom_flat_violin(aes(fill = RDK_isattended),position = position_nudge(x = .1, y = 0), 
                   adjust = 1.3, trim = FALSE, alpha = 1, colour = NA)+
  geom_hline(yintercept=0, show.legend = FALSE) +
  # scale_fill_manual(values=c("#193A3D", "#F03F3F"))+
  # scale_color_manual(values=c("#193A3D", "#F03F3F"))+
  scale_fill_manual(values=c("steelblue2", "#F03F3F"))+
  scale_color_manual(values=c("steelblue2", "#F03F3F"))+
  # scale_fill_manual(values=c(rgb2hex(0.0, 153.0, 204.0),rgb2hex(0.0, 77, 102.0)))+
  # scale_color_manual(values=c(rgb2hex(0.0, 153.0, 204.0),rgb2hex(0.0, 77, 102.0)))+
  theme(axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank())+
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+
  # scale_y_continuous(limits=c(-60, 140))
  scale_y_continuous(limits=yax_limits)



# cowplot::plot_grid(plot1, plot2, plot3, ncol = 3,labels = "AUTO")
plotttitle <- ggdraw() + 
  draw_label("SSVEP mod. | evoked \ncentral RDKs | luminance offset", fontface='bold', size = 10)
plotplots <- ggarrange(plot1, plot2,ncol = 2,common.legend = TRUE,align = "h", widths=c(3,1))

savefig <- multi_panel_figure(columns = 1, rows = 1, panel_label_type = "none", width = 3.5, height = 5, unit = "in")
saveplot <- ggarrange(plotttitle, plotplots, nrow = 2, heights=c(0.2, 1))

savefig %<>%
  fill_panel(saveplot, column = 1, row = 1)
savefig
# save_multi_panel_figure(savefig, "figures/FFT_BeeSwarm_Mod_ALPHA_COL_34subs.eps")




dat2plot <- DataIn %>%
  filter(RDK_position2=="center") %>%
  group_by(subjects, time, RDK_isattended, RDK_colorlum)%>%
  summarise(amplitude_evoked=mean(amplitude_evoked), modulation_evoked=mean(modulation_evoked))%>%
  filter(time=='[0.5 1.5] ', RDK_colorlum == 'isolum__to_bckgrd')


# set limits
# yax_limits <- c( min(dat2plot$modulation_evoked), max(dat2plot$modulation_evoked))
# yax_limits <- round(yax_limits + c(-1, 1)*diff(yax_limits)*0.1)
# yax_limits <- yax_limits + c(-1, 1)*diff(yax_limits)*0.2
# # yax_limits <- c(-27, 15)

theme_set(theme_bw())
plot1 <- ggplot(dat2plot, aes(x = RDK_isattended, y = modulation_evoked, fill = RDK_isattended)) +
  geom_hline(yintercept=0, show.legend = FALSE) +
  geom_line(aes(group = interaction(subjects,time)),colour = "grey60",alpha = 1,size =0.5) +
  geom_beeswarm(aes(color = RDK_isattended, x = RDK_isattended,
                    group = RDK_isattended), cex=3, size = 5,alpha=1,fill="grey40",shape=21)+
  # geom_point(aes(color = RDK_isattended, x = interaction(time,RDK_isattended),
  #                   group = RDK_isattended), size = 4,alpha=0.4)+
  stat_summary(fun.y=mean, aes(ymin=..y.., ymax=..y.., color =RDK_isattended), geom='errorbar', width=0.9, size=1.5) +
  scale_x_discrete("RDK_isattended", breaks=waiver(), labels = rep(c(""),1,2)) +
  # theme(legend.position="bottom") +
  ylab(expression(paste("amplitude modulation in %")))+
  scale_fill_manual(values=c("steelblue2", "#F03F3F"))+
  scale_color_manual(values=c("steelblue2", "#F03F3F"))+
  #  scale_fill_manual(values=c("#193A3D", "#F03F3F"))+
  # scale_color_manual(values=c("#193A3D", "#F03F3F"))+
  # scale_fill_manual(values=c(rgb2hex(0.0, 153.0, 204.0),rgb2hex(0.0, 77, 102.0)))+
  # scale_color_manual(values=c(rgb2hex(0.0, 153.0, 204.0),rgb2hex(0.0, 77, 102.0)))+
  theme(legend.position="none")+
  # scale_y_continuous(limits=c(-60, 140))
  scale_y_continuous(limits=yax_limits)


plot2 <- ggplot(dat2plot, aes(y = modulation_evoked, fill = RDK_isattended, x = 1)) +
  geom_flat_violin(aes(fill = RDK_isattended),position = position_nudge(x = .1, y = 0), 
                   adjust = 1.3, trim = FALSE, alpha = 1, colour = NA)+
  geom_hline(yintercept=0, show.legend = FALSE) +
  # scale_fill_manual(values=c("#193A3D", "#F03F3F"))+
  # scale_color_manual(values=c("#193A3D", "#F03F3F"))+
  scale_fill_manual(values=c("steelblue2", "#F03F3F"))+
  scale_color_manual(values=c("steelblue2", "#F03F3F"))+
  # scale_fill_manual(values=c(rgb2hex(0.0, 153.0, 204.0),rgb2hex(0.0, 77, 102.0)))+
  # scale_color_manual(values=c(rgb2hex(0.0, 153.0, 204.0),rgb2hex(0.0, 77, 102.0)))+
  theme(axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank())+
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+
  # scale_y_continuous(limits=c(-60, 140))
  scale_y_continuous(limits=yax_limits)



# cowplot::plot_grid(plot1, plot2, plot3, ncol = 3,labels = "AUTO")
plotttitle <- ggdraw() + 
  draw_label("SSVEP mod. | evoked \ncentral RDKs | isoluminant to background", fontface='bold', size = 10)
plotplots <- ggarrange(plot1, plot2,ncol = 2,common.legend = TRUE,align = "h", widths=c(3,1))

savefig <- multi_panel_figure(columns = 1, rows = 1, panel_label_type = "none", width = 3.5, height = 5, unit = "in")
saveplot <- ggarrange(plotttitle, plotplots, nrow = 2, heights=c(0.2, 1))

savefig %<>%
  fill_panel(saveplot, column = 1, row = 1)
savefig
# save_multi_panel_figure(savefig, "figures/FFT_BeeSwarm_Mod_ALPHA_COL_34subs.eps")



dat2plot <- DataIn %>%
  filter(RDK_position2=="center") %>%
  group_by(subjects, time, RDK_isattended, RDK_colorlum)%>%
  summarise(amplitude_evoked=mean(amplitude_evoked), modulation_evoked=mean(modulation_evoked), subtraction_evoked = mean(subtraction_evoked))%>%
  filter(time=='[0.5 1.5] ', RDK_colorlum == 'isolum__to_bckgrd')


# set limits
yax_limits <- c( min(dat2plot$subtraction_evoked), max(dat2plot$subtraction_evoked))
# yax_limits <- round(yax_limits + c(-1, 1)*diff(yax_limits)*0.1)
yax_limits <- yax_limits + c(-1, 1)*diff(yax_limits)*0.2
# # yax_limits <- c(-27, 15)

theme_set(theme_bw())
plot1 <- ggplot(dat2plot, aes(x = RDK_isattended, y = subtraction_evoked, fill = RDK_isattended)) +
  geom_hline(yintercept=0, show.legend = FALSE) +
  geom_line(aes(group = interaction(subjects,time)),colour = "grey60",alpha = 1,size =0.5) +
  geom_beeswarm(aes(color = RDK_isattended, x = RDK_isattended,
                    group = RDK_isattended), cex=3, size = 5,alpha=1,fill="grey40",shape=21)+
  # geom_point(aes(color = RDK_isattended, x = interaction(time,RDK_isattended),
  #                   group = RDK_isattended), size = 4,alpha=0.4)+
  stat_summary(fun.y=mean, aes(ymin=..y.., ymax=..y.., color =RDK_isattended), geom='errorbar', width=0.9, size=1.5) +
  scale_x_discrete("RDK_isattended", breaks=waiver(), labels = rep(c(""),1,2)) +
  # theme(legend.position="bottom") +
  ylab(expression(paste("amplitude diff in muV/cm²")))+
  scale_fill_manual(values=c("steelblue2", "#F03F3F"))+
  scale_color_manual(values=c("steelblue2", "#F03F3F"))+
  #  scale_fill_manual(values=c("#193A3D", "#F03F3F"))+
  # scale_color_manual(values=c("#193A3D", "#F03F3F"))+
  # scale_fill_manual(values=c(rgb2hex(0.0, 153.0, 204.0),rgb2hex(0.0, 77, 102.0)))+
  # scale_color_manual(values=c(rgb2hex(0.0, 153.0, 204.0),rgb2hex(0.0, 77, 102.0)))+
  theme(legend.position="none")+
  # scale_y_continuous(limits=c(-60, 140))
  scale_y_continuous(limits=yax_limits)


plot2 <- ggplot(dat2plot, aes(y = subtraction_evoked, fill = RDK_isattended, x = 1)) +
  geom_flat_violin(aes(fill = RDK_isattended),position = position_nudge(x = .1, y = 0), 
                   adjust = 1.3, trim = FALSE, alpha = 1, colour = NA)+
  geom_hline(yintercept=0, show.legend = FALSE) +
  # scale_fill_manual(values=c("#193A3D", "#F03F3F"))+
  # scale_color_manual(values=c("#193A3D", "#F03F3F"))+
  scale_fill_manual(values=c("steelblue2", "#F03F3F"))+
  scale_color_manual(values=c("steelblue2", "#F03F3F"))+
  # scale_fill_manual(values=c(rgb2hex(0.0, 153.0, 204.0),rgb2hex(0.0, 77, 102.0)))+
  # scale_color_manual(values=c(rgb2hex(0.0, 153.0, 204.0),rgb2hex(0.0, 77, 102.0)))+
  theme(axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank())+
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+
  # scale_y_continuous(limits=c(-60, 140))
  scale_y_continuous(limits=yax_limits)



# cowplot::plot_grid(plot1, plot2, plot3, ncol = 3,labels = "AUTO")
plotttitle <- ggdraw() + 
  draw_label("SSVEP diff. | evoked \ncentral RDKs | isoluminant to background", fontface='bold', size = 10)
plotplots <- ggarrange(plot1, plot2,ncol = 2,common.legend = TRUE,align = "h", widths=c(3,1))

savefig <- multi_panel_figure(columns = 1, rows = 1, panel_label_type = "none", width = 3.5, height = 5, unit = "in")
saveplot <- ggarrange(plotttitle, plotplots, nrow = 2, heights=c(0.2, 1))

savefig %<>%
  fill_panel(saveplot, column = 1, row = 1)
savefig
# save_multi_panel_figure(savefig, "figures/FFT_BeeSwarm_Mod_ALPHA_COL_34subs.eps")
```


### 1b ad1  Illustrate Data as is | center RDKs

some trouble shooting...plot both RDKs

<br>  

```{r plot_data_st_center_2a, results = "hide",  fig.height=4, fig.width=6, warning = FALSE}
#evoked raw#### for center

# set overall limits?
dat2plot <- DataIn %>%
  filter(RDK_position2=="center") %>%
  group_by(subjects, time, RDK_isattended, RDK_colorlum, RDK_id)%>%
  summarise(amplitude_evoked=mean(amplitude_evoked), modulation_evoked=mean(modulation_evoked), subtraction_evoked = mean(subtraction_evoked))%>%
  filter(time=='[0.5 1.5] ', RDK_colorlum == 'isolum__to_bckgrd')

# set limits
yax_limits <- c( min(dat2plot$modulation_evoked), max(dat2plot$modulation_evoked))
yax_limits <- round(yax_limits + c(-1, 1)*diff(yax_limits)*0.1)
yax_limits <- yax_limits + c(-1, 1)*diff(yax_limits)*0.2


theme_set(theme_bw())
ggplot(dat2plot, aes(x = RDK_isattended, y = modulation_evoked, fill = RDK_isattended)) +
  geom_hline(yintercept=0, show.legend = FALSE) +
  geom_line(aes(group = interaction(subjects,time)),colour = "grey60",alpha = 1,size =0.5) +
  geom_beeswarm(aes(color = RDK_isattended, x = RDK_isattended,
                    group = RDK_isattended), cex=3, size = 5,alpha=1,fill="grey40",shape=21)+
  # geom_point(aes(color = RDK_isattended, x = interaction(time,RDK_isattended),
  #                   group = RDK_isattended), size = 4,alpha=0.4)+
  stat_summary(fun.y=mean, aes(ymin=..y.., ymax=..y.., color =RDK_isattended), geom='errorbar', width=0.9, size=1.5) +
  scale_x_discrete("RDK_isattended", breaks=waiver(), labels = rep(c(""),1,2)) +
  # theme(legend.position="bottom") +
  facet_grid(.~RDK_id)+
  ylab(expression(paste("amplitude modulation in %")))+
  scale_fill_manual(values=c("steelblue2", "#F03F3F"))+
  scale_color_manual(values=c("steelblue2", "#F03F3F"))+
  #  scale_fill_manual(values=c("#193A3D", "#F03F3F"))+
  # scale_color_manual(values=c("#193A3D", "#F03F3F"))+
  # scale_fill_manual(values=c(rgb2hex(0.0, 153.0, 204.0),rgb2hex(0.0, 77, 102.0)))+
  # scale_color_manual(values=c(rgb2hex(0.0, 153.0, 204.0),rgb2hex(0.0, 77, 102.0)))+
  theme(legend.position="none")+
  # scale_y_continuous(limits=c(-60, 140))
  scale_y_continuous(limits=yax_limits)

# set limits
yax_limits <- c( min(dat2plot$subtraction_evoked), max(dat2plot$subtraction_evoked))
yax_limits <- round(yax_limits + c(-1, 1)*diff(yax_limits)*0.1)
yax_limits <- yax_limits + c(-1, 1)*diff(yax_limits)*0.2


theme_set(theme_bw())
ggplot(dat2plot, aes(x = RDK_isattended, y = subtraction_evoked, fill = RDK_isattended)) +
  geom_hline(yintercept=0, show.legend = FALSE) +
  geom_line(aes(group = interaction(subjects,time)),colour = "grey60",alpha = 1,size =0.5) +
  geom_beeswarm(aes(color = RDK_isattended, x = RDK_isattended,
                    group = RDK_isattended), cex=3, size = 5,alpha=1,fill="grey40",shape=21)+
  # geom_point(aes(color = RDK_isattended, x = interaction(time,RDK_isattended),
  #                   group = RDK_isattended), size = 4,alpha=0.4)+
  stat_summary(fun.y=mean, aes(ymin=..y.., ymax=..y.., color =RDK_isattended), geom='errorbar', width=0.9, size=1.5) +
  scale_x_discrete("RDK_isattended", breaks=waiver(), labels = rep(c(""),1,2)) +
  # theme(legend.position="bottom") +
  facet_grid(.~RDK_id)+
  ylab(expression(paste("amplitude diff in muV/cm²")))+
  scale_fill_manual(values=c("steelblue2", "#F03F3F"))+
  scale_color_manual(values=c("steelblue2", "#F03F3F"))+
  #  scale_fill_manual(values=c("#193A3D", "#F03F3F"))+
  # scale_color_manual(values=c("#193A3D", "#F03F3F"))+
  # scale_fill_manual(values=c(rgb2hex(0.0, 153.0, 204.0),rgb2hex(0.0, 77, 102.0)))+
  # scale_color_manual(values=c(rgb2hex(0.0, 153.0, 204.0),rgb2hex(0.0, 77, 102.0)))+
  theme(legend.position="none")+
  # scale_y_continuous(limits=c(-60, 140))
  scale_y_continuous(limits=yax_limits)


# set overall limits?

dat2plot <- DataIn %>%
  filter(RDK_position2=="center") %>%
  group_by(subjects, time, RDK_isattended, RDK_colorlum, RDK_id, condition)%>%
  summarise(amplitude_evoked=mean(amplitude_evoked), modulation_evoked=mean(modulation_evoked), subtraction_evoked = mean(subtraction_evoked))%>%
  filter(time=='[0.5 1.5] ', RDK_colorlum == 'isolum__to_bckgrd')
yax_limits <- c( min(dat2plot$subtraction_evoked), max(dat2plot$subtraction_evoked))
yax_limits <- round(yax_limits + c(-1, 1)*diff(yax_limits)*0.1)
yax_limits <- yax_limits + c(-1, 1)*diff(yax_limits)*0.2


theme_set(theme_bw())
ggplot(dat2plot, aes(x = condition, y = subtraction_evoked, fill = RDK_isattended)) +
  geom_hline(yintercept=0, show.legend = FALSE) +
  geom_line(aes(group = interaction(subjects,time)),colour = "grey60",alpha = 1,size =0.5) +
  geom_beeswarm(aes(color = RDK_isattended, x = condition,
                    group = condition), cex=3, size = 4,alpha=1,fill="grey40",shape=21)+
  # geom_point(aes(color = RDK_isattended, x = interaction(time,RDK_isattended),
  #                   group = RDK_isattended), size = 4,alpha=0.4)+
  stat_summary(fun.y=mean, aes(ymin=..y.., ymax=..y.., color =RDK_isattended), geom='errorbar', width=0.9, size=1.5) +
  scale_x_discrete("RDK_isattended", breaks=waiver(), labels = rep(c(""),1,2)) +
  # theme(legend.position="bottom") +
  facet_grid(.~RDK_id)+
  ylab(expression(paste("amplitude diff in muV/cm²")))+
  scale_fill_manual(values=c("steelblue2", "#F03F3F"))+
  scale_color_manual(values=c("steelblue2", "#F03F3F"))+
  #  scale_fill_manual(values=c("#193A3D", "#F03F3F"))+
  # scale_color_manual(values=c("#193A3D", "#F03F3F"))+
  # scale_fill_manual(values=c(rgb2hex(0.0, 153.0, 204.0),rgb2hex(0.0, 77, 102.0)))+
  # scale_color_manual(values=c(rgb2hex(0.0, 153.0, 204.0),rgb2hex(0.0, 77, 102.0)))+
  theme(legend.position="none")+
  # scale_y_continuous(limits=c(-60, 140))
  scale_y_continuous(limits=yax_limits)


dat2plot <- DataIn %>%
  filter(RDK_position2=="center") %>%
  group_by(subjects, time, RDK_isattended, RDK_colorlum, RDK_id, condition)%>%
  summarise(amplitude_evoked=mean(amplitude_evoked), modulation_evoked=mean(modulation_evoked), subtraction_evoked = mean(subtraction_evoked))%>%
  filter(time=='[0.5 1.5] ', RDK_colorlum == 'isolum__to_bckgrd')
yax_limits <- c( min(dat2plot$modulation_evoked), max(dat2plot$modulation_evoked))
yax_limits <- round(yax_limits + c(-1, 1)*diff(yax_limits)*0.1)
yax_limits <- yax_limits + c(-1, 1)*diff(yax_limits)*0.2


theme_set(theme_bw())
ggplot(dat2plot, aes(x = condition, y = modulation_evoked, fill = RDK_isattended)) +
  geom_hline(yintercept=0, show.legend = FALSE) +
  geom_line(aes(group = interaction(subjects,time)),colour = "grey60",alpha = 1,size =0.5) +
  geom_beeswarm(aes(color = RDK_isattended, x = condition,
                    group = condition), cex=3, size = 4,alpha=1,fill="grey40",shape=21)+
  # geom_point(aes(color = RDK_isattended, x = interaction(time,RDK_isattended),
  #                   group = RDK_isattended), size = 4,alpha=0.4)+
  stat_summary(fun.y=mean, aes(ymin=..y.., ymax=..y.., color =RDK_isattended), geom='errorbar', width=0.9, size=1.5) +
  scale_x_discrete("RDK_isattended", breaks=waiver(), labels = rep(c(""),1,2)) +
  # theme(legend.position="bottom") +
  facet_grid(.~RDK_id)+
  ylab(expression(paste("modulation in %")))+
  scale_fill_manual(values=c("steelblue2", "#F03F3F"))+
  scale_color_manual(values=c("steelblue2", "#F03F3F"))+
  #  scale_fill_manual(values=c("#193A3D", "#F03F3F"))+
  # scale_color_manual(values=c("#193A3D", "#F03F3F"))+
  # scale_fill_manual(values=c(rgb2hex(0.0, 153.0, 204.0),rgb2hex(0.0, 77, 102.0)))+
  # scale_color_manual(values=c(rgb2hex(0.0, 153.0, 204.0),rgb2hex(0.0, 77, 102.0)))+
  theme(legend.position="none")+
  # scale_y_continuous(limits=c(-60, 140))
  scale_y_continuous(limits=yax_limits)


# corrdata <- DataIn %>%
#   mutate(sign_modulation = sign(modulation_evoked), sign_subtraction=sign(subtraction_evoked) )
# 
# ggscatter(corrdat3, 
#           x = "POS", 
#           y = "POS_X_COL", 
#           size = 2,
#           palette = "jco",
#           add = "reg.line",
#           conf.int = TRUE) +
#   # stat_cor(aes(color = con_RDK_col_attended), method = "spearman", label.y = 60) +
#   stat_cor( method = "spearman") +
#   # stat_cor(aes(color = con_RDK_col_attended), method = "pearson", label.y = 60) + 
#   ggtitle("Spearman Rank Correlations | amplitude modulations separate for pos.")
```



### 2a  Illustrate Data as is | peri RDKs

<br>  

```{r plot_data_st_peri, results = "hide",  fig.height=3, fig.width=6, warning = FALSE}
#evoked raw#### for center
dat2plot <- DataIn %>%
  filter(RDK_position2=="peri") %>%
  filter(RDK_ispresented=="presented")%>%
  group_by(subjects, time, RDK_isattended, RDK_colorlum)%>%
  summarise(amplitude_evoked=mean(amplitude_evoked), modulation_evoked=mean(modulation_evoked))

theme_set(theme_bw())
ggplot(dat2plot, aes(x = interaction(time,RDK_isattended), y = amplitude_evoked, fill = RDK_isattended)) +
  # geom_hline(yintercept=0, show.legend = FALSE) +
  geom_line(aes(group = interaction(subjects,RDK_isattended)),colour = "grey60",alpha = 0.5,size =0.5) +
  geom_beeswarm(aes(color = RDK_isattended, x = interaction(time,RDK_isattended),
                    group = RDK_isattended), cex=2, size = 4,alpha=1,fill="grey40",shape=21)+
  # geom_point(aes(color = condition, x = interaction(time,condition),
  #                   group = condition), size = 4,alpha=0.4)+
  stat_summary(fun.y=mean, aes(ymin=..y.., ymax=..y.., color =RDK_isattended), geom='errorbar', width=0.9, size=1.5) +
  scale_x_discrete("time windows in s", breaks=waiver(), labels = rep(c("[-1 0]","[0.5 1.5]","[1 2]"),1,9)) +
  facet_grid(.~RDK_colorlum)+
  theme(legend.position="bottom") +
  ylab(expression(paste("amplitude in muV")))+
  labs(title=sprintf("SSVEP amplitudes | evoked"),
       subtitle="collapsed across frequencies")+
  scale_fill_brewer(palette = "Dark2")+
  scale_color_brewer(palette = "Dark2")


theme_set(theme_bw())
ggplot(dat2plot, aes(x = interaction(time,RDK_isattended), y = modulation_evoked, fill = RDK_isattended)) +
  # geom_hline(yintercept=0, show.legend = FALSE) +
  geom_line(aes(group = interaction(subjects,RDK_isattended)),colour = "grey60",alpha = 0.5,size =0.5) +
  geom_beeswarm(aes(color = RDK_isattended, x = interaction(time,RDK_isattended),
                    group = RDK_isattended), cex=2, size = 4,alpha=1,fill="grey40",shape=21)+
  # geom_point(aes(color = condition, x = interaction(time,condition),
  #                   group = condition), size = 4,alpha=0.4)+
  stat_summary(fun.y=mean, aes(ymin=..y.., ymax=..y.., color =RDK_isattended), geom='errorbar', width=0.9, size=1.5) +
  scale_x_discrete("time windows in s", breaks=waiver(), labels = rep(c("[-1 0]","[0.5 1.5]","[1 2]"),1,9)) +
  facet_grid(.~RDK_colorlum)+
  theme(legend.position="bottom") +
  ylab(expression(paste("modulation in %")))+
  labs(title=sprintf("SSVEP amplitudes | evoked"),
       subtitle="collapsed across frequencies")+
  scale_fill_brewer(palette = "Dark2")+
  scale_color_brewer(palette = "Dark2")
```

### 2b  Illustrate Data as is | peri RDKs

plot differently

<br>  


```{r plot_data_st_peri_2, results = "hide",  fig.height=5.5, fig.width=4, warning = FALSE}
#evoked raw#### for periphery
# general ylims
dat2plot <- DataIn %>%
  filter(RDK_position2=="peri") %>%
  filter(RDK_ispresented=="presented")%>%
  group_by(subjects, time, RDK_isattended, RDK_colorlum)%>%
  summarise(amplitude_evoked=mean(amplitude_evoked), modulation_evoked=mean(modulation_evoked), subtraction_evoked=mean(subtraction_evoked))%>%
  filter(time=='[0.5 1.5] ')

# set limits
yax_limits <- c( min(dat2plot$modulation_evoked), max(dat2plot$modulation_evoked))
yax_limits <- round(yax_limits + c(-1, 1)*diff(yax_limits)*0.1)
# yax_limits <- yax_limits + c(-1, 1)*diff(yax_limits)*0.2
# yax_limits <- c(-27, 15)


dat2plot <- DataIn %>%
  filter(RDK_position2=="peri") %>%
  filter(RDK_ispresented=="presented")%>%
  group_by(subjects, time, RDK_isattended, RDK_colorlum)%>%
  summarise(amplitude_evoked=mean(amplitude_evoked), modulation_evoked=mean(modulation_evoked))%>%
  filter(time=='[0.5 1.5] ', RDK_colorlum == 'offset_to_bckgrd')


theme_set(theme_bw())
plot1 <- ggplot(dat2plot, aes(x = RDK_isattended, y = modulation_evoked, fill = RDK_isattended)) +
  geom_hline(yintercept=0, show.legend = FALSE) +
  geom_line(aes(group = interaction(subjects,time)),colour = "grey60",alpha = 1,size =0.5) +
  geom_beeswarm(aes(color = RDK_isattended, x = RDK_isattended,
                    group = RDK_isattended), cex=3, size = 5,alpha=1,fill="grey40",shape=21)+
  # geom_point(aes(color = RDK_isattended, x = interaction(time,RDK_isattended),
  #                   group = RDK_isattended), size = 4,alpha=0.4)+
  stat_summary(fun.y=mean, aes(ymin=..y.., ymax=..y.., color =RDK_isattended), geom='errorbar', width=0.9, size=1.5) +
  scale_x_discrete("RDK_isattended", breaks=waiver(), labels = rep(c(""),1,3)) +
  # theme(legend.position="bottom") +
  ylab(expression(paste("amplitude modulation in %")))+
  scale_fill_manual(values=c("#F1831A", "#293C4A", "#198A83"))+
  scale_color_manual(values=c("#F1831A", "#293C4A", "#198A83"))+
  theme(legend.position="none")+
  # scale_y_continuous(limits=c(-60, 140))
  scale_y_continuous(limits=yax_limits)


plot2 <- ggplot(dat2plot, aes(y = modulation_evoked, fill = RDK_isattended, x = 1)) +
  geom_flat_violin(aes(fill = RDK_isattended),position = position_nudge(x = .1, y = 0), 
                   adjust = 1.3, trim = FALSE, alpha = 1, colour = NA)+
  geom_hline(yintercept=0, show.legend = FALSE) +
  scale_fill_manual(values=c("#F1831A", "#293C4A", "#198A83"))+
  scale_color_manual(values=c("#F1831A", "#293C4A", "#198A83"))+
  theme(axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank())+
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+
  # scale_y_continuous(limits=c(-60, 140))
  scale_y_continuous(limits=yax_limits)



# cowplot::plot_grid(plot1, plot2, plot3, ncol = 3,labels = "AUTO")
plotttitle <- ggdraw() + 
  draw_label("SSVEP mod. | evoked \nperi RDKs | luminance offset", fontface='bold', size = 10)
plotplots <- ggarrange(plot1, plot2,ncol = 2,common.legend = TRUE,align = "h", widths=c(3,1))

savefig <- multi_panel_figure(columns = 1, rows = 1, panel_label_type = "none", width = 4, height = 5.5, unit = "in")
saveplot <- ggarrange(plotttitle, plotplots, nrow = 2, heights=c(0.2, 1))

savefig %<>%
  fill_panel(saveplot, column = 1, row = 1)
savefig
# save_multi_panel_figure(savefig, "figures/FFT_BeeSwarm_Mod_ALPHA_COL_34subs.eps")


dat2plot <- DataIn %>%
  filter(RDK_position2=="peri") %>%
  filter(RDK_ispresented=="presented")%>%
  group_by(subjects, time, RDK_isattended, RDK_colorlum)%>%
  summarise(amplitude_evoked=mean(amplitude_evoked), modulation_evoked=mean(modulation_evoked))%>%
  filter(time=='[0.5 1.5] ', RDK_colorlum == 'isolum__to_bckgrd')


theme_set(theme_bw())
plot1 <- ggplot(dat2plot, aes(x = RDK_isattended, y = modulation_evoked, fill = RDK_isattended)) +
  geom_hline(yintercept=0, show.legend = FALSE) +
  geom_line(aes(group = interaction(subjects,time)),colour = "grey60",alpha = 1,size =0.5) +
  geom_beeswarm(aes(color = RDK_isattended, x = RDK_isattended,
                    group = RDK_isattended), cex=3, size = 5,alpha=1,fill="grey40",shape=21)+
  # geom_point(aes(color = RDK_isattended, x = interaction(time,RDK_isattended),
  #                   group = RDK_isattended), size = 4,alpha=0.4)+
  stat_summary(fun.y=mean, aes(ymin=..y.., ymax=..y.., color =RDK_isattended), geom='errorbar', width=0.9, size=1.5) +
  scale_x_discrete("RDK_isattended", breaks=waiver(), labels = rep(c(""),1,3)) +
  # theme(legend.position="bottom") +
  ylab(expression(paste("amplitude modulation in %")))+
  scale_fill_manual(values=c("#F1831A", "#293C4A", "#198A83"))+
  scale_color_manual(values=c("#F1831A", "#293C4A", "#198A83"))+
  theme(legend.position="none")+
  # scale_y_continuous(limits=c(-60, 140))
  scale_y_continuous(limits=yax_limits)


plot2 <- ggplot(dat2plot, aes(y = modulation_evoked, fill = RDK_isattended, x = 1)) +
  geom_flat_violin(aes(fill = RDK_isattended),position = position_nudge(x = .1, y = 0), 
                   adjust = 1.3, trim = FALSE, alpha = 1, colour = NA)+
  geom_hline(yintercept=0, show.legend = FALSE) +
  scale_fill_manual(values=c("#F1831A", "#293C4A", "#198A83"))+
  scale_color_manual(values=c("#F1831A", "#293C4A", "#198A83"))+
  theme(axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank())+
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+
  # scale_y_continuous(limits=c(-60, 140))
  scale_y_continuous(limits=yax_limits)



# cowplot::plot_grid(plot1, plot2, plot3, ncol = 3,labels = "AUTO")
plotttitle <- ggdraw() + 
  draw_label("SSVEP mod. | evoked \nperi RDKs | isoluminant to background", fontface='bold', size = 10)
plotplots <- ggarrange(plot1, plot2,ncol = 2,common.legend = TRUE,align = "h", widths=c(3,1))

savefig <- multi_panel_figure(columns = 1, rows = 1, panel_label_type = "none", width = 4, height = 5.5, unit = "in")
saveplot <- ggarrange(plotttitle, plotplots, nrow = 2, heights=c(0.2, 1))

savefig %<>%
  fill_panel(saveplot, column = 1, row = 1)
savefig
# save_multi_panel_figure(savefig, "figures/FFT_BeeSwarm_Mod_ALPHA_COL_34subs.eps")


# plot difference
dat2plot <- DataIn %>%
  filter(RDK_position2=="peri") %>%
  filter(RDK_ispresented=="presented")%>%
  group_by(subjects, time, RDK_isattended, RDK_colorlum)%>%
  summarise(subtraction_evoked=mean(subtraction_evoked), modulation_evoked=mean(modulation_evoked))%>%
  filter(time=='[0.5 1.5] ', RDK_colorlum == 'offset_to_bckgrd')

# set limits
yax_limits <- c( min(dat2plot$subtraction_evoked), max(dat2plot$subtraction_evoked))
# yax_limits <- round(yax_limits + c(-1, 1)*diff(yax_limits)*0.1)
yax_limits <- yax_limits + c(-1, 1)*diff(yax_limits)*0.2
# yax_limits <- c(-27, 15)

theme_set(theme_bw())
plot1 <- ggplot(dat2plot, aes(x = RDK_isattended, y = subtraction_evoked, fill = RDK_isattended)) +
  geom_hline(yintercept=0, show.legend = FALSE) +
  geom_line(aes(group = interaction(subjects,time)),colour = "grey60",alpha = 1,size =0.5) +
  geom_beeswarm(aes(color = RDK_isattended, x = RDK_isattended,
                    group = RDK_isattended), cex=3, size = 5,alpha=1,fill="grey40",shape=21)+
  # geom_point(aes(color = RDK_isattended, x = interaction(time,RDK_isattended),
  #                   group = RDK_isattended), size = 4,alpha=0.4)+
  stat_summary(fun.y=mean, aes(ymin=..y.., ymax=..y.., color =RDK_isattended), geom='errorbar', width=0.9, size=1.5) +
  scale_x_discrete("RDK_isattended", breaks=waiver(), labels = rep(c(""),1,3)) +
  # theme(legend.position="bottom") +
  ylab(expression(paste("amplitude diff in muV/cm²")))+
  scale_fill_manual(values=c("#F1831A", "#293C4A", "#198A83"))+
  scale_color_manual(values=c("#F1831A", "#293C4A", "#198A83"))+
  theme(legend.position="none")+
  # scale_y_continuous(limits=c(-60, 140))
  scale_y_continuous(limits=yax_limits)


plot2 <- ggplot(dat2plot, aes(y = subtraction_evoked, fill = RDK_isattended, x = 1)) +
  geom_flat_violin(aes(fill = RDK_isattended),position = position_nudge(x = .1, y = 0), 
                   adjust = 1.3, trim = FALSE, alpha = 1, colour = NA)+
  geom_hline(yintercept=0, show.legend = FALSE) +
  scale_fill_manual(values=c("#F1831A", "#293C4A", "#198A83"))+
  scale_color_manual(values=c("#F1831A", "#293C4A", "#198A83"))+
  theme(axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank())+
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+
  # scale_y_continuous(limits=c(-60, 140))
  scale_y_continuous(limits=yax_limits)



# cowplot::plot_grid(plot1, plot2, plot3, ncol = 3,labels = "AUTO")
plotttitle <- ggdraw() + 
  draw_label("SSVEP mod. | evoked \nperi RDKs | luminance offset", fontface='bold', size = 10)
plotplots <- ggarrange(plot1, plot2,ncol = 2,common.legend = TRUE,align = "h", widths=c(3,1))

savefig <- multi_panel_figure(columns = 1, rows = 1, panel_label_type = "none", width = 4, height = 5.5, unit = "in")
saveplot <- ggarrange(plotttitle, plotplots, nrow = 2, heights=c(0.2, 1))

savefig %<>%
  fill_panel(saveplot, column = 1, row = 1)
savefig
# save_multi_panel_figure(savefig, "figures/FFT_BeeSwarm_Mod_ALPHA_COL_34subs.eps")


dat2plot <- DataIn %>%
  filter(RDK_position2=="peri") %>%
  filter(RDK_ispresented=="presented")%>%
  group_by(subjects, time, RDK_isattended, RDK_colorlum)%>%
  summarise(subtraction_evoked=mean(subtraction_evoked), modulation_evoked=mean(modulation_evoked))%>%
  filter(time=='[0.5 1.5] ', RDK_colorlum == 'isolum__to_bckgrd')

# set limits
yax_limits <- c( min(dat2plot$subtraction_evoked), max(dat2plot$subtraction_evoked))
# yax_limits <- round(yax_limits + c(-1, 1)*diff(yax_limits)*0.1)
yax_limits <- yax_limits + c(-1, 1)*diff(yax_limits)*0.2
# yax_limits <- c(-27, 15)


theme_set(theme_bw())
plot1 <- ggplot(dat2plot, aes(x = RDK_isattended, y = subtraction_evoked, fill = RDK_isattended)) +
  geom_hline(yintercept=0, show.legend = FALSE) +
  geom_line(aes(group = interaction(subjects,time)),colour = "grey60",alpha = 1,size =0.5) +
  geom_beeswarm(aes(color = RDK_isattended, x = RDK_isattended,
                    group = RDK_isattended), cex=3, size = 5,alpha=1,fill="grey40",shape=21)+
  # geom_point(aes(color = RDK_isattended, x = interaction(time,RDK_isattended),
  #                   group = RDK_isattended), size = 4,alpha=0.4)+
  stat_summary(fun.y=mean, aes(ymin=..y.., ymax=..y.., color =RDK_isattended), geom='errorbar', width=0.9, size=1.5) +
  scale_x_discrete("RDK_isattended", breaks=waiver(), labels = rep(c(""),1,3)) +
  # theme(legend.position="bottom") +
  ylab(expression(paste("amplitude diff in muV/cm²")))+
  scale_fill_manual(values=c("#F1831A", "#293C4A", "#198A83"))+
  scale_color_manual(values=c("#F1831A", "#293C4A", "#198A83"))+
  theme(legend.position="none")+
  # scale_y_continuous(limits=c(-60, 140))
  scale_y_continuous(limits=yax_limits)


plot2 <- ggplot(dat2plot, aes(y = subtraction_evoked, fill = RDK_isattended, x = 1)) +
  geom_flat_violin(aes(fill = RDK_isattended),position = position_nudge(x = .1, y = 0), 
                   adjust = 1.3, trim = FALSE, alpha = 1, colour = NA)+
  geom_hline(yintercept=0, show.legend = FALSE) +
  scale_fill_manual(values=c("#F1831A", "#293C4A", "#198A83"))+
  scale_color_manual(values=c("#F1831A", "#293C4A", "#198A83"))+
  theme(axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank())+
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+
  # scale_y_continuous(limits=c(-60, 140))
  scale_y_continuous(limits=yax_limits)



# cowplot::plot_grid(plot1, plot2, plot3, ncol = 3,labels = "AUTO")
plotttitle <- ggdraw() + 
  draw_label("SSVEP diff. | evoked \nperi RDKs | isoluminant to background", fontface='bold', size = 10)
plotplots <- ggarrange(plot1, plot2,ncol = 2,common.legend = TRUE,align = "h", widths=c(3,1))

savefig <- multi_panel_figure(columns = 1, rows = 1, panel_label_type = "none", width = 4, height = 5.5, unit = "in")
saveplot <- ggarrange(plotttitle, plotplots, nrow = 2, heights=c(0.2, 1))

savefig %<>%
  fill_panel(saveplot, column = 1, row = 1)
savefig
# save_multi_panel_figure(savefig, "figures/FFT_BeeSwarm_Mod_ALPHA_COL_34subs.eps")

```

### 2c  Illustrate Data as is | peri RDKs

plot all conditions

<br>  


```{r plot_data_st_peri_3, results = "hide",  fig.height=6, fig.width=6, warning = FALSE}

#evoked raw#### for periphery
dat2plot <- DataIn %>%
  filter(RDK_position2=="peri") %>%
  filter(RDK_ispresented=="presented")%>%
  group_by(subjects, time, RDK_isattended2, RDK_colorlum)%>%
  summarise(amplitude_evoked=mean(amplitude_evoked), modulation_evoked=mean(modulation_evoked))%>%
  filter(time=='[0.5 1.5] ')


# set general limits
yax_limits <- c( min(dat2plot$modulation_evoked), max(dat2plot$modulation_evoked))
yax_limits <- round(yax_limits + c(-1, 1)*diff(yax_limits)*0.1)
# yax_limits <- yax_limits + c(-1, 1)*diff(yax_limits)*0.2
# yax_limits <- c(-27, 15)


dat2plot <- DataIn %>%
  filter(RDK_position2=="peri") %>%
  filter(RDK_ispresented=="presented")%>%
  group_by(subjects, time, RDK_isattended2, RDK_colorlum)%>%
  summarise(amplitude_evoked=mean(amplitude_evoked), modulation_evoked=mean(modulation_evoked))%>%
  filter(time=='[0.5 1.5] ', RDK_colorlum == 'offset_to_bckgrd')

theme_set(theme_bw())
plot1 <- ggplot(dat2plot, aes(x = RDK_isattended2, y = modulation_evoked, fill = RDK_isattended2)) +
  geom_hline(yintercept=0, show.legend = FALSE) +
  geom_line(aes(group = interaction(subjects,time)),colour = "grey60",alpha = 1,size =0.5) +
  geom_beeswarm(aes(color = RDK_isattended2, x = RDK_isattended2,
                    group = RDK_isattended2), cex=2, size = 5,alpha=1,fill="grey40",shape=21)+
  # geom_point(aes(color = RDK_isattended2, x = interaction(time,RDK_isattended),
  #                   group = RDK_isattended2), size = 4,alpha=0.4)+
  stat_summary(fun.y=mean, aes(ymin=..y.., ymax=..y.., color =RDK_isattended2), geom='errorbar', width=0.9, size=1.5) +
  scale_x_discrete("RDK_isattended2", breaks=waiver(), labels = rep(c(""),1,6)) +
  # theme(legend.position="bottom") +
  ylab(expression(paste("amplitude modulation in %")))+
  scale_fill_brewer(palette = "Dark2")+
  scale_color_brewer(palette = "Dark2")+
  theme(legend.position="none")+
  # scale_y_continuous(limits=c(-60, 140))
  scale_y_continuous(limits=yax_limits)

plot2 <- ggplot(dat2plot, aes(y = modulation_evoked, fill = RDK_isattended2, x = 1)) +
  geom_flat_violin(aes(fill = RDK_isattended2),position = position_nudge(x = .1, y = 0), 
                   adjust = 1.3, trim = FALSE, alpha = 1, colour = NA)+
  geom_hline(yintercept=0, show.legend = FALSE) +
  scale_fill_brewer(palette = "Dark2")+
  scale_color_brewer(palette = "Dark2")+
  theme(axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank())+
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+
  # scale_y_continuous(limits=c(-60, 140))
  scale_y_continuous(limits=yax_limits)



# cowplot::plot_grid(plot1, plot2, plot3, ncol = 3,labels = "AUTO")
plotttitle <- ggdraw() + 
  draw_label("SSVEP mod. | evoked \nperi RDKs | luminance offset", fontface='bold', size = 10)
plotplots <- ggarrange(plot1, plot2,ncol = 2,common.legend = TRUE,align = "h", widths=c(3,1))

savefig <- multi_panel_figure(columns = 1, rows = 1, panel_label_type = "none", width = 6, height = 6, unit = "in")
saveplot <- ggarrange(plotttitle, plotplots, nrow = 2, heights=c(0.2, 1))

savefig %<>%
  fill_panel(saveplot, column = 1, row = 1)
savefig
# save_multi_panel_figure(savefig, "figures/FFT_BeeSwarm_Mod_ALPHA_COL_34subs.eps")



dat2plot <- DataIn %>%
  filter(RDK_position2=="peri") %>%
  filter(RDK_ispresented=="presented")%>%
  group_by(subjects, time, RDK_isattended2, RDK_colorlum)%>%
  summarise(amplitude_evoked=mean(amplitude_evoked), modulation_evoked=mean(modulation_evoked))%>%
  filter(time=='[0.5 1.5] ', RDK_colorlum == 'isolum__to_bckgrd')

theme_set(theme_bw())
plot1 <- ggplot(dat2plot, aes(x = RDK_isattended2, y = modulation_evoked, fill = RDK_isattended2)) +
  geom_hline(yintercept=0, show.legend = FALSE) +
  geom_line(aes(group = interaction(subjects,time)),colour = "grey60",alpha = 1,size =0.5) +
  geom_beeswarm(aes(color = RDK_isattended2, x = RDK_isattended2,
                    group = RDK_isattended2), cex=2, size = 5,alpha=1,fill="grey40",shape=21)+
  # geom_point(aes(color = RDK_isattended2, x = interaction(time,RDK_isattended),
  #                   group = RDK_isattended2), size = 4,alpha=0.4)+
  stat_summary(fun.y=mean, aes(ymin=..y.., ymax=..y.., color =RDK_isattended2), geom='errorbar', width=0.9, size=1.5) +
  scale_x_discrete("RDK_isattended2", breaks=waiver(), labels = rep(c(""),1,6)) +
  # theme(legend.position="bottom") +
  ylab(expression(paste("amplitude modulation in %")))+
  scale_fill_brewer(palette = "Dark2")+
  scale_color_brewer(palette = "Dark2")+
  theme(legend.position="none")+
  # scale_y_continuous(limits=c(-60, 140))
  scale_y_continuous(limits=yax_limits)

plot2 <- ggplot(dat2plot, aes(y = modulation_evoked, fill = RDK_isattended2, x = 1)) +
  geom_flat_violin(aes(fill = RDK_isattended2),position = position_nudge(x = .1, y = 0), 
                   adjust = 1.3, trim = FALSE, alpha = 1, colour = NA)+
  geom_hline(yintercept=0, show.legend = FALSE) +
  scale_fill_brewer(palette = "Dark2")+
  scale_color_brewer(palette = "Dark2")+
  theme(axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank())+
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+
  # scale_y_continuous(limits=c(-60, 140))
  scale_y_continuous(limits=yax_limits)



# cowplot::plot_grid(plot1, plot2, plot3, ncol = 3,labels = "AUTO")
plotttitle <- ggdraw() + 
  draw_label("SSVEP mod. | evoked \nperi RDKs | isoluminant to background", fontface='bold', size = 10)
plotplots <- ggarrange(plot1, plot2,ncol = 2,common.legend = TRUE,align = "h", widths=c(3,1))

savefig <- multi_panel_figure(columns = 1, rows = 1, panel_label_type = "none", width = 6, height = 6, unit = "in")
saveplot <- ggarrange(plotttitle, plotplots, nrow = 2, heights=c(0.2, 1))

savefig %<>%
  fill_panel(saveplot, column = 1, row = 1)
savefig
# save_multi_panel_figure(savefig, "figures/FFT_BeeSwarm_Mod_ALPHA_COL_34subs.eps")


###
# plot difference
####
#evoked raw#### for periphery
dat2plot <- DataIn %>%
  filter(RDK_position2=="peri") %>%
  filter(RDK_ispresented=="presented")%>%
  group_by(subjects, time, RDK_isattended2, RDK_colorlum)%>%
  summarise(subtraction_evoked=mean(subtraction_evoked), modulation_evoked=mean(modulation_evoked))%>%
  filter(time=='[0.5 1.5] ', RDK_colorlum == 'offset_to_bckgrd')

# set general limits
yax_limits <- c( min(dat2plot$subtraction_evoked), max(dat2plot$subtraction_evoked))
# yax_limits <- round(yax_limits + c(-1, 1)*diff(yax_limits)*0.1)
yax_limits <- yax_limits + c(-1, 1)*diff(yax_limits)*0.2
# yax_limits <- c(-27, 15)

theme_set(theme_bw())
plot1 <- ggplot(dat2plot, aes(x = RDK_isattended2, y = subtraction_evoked, fill = RDK_isattended2)) +
  geom_hline(yintercept=0, show.legend = FALSE) +
  geom_line(aes(group = interaction(subjects,time)),colour = "grey60",alpha = 1,size =0.5) +
  geom_beeswarm(aes(color = RDK_isattended2, x = RDK_isattended2,
                    group = RDK_isattended2), cex=2, size = 5,alpha=1,fill="grey40",shape=21)+
  # geom_point(aes(color = RDK_isattended2, x = interaction(time,RDK_isattended),
  #                   group = RDK_isattended2), size = 4,alpha=0.4)+
  stat_summary(fun.y=mean, aes(ymin=..y.., ymax=..y.., color =RDK_isattended2), geom='errorbar', width=0.9, size=1.5) +
  scale_x_discrete("RDK_isattended2", breaks=waiver(), labels = rep(c(""),1,6)) +
  # theme(legend.position="bottom") +
  ylab(expression(paste("amplitude diff in muV/cm²")))+
  scale_fill_brewer(palette = "Dark2")+
  scale_color_brewer(palette = "Dark2")+
  theme(legend.position="none")+
  # scale_y_continuous(limits=c(-60, 140))
  scale_y_continuous(limits=yax_limits)

plot2 <- ggplot(dat2plot, aes(y = subtraction_evoked, fill = RDK_isattended2, x = 1)) +
  geom_flat_violin(aes(fill = RDK_isattended2),position = position_nudge(x = .1, y = 0), 
                   adjust = 1.3, trim = FALSE, alpha = 1, colour = NA)+
  geom_hline(yintercept=0, show.legend = FALSE) +
  scale_fill_brewer(palette = "Dark2")+
  scale_color_brewer(palette = "Dark2")+
  theme(axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank())+
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+
  # scale_y_continuous(limits=c(-60, 140))
  scale_y_continuous(limits=yax_limits)



# cowplot::plot_grid(plot1, plot2, plot3, ncol = 3,labels = "AUTO")
plotttitle <- ggdraw() + 
  draw_label("SSVEP amp difference | evoked \nperi RDKs | luminance offset", fontface='bold', size = 10)
plotplots <- ggarrange(plot1, plot2,ncol = 2,common.legend = TRUE,align = "h", widths=c(3,1))

savefig <- multi_panel_figure(columns = 1, rows = 1, panel_label_type = "none", width = 6, height = 6, unit = "in")
saveplot <- ggarrange(plotttitle, plotplots, nrow = 2, heights=c(0.2, 1))

savefig %<>%
  fill_panel(saveplot, column = 1, row = 1)
savefig
# save_multi_panel_figure(savefig, "figures/FFT_BeeSwarm_Mod_ALPHA_COL_34subs.eps")



dat2plot <- DataIn %>%
  filter(RDK_position2=="peri") %>%
  filter(RDK_ispresented=="presented")%>%
  group_by(subjects, time, RDK_isattended2, RDK_colorlum)%>%
  summarise(subtraction_evoked=mean(subtraction_evoked), modulation_evoked=mean(modulation_evoked))%>%
  filter(time=='[0.5 1.5] ', RDK_colorlum == 'isolum__to_bckgrd')

# set general limits
yax_limits <- c( min(dat2plot$subtraction_evoked), max(dat2plot$subtraction_evoked))
# yax_limits <- round(yax_limits + c(-1, 1)*diff(yax_limits)*0.1)
yax_limits <- yax_limits + c(-1, 1)*diff(yax_limits)*0.2
# yax_limits <- c(-27, 15)

theme_set(theme_bw())
plot1 <- ggplot(dat2plot, aes(x = RDK_isattended2, y = subtraction_evoked, fill = RDK_isattended2)) +
  geom_hline(yintercept=0, show.legend = FALSE) +
  geom_line(aes(group = interaction(subjects,time)),colour = "grey60",alpha = 1,size =0.5) +
  geom_beeswarm(aes(color = RDK_isattended2, x = RDK_isattended2,
                    group = RDK_isattended2), cex=2, size = 5,alpha=1,fill="grey40",shape=21)+
  # geom_point(aes(color = RDK_isattended2, x = interaction(time,RDK_isattended),
  #                   group = RDK_isattended2), size = 4,alpha=0.4)+
  stat_summary(fun.y=mean, aes(ymin=..y.., ymax=..y.., color =RDK_isattended2), geom='errorbar', width=0.9, size=1.5) +
  scale_x_discrete("RDK_isattended2", breaks=waiver(), labels = rep(c(""),1,6)) +
  # theme(legend.position="bottom") +
  ylab(expression(paste("amplitude diff in muV/cm²")))+
  scale_fill_brewer(palette = "Dark2")+
  scale_color_brewer(palette = "Dark2")+
  theme(legend.position="none")+
  # scale_y_continuous(limits=c(-60, 140))
  scale_y_continuous(limits=yax_limits)

plot2 <- ggplot(dat2plot, aes(y = subtraction_evoked, fill = RDK_isattended2, x = 1)) +
  geom_flat_violin(aes(fill = RDK_isattended2),position = position_nudge(x = .1, y = 0), 
                   adjust = 1.3, trim = FALSE, alpha = 1, colour = NA)+
  geom_hline(yintercept=0, show.legend = FALSE) +
  scale_fill_brewer(palette = "Dark2")+
  scale_color_brewer(palette = "Dark2")+
  theme(axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank())+
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+
  # scale_y_continuous(limits=c(-60, 140))
  scale_y_continuous(limits=yax_limits)



# cowplot::plot_grid(plot1, plot2, plot3, ncol = 3,labels = "AUTO")
plotttitle <- ggdraw() + 
  draw_label("SSVEP amp difference | evoked \nperi RDKs | isoluminant to background", fontface='bold', size = 10)
plotplots <- ggarrange(plot1, plot2,ncol = 2,common.legend = TRUE,align = "h", widths=c(3,1))

savefig <- multi_panel_figure(columns = 1, rows = 1, panel_label_type = "none", width = 6, height = 6, unit = "in")
saveplot <- ggarrange(plotttitle, plotplots, nrow = 2, heights=c(0.2, 1))

savefig %<>%
  fill_panel(saveplot, column = 1, row = 1)
savefig
# save_multi_panel_figure(savefig, "figures/FFT_BeeSwarm_Mod_ALPHA_COL_34subs.eps")

```


### 2d  Illustrate Data as is | peri RDKs

plot all conditions in combination they were actually presented

<br>  


```{r plot_data_st_peri_4, results = "hide",  fig.height=5, fig.width=8, warning = FALSE}

#evoked raw#### for periphery
dat2plot <- DataIn %>%
  mutate(condition2 = case_when(
    (condition == 1 | condition == 2) ~ "peri_att_unatt",
    (condition == 3 | condition == 4) ~ "peri_att_irrel",
    (condition == 5 | condition == 6) ~ "peri_unatt_irrel",
  )) %>%
  filter(RDK_position2=="peri") %>%
  filter(RDK_ispresented=="presented")%>%
  group_by(subjects, time, RDK_isattended, RDK_colorlum, condition2)%>%
  summarise(amplitude_evoked=mean(amplitude_evoked), modulation_evoked=mean(modulation_evoked))%>%
  filter(time=='[0.5 1.5] ')


dat2plot2 <- dat2plot %>%
  filter(RDK_colorlum == 'offset_to_bckgrd')


theme_set(theme_bw())
ggplot(dat2plot2, aes(x = RDK_isattended, y = modulation_evoked, fill = RDK_isattended)) +
  geom_hline(yintercept=0, show.legend = FALSE) +
  geom_line(aes(group = interaction(subjects,time)),colour = "grey60",alpha = 1,size =0.5) +
  geom_beeswarm(aes(color = RDK_isattended, x = RDK_isattended,
                    group = RDK_isattended), cex=3, size = 5,alpha=1,fill="grey40",shape=21)+
  # geom_point(aes(color = RDK_isattended, x = interaction(time,RDK_isattended),
  #                   group = RDK_isattended), size = 4,alpha=0.4)+
  stat_summary(fun.y=mean, aes(ymin=..y.., ymax=..y.., color =RDK_isattended), geom='errorbar', width=0.9, size=1.5) +
  scale_x_discrete("RDK_isattended", breaks=waiver(), labels = rep(c(""),1,3)) +
  # theme(legend.position="bottom") +
  facet_grid(.~condition2)+
  ylab(expression(paste("amplitude mod in %")))+
  scale_fill_manual(values=c("#F1831A", "#293C4A", "#198A83"))+
  scale_color_manual(values=c("#F1831A", "#293C4A", "#198A83"))+
  labs(title=sprintf("SSVEP modulations | evoked | peri RDKs | luminance offset"),
       subtitle="collapsed across frequencies")
  # scale_y_continuous(limits=c(-60, 140))

dat2plot2 <- dat2plot %>%
  filter(RDK_colorlum == 'isolum__to_bckgrd')


theme_set(theme_bw())
ggplot(dat2plot2, aes(x = RDK_isattended, y = modulation_evoked, fill = RDK_isattended)) +
  geom_hline(yintercept=0, show.legend = FALSE) +
  geom_line(aes(group = interaction(subjects,time)),colour = "grey60",alpha = 1,size =0.5) +
  geom_beeswarm(aes(color = RDK_isattended, x = RDK_isattended,
                    group = RDK_isattended), cex=3, size = 5,alpha=1,fill="grey40",shape=21)+
  # geom_point(aes(color = RDK_isattended, x = interaction(time,RDK_isattended),
  #                   group = RDK_isattended), size = 4,alpha=0.4)+
  stat_summary(fun.y=mean, aes(ymin=..y.., ymax=..y.., color =RDK_isattended), geom='errorbar', width=0.9, size=1.5) +
  scale_x_discrete("RDK_isattended", breaks=waiver(), labels = rep(c(""),1,3)) +
  # theme(legend.position="bottom") +
  facet_grid(.~condition2)+
  ylab(expression(paste("amplitude mod in %")))+
  scale_fill_manual(values=c("#F1831A", "#293C4A", "#198A83"))+
  scale_color_manual(values=c("#F1831A", "#293C4A", "#198A83"))+
  labs(title=sprintf("SSVEP modulations | evoked | peri RDKs | isoluminant"),
       subtitle="collapsed across frequencies")
  # scale_y_continuous(limits=c(-60, 140))
```


### 3a  Illustrate Data as is | peri and center | general modulation

plot differently

<br>  

```{r plot_data_peri_precue, results = "hide",  fig.height=5, fig.width=3.5, warning = FALSE}
#evoked raw#### for center

# set overall limits?
dat2plot <- DataIn %>%
  filter(RDK_ispresented=="presented", RDK_colorlum=="isolum__to_bckgrd")%>%
  group_by(subjects, time, RDK_position2)%>%
  summarise(amplitude_evoked=mean(amplitude_evoked), modulation_evoked=mean(modulation_evoked))%>%
  filter(time == '[0.5 1.5] ')
# set limits
yax_limits <- c( min(dat2plot$modulation_evoked), max(dat2plot$modulation_evoked))
yax_limits <- round(yax_limits + c(-1, 1)*diff(yax_limits)*0.1)
yax_limits <- yax_limits + c(-1, 1)*diff(yax_limits)*0.1


theme_set(theme_bw())
plot1 <- ggplot(dat2plot, aes(x = RDK_position2, y = modulation_evoked, fill = RDK_position2)) +
  geom_hline(yintercept=0, show.legend = FALSE) +
  geom_line(aes(group = interaction(subjects,time)),colour = "grey60",alpha = 1,size =0.5) +
  geom_beeswarm(aes(color = RDK_position2, x = RDK_position2,
                    group = RDK_position2), cex=3, size = 5,alpha=1,fill="grey60",shape=21)+
  # geom_point(aes(color = RDK_isattended, x = interaction(time,RDK_isattended),
  #                   group = RDK_isattended), size = 4,alpha=0.4)+
  stat_summary(fun.y=mean, aes(ymin=..y.., ymax=..y.., color =RDK_position2), geom='errorbar', width=0.9, size=1.5) +
  scale_x_discrete("RDK position", breaks=waiver(), labels = rep(c(""),1,2)) +
  # theme(legend.position="bottom") +
  ylab(expression(paste("amplitude modulation in %")))+
  scale_fill_manual(values=c("seagreen", "plum4"))+
  scale_color_manual(values=c("seagreen", "plum4"))+
  #  scale_fill_manual(values=c("#193A3D", "#F03F3F"))+
  # scale_color_manual(values=c("#193A3D", "#F03F3F"))+
  # scale_fill_manual(values=c(rgb2hex(0.0, 153.0, 204.0),rgb2hex(0.0, 77, 102.0)))+
  # scale_color_manual(values=c(rgb2hex(0.0, 153.0, 204.0),rgb2hex(0.0, 77, 102.0)))+
  theme(legend.position="none")+
  # scale_y_continuous(limits=c(-60, 140))
  scale_y_continuous(limits=yax_limits)


plot2 <- ggplot(dat2plot, aes(y = modulation_evoked, fill = RDK_position2, x = 1)) +
  geom_flat_violin(aes(fill = RDK_position2),position = position_nudge(x = .1, y = 0), 
                   adjust = 1.3, trim = FALSE, alpha = 1, colour = NA)+
  geom_hline(yintercept=0, show.legend = FALSE) +
  # scale_fill_manual(values=c("#193A3D", "#F03F3F"))+
  # scale_color_manual(values=c("#193A3D", "#F03F3F"))+
  scale_fill_manual(values=c("seagreen", "plum4"))+
  scale_color_manual(values=c("seagreen", "plum4"))+
  # scale_fill_manual(values=c(rgb2hex(0.0, 153.0, 204.0),rgb2hex(0.0, 77, 102.0)))+
  # scale_color_manual(values=c(rgb2hex(0.0, 153.0, 204.0),rgb2hex(0.0, 77, 102.0)))+
  theme(axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank())+
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+
  # scale_y_continuous(limits=c(-60, 140))
  scale_y_continuous(limits=yax_limits)



# cowplot::plot_grid(plot1, plot2, plot3, ncol = 3,labels = "AUTO")
plotttitle <- ggdraw() + 
  draw_label("SSVEP mod. | evoked \nacross cons | isoluminat", fontface='bold', size = 10)
plotplots <- ggarrange(plot1, plot2,ncol = 2,common.legend = TRUE,align = "h", widths=c(3,1))

savefig <- multi_panel_figure(columns = 1, rows = 1, panel_label_type = "none", width = 3.5, height = 5, unit = "in")
saveplot <- ggarrange(plotttitle, plotplots, nrow = 2, heights=c(0.2, 1))

savefig %<>%
  fill_panel(saveplot, column = 1, row = 1)
savefig
# save_multi_panel_figure(savefig, "figures/FFT_BeeSwarm_Mod_ALPHA_COL_34subs.eps")
```



## Statistical analysis




### Central Stimuli


**modulation** ~ **COLOR ATTENTION**

- t-test post-cue modulation against zero for attended and unattended color
- t-test difference of post-cue modulation for attended vs unattended color

<br> 

```{r Stat central stimuli, message=FALSE, warning=FALSE, include=TRUE}
dat2plot <- DataIn %>%
  filter(RDK_position2=="center") %>%
  group_by(subjects, time, RDK_isattended, RDK_colorlum)%>%
  summarise(amplitude_evoked=mean(amplitude_evoked), modulation_evoked=mean(modulation_evoked))%>%
  filter(time == '[0.5 1.5] ')

dat2plot %>%
  group_by(RDK_isattended, RDK_colorlum)%>%
  nest()%>%
  mutate(stats = map(data, ~broom::tidy(
    t.test(modulation_evoked ~ 1, data = .)
  ))) %>%
  mutate(
    t_test_bf = map(data, ~{extractBF(ttestBF(x = .$modulation_evoked, data = .,iterations=num.iter,rscale = sqrt(2)/2))})
  )%>%
  mutate(meanval = map(data, ~ mean(.x$modulation_evoked))) %>%
  mutate(std = map(data, ~ sd(.x$modulation_evoked))) %>%
  dplyr::select(-data) %>%
  unnest(cols = c(stats, t_test_bf, meanval, std))%>%
  mutate(BF10 = bf, BF01 = 1/bf)%>%
  dplyr::select(RDK_colorlum, RDK_isattended, meanval, std,  statistic, parameter, p.value, BF10, BF01)%>%
  mutate(p.value = p.adjust(p.value, method="holm")) %>% # none, holm
  # mutate(p.value = p.adjust(p.value, method="none")) %>% # none, holm
  ungroup()%>%
  mutate(CohensD = `statistic`/sqrt(parameter +1))%>%
  mutate(
    p.value = cell_spec(ifelse(round(p.value,4)<.001,"< .001",round(p.value,4)), 
                        color = ifelse(is.nan(p.value),"blue", ifelse(p.value < .05, "green", "red")),
                        bold = ifelse(is.nan(p.value),F, ifelse(p.value < .05, T,F)),
                        align = "center")
  ) %>%
  kable(escape = F, digits = c(3,3,3,3,3,3,3,3,3), 
        caption = c("central SSVEP | modulation | t-tests for modulation agains zero | Holm-corrected")) %>%
  kable_styling("striped", full_width = T, bootstrap_options = c("striped", "hover", "condensed", "responsive",font_size = 8))



dat2plot %>%
  dplyr::select(-amplitude_evoked)%>%
  pivot_wider(names_from = "RDK_isattended", values_from = "modulation_evoked")%>%
  mutate(attendedMINUSunattended = `attended` -`not attended`)%>%
  group_by(time, RDK_colorlum)%>%
  nest()%>%
  mutate(stats = map(data, ~broom::tidy(
    t.test(attendedMINUSunattended ~ 1, data = .)
  ))) %>%
  mutate(
    t_test_bf = map(data, ~{extractBF(ttestBF(x = .$attendedMINUSunattended, data = .,iterations=num.iter,rscale = sqrt(2)/2))})
  )%>%
  mutate(meanval = map(data, ~ mean(.x$attendedMINUSunattended))) %>%
  mutate(std = map(data, ~ sd(.x$attendedMINUSunattended))) %>%
  ungroup()%>%
  dplyr::select(-data, -time) %>%
  unnest(cols = c(stats, t_test_bf, meanval, std))%>%
  mutate(BF10 = bf, BF01 = 1/bf)%>%
  dplyr::select(RDK_colorlum, meanval, std,  statistic, parameter, p.value, BF10, BF01)%>%
  # mutate(p.value = p.adjust(p.value, method="holm")) %>% # none, holm
  # mutate(p.value = p.adjust(p.value, method="none")) %>% # none, holm
  ungroup()%>%
  mutate(CohensD = `statistic`/sqrt(parameter +1))%>%
  mutate(
    p.value = cell_spec(ifelse(round(p.value,4)<.001,"< .001",round(p.value,4)), 
                        color = ifelse(is.nan(p.value),"blue", ifelse(p.value < .05, "green", "red")),
                        bold = ifelse(is.nan(p.value),F, ifelse(p.value < .05, T,F)),
                        align = "center")
  ) %>%
  kable(escape = F, digits = c(3,3,3,3,3,3,3,3,3), caption = c("central SSVEP | modulation | attended - unattended ")) %>%
  kable_styling("striped", full_width = T, bootstrap_options = c("striped", "hover", "condensed", "responsive",font_size = 8))

```


**amp diff** ~ **COLOR ATTENTION**

- t-test post-cue modulation against zero for attended and unattended color
- t-test difference of post-cue modulation for attended vs unattended color

<br> 

```{r Stat2 central stimuli, message=FALSE, warning=FALSE, include=TRUE}
dat2plot <- DataIn %>%
  filter(RDK_position2=="center") %>%
  group_by(subjects, time, RDK_isattended, RDK_colorlum)%>%
  summarise(subtraction_evoked=mean(subtraction_evoked), modulation_evoked=mean(modulation_evoked))%>%
  filter(time == '[0.5 1.5] ')

dat2plot %>%
  group_by(RDK_isattended, RDK_colorlum)%>%
  nest()%>%
  mutate(stats = map(data, ~broom::tidy(
    t.test(subtraction_evoked ~ 1, data = .)
  ))) %>%
  mutate(
    t_test_bf = map(data, ~{extractBF(ttestBF(x = .$subtraction_evoked, data = .,iterations=num.iter,rscale = sqrt(2)/2))})
  )%>%
  mutate(meanval = map(data, ~ mean(.x$subtraction_evoked))) %>%
  mutate(std = map(data, ~ sd(.x$subtraction_evoked))) %>%
  dplyr::select(-data) %>%
  unnest(cols = c(stats, t_test_bf, meanval, std))%>%
  mutate(BF10 = bf, BF01 = 1/bf)%>%
  dplyr::select(RDK_colorlum, RDK_isattended, meanval, std,  statistic, parameter, p.value, BF10, BF01)%>%
  mutate(p.value = p.adjust(p.value, method="holm")) %>% # none, holm
  # mutate(p.value = p.adjust(p.value, method="none")) %>% # none, holm
  ungroup()%>%
  mutate(CohensD = `statistic`/sqrt(parameter +1))%>%
  mutate(
    p.value = cell_spec(ifelse(round(p.value,4)<.001,"< .001",round(p.value,4)), 
                        color = ifelse(is.nan(p.value),"blue", ifelse(p.value < .05, "green", "red")),
                        bold = ifelse(is.nan(p.value),F, ifelse(p.value < .05, T,F)),
                        align = "center")
  ) %>%
  kable(escape = F, digits = c(3,3,3,3,3,3,3,3,3), 
        caption = c("central SSVEP | amp diff | t-tests for modulation agains zero | Holm-corrected")) %>%
  kable_styling("striped", full_width = T, bootstrap_options = c("striped", "hover", "condensed", "responsive",font_size = 8))



dat2plot %>%
  dplyr::select(-modulation_evoked)%>%
  pivot_wider(names_from = "RDK_isattended", values_from = "subtraction_evoked")%>%
  mutate(attendedMINUSunattended = `attended` -`not attended`)%>%
  group_by(time, RDK_colorlum)%>%
  nest()%>%
  mutate(stats = map(data, ~broom::tidy(
    t.test(attendedMINUSunattended ~ 1, data = .)
  ))) %>%
  mutate(
    t_test_bf = map(data, ~{extractBF(ttestBF(x = .$attendedMINUSunattended, data = .,iterations=num.iter,rscale = sqrt(2)/2))})
  )%>%
  mutate(meanval = map(data, ~ mean(.x$attendedMINUSunattended))) %>%
  mutate(std = map(data, ~ sd(.x$attendedMINUSunattended))) %>%
  ungroup()%>%
  dplyr::select(-data, -time) %>%
  unnest(cols = c(stats, t_test_bf, meanval, std))%>%
  mutate(BF10 = bf, BF01 = 1/bf)%>%
  dplyr::select(RDK_colorlum, meanval, std,  statistic, parameter, p.value, BF10, BF01)%>%
  # mutate(p.value = p.adjust(p.value, method="holm")) %>% # none, holm
  # mutate(p.value = p.adjust(p.value, method="none")) %>% # none, holm
  ungroup()%>%
  mutate(CohensD = `statistic`/sqrt(parameter +1))%>%
  mutate(
    p.value = cell_spec(ifelse(round(p.value,4)<.001,"< .001",round(p.value,4)), 
                        color = ifelse(is.nan(p.value),"blue", ifelse(p.value < .05, "green", "red")),
                        bold = ifelse(is.nan(p.value),F, ifelse(p.value < .05, T,F)),
                        align = "center")
  ) %>%
  kable(escape = F, digits = c(3,3,3,3,3,3,3,3,3), caption = c("central SSVEP | amp diff | attended - unattended ")) %>%
  kable_styling("striped", full_width = T, bootstrap_options = c("striped", "hover", "condensed", "responsive",font_size = 8))

```



### Peripheral Stimuli

#### analysis I

**modulation** ~ **COLOR ATTENTION** 

ANOVA_RM: modulation ~ ATTENTION (centrally cued, centrally uncued, irrelevant)

- post-hoc t-test contrasting differences between all levels
- post-hoc t-test difference of post-cue modulation for attended vs unattended color

<br> 

```{r Stat perip stimuli I, message=FALSE, warning=FALSE, include=TRUE}
dat2plot <- DataIn %>%
  filter(RDK_position2=="peri") %>%
  filter(RDK_ispresented=="presented")%>%
  group_by(subjects, time, RDK_isattended, RDK_colorlum)%>%
  summarise(amplitude_evoked=mean(amplitude_evoked), modulation_evoked=mean(modulation_evoked))%>%
  filter(time == '[0.5 1.5] ')

dat2plot %>%
  group_by(time, RDK_colorlum)%>%
  nest()%>%
  mutate(stats= purrr::map(data, ~broom::tidy(
    anova(aov_ez(id="subjects", dv = "modulation_evoked", data = ., within = "RDK_isattended"))
  ))) %>%
  dplyr::select(-data) %>%
  unnest()%>%
  ungroup()%>%
  mutate(
    `p.value` = cell_spec(ifelse(round(`p.value`,4)<.001,"< .001",round(`p.value`,4)), 
                        color = ifelse(is.nan(`p.value`),"blue", ifelse(`p.value` < .05, "green", "red")),
                        bold = ifelse(is.nan(`p.value`),F, ifelse(`p.value` < .05, T,F)),
                        align = "center")
  ) %>%
  dplyr::select(RDK_colorlum, term, `num.Df`, `den.Df`, MSE, `statistic`, ges, `p.value`) %>%
  kable(escape = F, digits = c(3,3,3,3,3,3,3,3,3), caption = c("repeated measures ANOVA for peripheral SSVEP amplitudes")) %>%
  kable_styling("striped", full_width = T, bootstrap_options = c("striped", "hover", "condensed", "responsive",font_size = 8))


dat2plot %>%
  group_by(RDK_colorlum, RDK_isattended)%>%
  nest()%>%
  mutate(stats = map(data, ~broom::tidy(
    t.test(modulation_evoked ~ 1, data = .)
  ))) %>%
  mutate(
    t_test_bf = map(data, ~{extractBF(ttestBF(x = .$modulation_evoked, data = .,iterations=num.iter,rscale = sqrt(2)/2))})
  )%>%
  mutate(meanval = map(data, ~ mean(.x$modulation_evoked))) %>%
  mutate(std = map(data, ~ sd(.x$modulation_evoked))) %>%
  dplyr::select(-data) %>%
  unnest(cols = c(stats, t_test_bf, meanval, std))%>%
  mutate(BF10 = bf, BF01 = 1/bf)%>%
  dplyr::select(RDK_colorlum, RDK_isattended, meanval, std,  statistic, parameter, p.value, BF10, BF01)%>%
  mutate(p.value = p.adjust(p.value, method="holm")) %>% # none, holm
  # mutate(p.value = p.adjust(p.value, method="none")) %>% # none, holm
  ungroup()%>%
  mutate(CohensD = `statistic`/sqrt(parameter +1))%>%
  mutate(
    p.value = cell_spec(ifelse(round(p.value,4)<.001,"< .001",round(p.value,4)), 
                        color = ifelse(is.nan(p.value),"blue", ifelse(p.value < .05, "green", "red")),
                        bold = ifelse(is.nan(p.value),F, ifelse(p.value < .05, T,F)),
                        align = "center")
  ) %>%
  kable(escape = F, digits = c(3,3,3,3,3,3,3,3,3), 
        caption = c("peripheral SSVEP | modulation | t-tests for modulation agains zero | Holm-corrected")) %>%
  kable_styling("striped", full_width = T, bootstrap_options = c("striped", "hover", "condensed", "responsive",font_size = 8))


dat2plot %>%
  dplyr::select(-amplitude_evoked)%>%
  pivot_wider(names_from = "RDK_isattended", values_from = "modulation_evoked")%>%
  mutate(attendedMINUSunattended = `attended` -`not attended`, 
         attendedMINUSirrelevant = `attended` -`irrelevant`,
         irrelevantMINUSunattended = `irrelevant` -`not attended`)%>%
  dplyr::select(-attended, -`not attended`, -irrelevant, -time)%>%
  pivot_longer(cols=`attendedMINUSunattended`:`irrelevantMINUSunattended`, names_to = "contrast", values_to = "amplitude")%>%
  group_by(RDK_colorlum, contrast)%>%
  nest()%>%
  mutate(stats = map(data, ~broom::tidy(
    t.test(amplitude ~ 1, data = .)
  ))) %>%
  mutate(
    t_test_bf = map(data, ~{extractBF(ttestBF(x = .$amplitude, data = .,iterations=num.iter,rscale = sqrt(2)/2))})
  )%>%
  mutate(meanval = map(data, ~ mean(.x$amplitude))) %>%
  mutate(std = map(data, ~ sd(.x$amplitude))) %>%
  ungroup()%>%
  dplyr::select(-data) %>%
  unnest(cols = c(stats, t_test_bf, meanval, std))%>%
  mutate(BF10 = bf, BF01 = 1/bf)%>%
  dplyr::select(RDK_colorlum, contrast, meanval, std,  statistic, parameter, p.value, BF10, BF01)%>%
  # mutate(p.value = p.adjust(p.value, method="holm")) %>% # none, holm
  # mutate(p.value = p.adjust(p.value, method="none")) %>% # none, holm
  ungroup()%>%
  mutate(CohensD = `statistic`/sqrt(parameter +1))%>%
  mutate(
    p.value = cell_spec(ifelse(round(p.value,4)<.001,"< .001",round(p.value,4)), 
                        color = ifelse(is.nan(p.value),"blue", ifelse(p.value < .05, "green", "red")),
                        bold = ifelse(is.nan(p.value),F, ifelse(p.value < .05, T,F)),
                        align = "center")
  ) %>%
  kable(escape = F, digits = c(3,3,3,3,3,3,3,3,3), caption = c("peripheral SSVEP | modulation | contrasts")) %>%
  kable_styling("striped", full_width = T, bootstrap_options = c("striped", "hover", "condensed", "responsive",font_size = 8))

```


**am diff** ~ **COLOR ATTENTION** 

ANOVA_RM: modulation ~ ATTENTION (centrally cued, centrally uncued, irrelevant)

- post-hoc t-test contrasting differences between all levels
- post-hoc t-test difference of post-cue modulation for attended vs unattended color

<br> 

```{r Stat2 perip stimuli I, message=FALSE, warning=FALSE, include=TRUE}
dat2plot <- DataIn %>%
  filter(RDK_position2=="peri") %>%
  filter(RDK_ispresented=="presented")%>%
  group_by(subjects, time, RDK_isattended, RDK_colorlum)%>%
  summarise(subtraction_evoked=mean(subtraction_evoked), modulation_evoked=mean(modulation_evoked))%>%
  filter(time == '[0.5 1.5] ')

dat2plot %>%
  group_by(time, RDK_colorlum)%>%
  nest()%>%
  mutate(stats= purrr::map(data, ~broom::tidy(
    anova(aov_ez(id="subjects", dv = "subtraction_evoked", data = ., within = "RDK_isattended"))
  ))) %>%
  dplyr::select(-data) %>%
  unnest()%>%
  ungroup()%>%
  mutate(
    `p.value` = cell_spec(ifelse(round(`p.value`,4)<.001,"< .001",round(`p.value`,4)), 
                        color = ifelse(is.nan(`p.value`),"blue", ifelse(`p.value` < .05, "green", "red")),
                        bold = ifelse(is.nan(`p.value`),F, ifelse(`p.value` < .05, T,F)),
                        align = "center")
  ) %>%
  dplyr::select(RDK_colorlum, term, `num.Df`, `den.Df`, MSE, `statistic`, ges, `p.value`) %>%
  kable(escape = F, digits = c(3,3,3,3,3,3,3,3,3), caption = c("repeated measures ANOVA for peripheral SSVEP amp diffs")) %>%
  kable_styling("striped", full_width = T, bootstrap_options = c("striped", "hover", "condensed", "responsive",font_size = 8))


dat2plot %>%
  group_by(RDK_colorlum, RDK_isattended)%>%
  nest()%>%
  mutate(stats = map(data, ~broom::tidy(
    t.test(subtraction_evoked ~ 1, data = .)
  ))) %>%
  mutate(
    t_test_bf = map(data, ~{extractBF(ttestBF(x = .$subtraction_evoked, data = .,iterations=num.iter,rscale = sqrt(2)/2))})
  )%>%
  mutate(meanval = map(data, ~ mean(.x$subtraction_evoked))) %>%
  mutate(std = map(data, ~ sd(.x$subtraction_evoked))) %>%
  dplyr::select(-data) %>%
  unnest(cols = c(stats, t_test_bf, meanval, std))%>%
  mutate(BF10 = bf, BF01 = 1/bf)%>%
  dplyr::select(RDK_colorlum, RDK_isattended, meanval, std,  statistic, parameter, p.value, BF10, BF01)%>%
  mutate(p.value = p.adjust(p.value, method="holm")) %>% # none, holm
  # mutate(p.value = p.adjust(p.value, method="none")) %>% # none, holm
  ungroup()%>%
  mutate(CohensD = `statistic`/sqrt(parameter +1))%>%
  mutate(
    p.value = cell_spec(ifelse(round(p.value,4)<.001,"< .001",round(p.value,4)), 
                        color = ifelse(is.nan(p.value),"blue", ifelse(p.value < .05, "green", "red")),
                        bold = ifelse(is.nan(p.value),F, ifelse(p.value < .05, T,F)),
                        align = "center")
  ) %>%
  kable(escape = F, digits = c(3,3,3,3,3,3,3,3,3), 
        caption = c("peripheral SSVEP | amp diff | t-tests for modulation against zero | Holm-corrected")) %>%
  kable_styling("striped", full_width = T, bootstrap_options = c("striped", "hover", "condensed", "responsive",font_size = 8))


dat2plot %>%
  dplyr::select(-modulation_evoked)%>%
  pivot_wider(names_from = "RDK_isattended", values_from = "subtraction_evoked")%>%
  mutate(attendedMINUSunattended = `attended` -`not attended`, 
         attendedMINUSirrelevant = `attended` -`irrelevant`,
         irrelevantMINUSunattended = `irrelevant` -`not attended`)%>%
  dplyr::select(-attended, -`not attended`, -irrelevant, -time)%>%
  pivot_longer(cols=`attendedMINUSunattended`:`irrelevantMINUSunattended`, names_to = "contrast", values_to = "amplitude")%>%
  group_by(RDK_colorlum, contrast)%>%
  nest()%>%
  mutate(stats = map(data, ~broom::tidy(
    t.test(amplitude ~ 1, data = .)
  ))) %>%
  mutate(
    t_test_bf = map(data, ~{extractBF(ttestBF(x = .$amplitude, data = .,iterations=num.iter,rscale = sqrt(2)/2))})
  )%>%
  mutate(meanval = map(data, ~ mean(.x$amplitude))) %>%
  mutate(std = map(data, ~ sd(.x$amplitude))) %>%
  ungroup()%>%
  dplyr::select(-data) %>%
  unnest(cols = c(stats, t_test_bf, meanval, std))%>%
  mutate(BF10 = bf, BF01 = 1/bf)%>%
  dplyr::select(RDK_colorlum, contrast, meanval, std,  statistic, parameter, p.value, BF10, BF01)%>%
  # mutate(p.value = p.adjust(p.value, method="holm")) %>% # none, holm
  # mutate(p.value = p.adjust(p.value, method="none")) %>% # none, holm
  ungroup()%>%
  mutate(CohensD = `statistic`/sqrt(parameter +1))%>%
  mutate(
    p.value = cell_spec(ifelse(round(p.value,4)<.001,"< .001",round(p.value,4)), 
                        color = ifelse(is.nan(p.value),"blue", ifelse(p.value < .05, "green", "red")),
                        bold = ifelse(is.nan(p.value),F, ifelse(p.value < .05, T,F)),
                        align = "center")
  ) %>%
  kable(escape = F, digits = c(3,3,3,3,3,3,3,3,3), caption = c("peripheral SSVEP | amp diff | contrasts")) %>%
  kable_styling("striped", full_width = T, bootstrap_options = c("striped", "hover", "condensed", "responsive",font_size = 8))

```


#### analysis II

**modulation** ~ **condition** 

ANOVA_RM: modulation ~ CONDITION (
                                    attended + irrelevant
                                    attended + not attended
                                    irrelevant + attended
                                    irrelevant + not attended
                                    not attended + attended
                                    not attended + irrelevant
)

- post-hoc t-test contrasting differences between defined levels
- post-hoc t-test difference of post-cue modulation for attended vs unattended color

<br> 

```{r Stat perip stimuli II, message=FALSE, warning=FALSE, include=TRUE}
dat2plot <- DataIn %>%
  filter(RDK_position2=="peri") %>%
  filter(RDK_ispresented=="presented")%>%
  group_by(subjects, time, RDK_isattended2, RDK_colorlum)%>%
  summarise(amplitude_evoked=mean(amplitude_evoked), modulation_evoked=mean(modulation_evoked))%>%
  filter(time == '[0.5 1.5] ')

dat2plot %>%
  group_by(RDK_colorlum, time)%>%
  nest()%>%
  mutate(stats= purrr::map(data, ~broom::tidy(
    anova(aov_ez(id="subjects", dv = "modulation_evoked", data = ., within = "RDK_isattended2"))
  ))) %>%
  dplyr::select(-data) %>%
  unnest()%>%
  ungroup()%>%
  mutate(
    `p.value` = cell_spec(ifelse(round(`p.value`,4)<.001,"< .001",round(`p.value`,4)), 
                        color = ifelse(is.nan(`p.value`),"blue", ifelse(`p.value` < .05, "green", "red")),
                        bold = ifelse(is.nan(`p.value`),F, ifelse(`p.value` < .05, T,F)),
                        align = "center")
  ) %>%
  dplyr::select(RDK_colorlum, term, `num.Df`, `den.Df`, MSE, `statistic`, ges, `p.value`) %>%
  kable(escape = F, digits = c(3,3,3,3,3,3,3,3,3), caption = c("repeated measures ANOVA for peripheral SSVEP amplitudes")) %>%
  kable_styling("striped", full_width = T, bootstrap_options = c("striped", "hover", "condensed", "responsive",font_size = 8))


dat2plot %>%
  group_by(RDK_colorlum, RDK_isattended2)%>%
  nest()%>%
  mutate(stats = map(data, ~broom::tidy(
    t.test(modulation_evoked ~ 1, data = .)
  ))) %>%
  mutate(
    t_test_bf = map(data, ~{extractBF(ttestBF(x = .$modulation_evoked, data = .,iterations=num.iter,rscale = sqrt(2)/2))})
  )%>%
  mutate(meanval = map(data, ~ mean(.x$modulation_evoked))) %>%
  mutate(std = map(data, ~ sd(.x$modulation_evoked))) %>%
  dplyr::select(-data) %>%
  unnest(cols = c(stats, t_test_bf, meanval, std))%>%
  mutate(BF10 = bf, BF01 = 1/bf)%>%
  dplyr::select(RDK_colorlum, RDK_isattended2, meanval, std,  statistic, parameter, p.value, BF10, BF01)%>%
  mutate(p.value = p.adjust(p.value, method="holm")) %>% # none, holm
  # mutate(p.value = p.adjust(p.value, method="none")) %>% # none, holm
  ungroup()%>%
  mutate(CohensD = `statistic`/sqrt(parameter +1))%>%
  mutate(
    p.value = cell_spec(ifelse(round(p.value,4)<.001,"< .001",round(p.value,4)), 
                        color = ifelse(is.nan(p.value),"blue", ifelse(p.value < .05, "green", "red")),
                        bold = ifelse(is.nan(p.value),F, ifelse(p.value < .05, T,F)),
                        align = "center")
  ) %>%
  kable(escape = F, digits = c(3,3,3,3,3,3,3,3,3), 
        caption = c("peripheral SSVEP | modulation | t-tests for modulation agains zero | Holm-corrected")) %>%
  kable_styling("striped", full_width = T, bootstrap_options = c("striped", "hover", "condensed", "responsive",font_size = 8))


dat2plot %>%
  dplyr::select(-amplitude_evoked)%>%
  pivot_wider(names_from = "RDK_isattended2", values_from = "modulation_evoked")%>%
  mutate(`attended-notattMINUSirre` = `attended + not attended` -`attended + irrelevant`, 
         `notattended-attMINUSirre` = `not attended + attended` -`not attended + irrelevant`,
         `irrelevant-atteMINUSnotatt` = `irrelevant + attended` -`irrelevant + not attended`)%>%
  dplyr::select(-c(`attended + irrelevant`:`not attended + irrelevant`))%>%
  pivot_longer(cols=`attended-notattMINUSirre`:`irrelevant-atteMINUSnotatt`, names_to = "contrast", values_to = "amplitude")%>%
  group_by(RDK_colorlum, contrast)%>%
  nest()%>%
  mutate(stats = map(data, ~broom::tidy(
    t.test(amplitude ~ 1, data = .)
  ))) %>%
  mutate(
    t_test_bf = map(data, ~{extractBF(ttestBF(x = .$amplitude, data = .,iterations=num.iter,rscale = sqrt(2)/2))})
  )%>%
  mutate(meanval = map(data, ~ mean(.x$amplitude))) %>%
  mutate(std = map(data, ~ sd(.x$amplitude))) %>%
  ungroup()%>%
  dplyr::select(-data) %>%
  unnest(cols = c(stats, t_test_bf, meanval, std))%>%
  mutate(BF10 = bf, BF01 = 1/bf)%>%
  dplyr::select(RDK_colorlum, contrast, meanval, std,  statistic, parameter, p.value, BF10, BF01)%>%
  # mutate(p.value = p.adjust(p.value, method="holm")) %>% # none, holm
  # mutate(p.value = p.adjust(p.value, method="none")) %>% # none, holm
  ungroup()%>%
  mutate(CohensD = `statistic`/sqrt(parameter +1))%>%
  mutate(
    p.value = cell_spec(ifelse(round(p.value,4)<.001,"< .001",round(p.value,4)), 
                        color = ifelse(is.nan(p.value),"blue", ifelse(p.value < .05, "green", "red")),
                        bold = ifelse(is.nan(p.value),F, ifelse(p.value < .05, T,F)),
                        align = "center")
  ) %>%
  kable(escape = F, digits = c(3,3,3,3,3,3,3,3,3), caption = c("peripheral SSVEP | modulation | contrasts")) %>%
  kable_styling("striped", full_width = T, bootstrap_options = c("striped", "hover", "condensed", "responsive",font_size = 8))

```




**amp diff** ~ **condition** 

ANOVA_RM: modulation ~ CONDITION (
                                    attended + irrelevant
                                    attended + not attended
                                    irrelevant + attended
                                    irrelevant + not attended
                                    not attended + attended
                                    not attended + irrelevant
)

- post-hoc t-test contrasting differences between defined levels
- post-hoc t-test difference of post-cue modulation for attended vs unattended color

<br> 

```{r Stat2 perip stimuli II, message=FALSE, warning=FALSE, include=TRUE}
dat2plot <- DataIn %>%
  filter(RDK_position2=="peri") %>%
  filter(RDK_ispresented=="presented")%>%
  group_by(subjects, time, RDK_isattended2, RDK_colorlum)%>%
  summarise(subtraction_evoked=mean(subtraction_evoked), modulation_evoked=mean(modulation_evoked))%>%
  filter(time == '[0.5 1.5] ')

dat2plot %>%
  group_by(RDK_colorlum, time)%>%
  nest()%>%
  mutate(stats= purrr::map(data, ~broom::tidy(
    anova(aov_ez(id="subjects", dv = "subtraction_evoked", data = ., within = "RDK_isattended2"))
  ))) %>%
  dplyr::select(-data) %>%
  unnest()%>%
  ungroup()%>%
  mutate(
    `p.value` = cell_spec(ifelse(round(`p.value`,4)<.001,"< .001",round(`p.value`,4)), 
                        color = ifelse(is.nan(`p.value`),"blue", ifelse(`p.value` < .05, "green", "red")),
                        bold = ifelse(is.nan(`p.value`),F, ifelse(`p.value` < .05, T,F)),
                        align = "center")
  ) %>%
  dplyr::select(RDK_colorlum, term, `num.Df`, `den.Df`, MSE, `statistic`, ges, `p.value`) %>%
  kable(escape = F, digits = c(3,3,3,3,3,3,3,3,3), caption = c("repeated measures ANOVA for peripheral SSVEP amp diffs")) %>%
  kable_styling("striped", full_width = T, bootstrap_options = c("striped", "hover", "condensed", "responsive",font_size = 8))


dat2plot %>%
  group_by(RDK_colorlum, RDK_isattended2)%>%
  nest()%>%
  mutate(stats = map(data, ~broom::tidy(
    t.test(subtraction_evoked ~ 1, data = .)
  ))) %>%
  mutate(
    t_test_bf = map(data, ~{extractBF(ttestBF(x = .$subtraction_evoked, data = .,iterations=num.iter,rscale = sqrt(2)/2))})
  )%>%
  mutate(meanval = map(data, ~ mean(.x$subtraction_evoked))) %>%
  mutate(std = map(data, ~ sd(.x$subtraction_evoked))) %>%
  dplyr::select(-data) %>%
  unnest(cols = c(stats, t_test_bf, meanval, std))%>%
  mutate(BF10 = bf, BF01 = 1/bf)%>%
  dplyr::select(RDK_colorlum, RDK_isattended2, meanval, std,  statistic, parameter, p.value, BF10, BF01)%>%
  mutate(p.value = p.adjust(p.value, method="holm")) %>% # none, holm
  # mutate(p.value = p.adjust(p.value, method="none")) %>% # none, holm
  ungroup()%>%
  mutate(CohensD = `statistic`/sqrt(parameter +1))%>%
  mutate(
    p.value = cell_spec(ifelse(round(p.value,4)<.001,"< .001",round(p.value,4)), 
                        color = ifelse(is.nan(p.value),"blue", ifelse(p.value < .05, "green", "red")),
                        bold = ifelse(is.nan(p.value),F, ifelse(p.value < .05, T,F)),
                        align = "center")
  ) %>%
  kable(escape = F, digits = c(3,3,3,3,3,3,3,3,3), 
        caption = c("peripheral SSVEP | amp diff | t-tests for modulation against zero | Holm-corrected")) %>%
  kable_styling("striped", full_width = T, bootstrap_options = c("striped", "hover", "condensed", "responsive",font_size = 8))


dat2plot %>%
  dplyr::select(-modulation_evoked)%>%
  pivot_wider(names_from = "RDK_isattended2", values_from = "subtraction_evoked")%>%
  mutate(`attended-notattMINUSirre` = `attended + not attended` -`attended + irrelevant`, 
         `notattended-attMINUSirre` = `not attended + attended` -`not attended + irrelevant`,
         `irrelevant-atteMINUSnotatt` = `irrelevant + attended` -`irrelevant + not attended`)%>%
  dplyr::select(-c(`attended + irrelevant`:`not attended + irrelevant`))%>%
  pivot_longer(cols=`attended-notattMINUSirre`:`irrelevant-atteMINUSnotatt`, names_to = "contrast", values_to = "amplitude")%>%
  group_by(RDK_colorlum, contrast)%>%
  nest()%>%
  mutate(stats = map(data, ~broom::tidy(
    t.test(amplitude ~ 1, data = .)
  ))) %>%
  mutate(
    t_test_bf = map(data, ~{extractBF(ttestBF(x = .$amplitude, data = .,iterations=num.iter,rscale = sqrt(2)/2))})
  )%>%
  mutate(meanval = map(data, ~ mean(.x$amplitude))) %>%
  mutate(std = map(data, ~ sd(.x$amplitude))) %>%
  ungroup()%>%
  dplyr::select(-data) %>%
  unnest(cols = c(stats, t_test_bf, meanval, std))%>%
  mutate(BF10 = bf, BF01 = 1/bf)%>%
  dplyr::select(RDK_colorlum, contrast, meanval, std,  statistic, parameter, p.value, BF10, BF01)%>%
  # mutate(p.value = p.adjust(p.value, method="holm")) %>% # none, holm
  # mutate(p.value = p.adjust(p.value, method="none")) %>% # none, holm
  ungroup()%>%
  mutate(CohensD = `statistic`/sqrt(parameter +1))%>%
  mutate(
    p.value = cell_spec(ifelse(round(p.value,4)<.001,"< .001",round(p.value,4)), 
                        color = ifelse(is.nan(p.value),"blue", ifelse(p.value < .05, "green", "red")),
                        bold = ifelse(is.nan(p.value),F, ifelse(p.value < .05, T,F)),
                        align = "center")
  ) %>%
  kable(escape = F, digits = c(3,3,3,3,3,3,3,3,3), caption = c("peripheral SSVEP | amp diff | contrasts")) %>%
  kable_styling("striped", full_width = T, bootstrap_options = c("striped", "hover", "condensed", "responsive",font_size = 8))

```


#### analysis II [displayed differently]

**modulation** ~ **condition** 

ANOVA_RM: modulation ~ CONDITION (
                                    attended + irrelevant
                                    attended + not attended
                                    irrelevant + attended
                                    irrelevant + not attended
                                    not attended + attended
                                    not attended + irrelevant
)

- post-hoc t-test contrasting differences between defined levels
- post-hoc t-test difference of post-cue modulation for attended vs unattended color

<br> 

```{r Stat perip stimuli IIb, message=FALSE, warning=FALSE, include=TRUE}
dat2plot <- DataIn %>%
  filter(RDK_position2=="peri") %>%
  filter(RDK_ispresented=="presented")%>%
  group_by(subjects, time, RDK_isattended2, RDK_colorlum)%>%
  summarise(amplitude_evoked=mean(amplitude_evoked), modulation_evoked=mean(modulation_evoked))%>%
  filter(time == '[0.5 1.5] ')


dat2plot2 <- DataIn %>%
  mutate(condition2 = case_when(
    (condition == 1 | condition == 2) ~ "peri_att_unatt",
    (condition == 3 | condition == 4) ~ "peri_att_irrel",
    (condition == 5 | condition == 6) ~ "peri_unatt_irrel",
  )) %>%
  filter(RDK_position2=="peri") %>%
  filter(RDK_ispresented=="presented")%>%
  group_by(subjects, time, RDK_isattended, RDK_colorlum, condition2)%>%
  summarise(amplitude_evoked=mean(amplitude_evoked), modulation_evoked=mean(modulation_evoked))%>%
  filter(time=='[0.5 1.5] ')

dat2plot %>%
  group_by(RDK_colorlum, time)%>%
  nest()%>%
  mutate(stats= purrr::map(data, ~broom::tidy(
    anova(aov_ez(id="subjects", dv = "modulation_evoked", data = ., within = "RDK_isattended2"))
  ))) %>%
  dplyr::select(-data) %>%
  unnest()%>%
  ungroup()%>%
  mutate(
    `p.value` = cell_spec(ifelse(round(`p.value`,4)<.001,"< .001",round(`p.value`,4)), 
                        color = ifelse(is.nan(`p.value`),"blue", ifelse(`p.value` < .05, "green", "red")),
                        bold = ifelse(is.nan(`p.value`),F, ifelse(`p.value` < .05, T,F)),
                        align = "center")
  ) %>%
  dplyr::select(RDK_colorlum, term, `num.Df`, `den.Df`, MSE, `statistic`, ges, `p.value`) %>%
  kable(escape = F, digits = c(3,3,3,3,3,3,3,3,3), caption = c("repeated measures ANOVA for peripheral SSVEP amplitudes")) %>%
  kable_styling("striped", full_width = T, bootstrap_options = c("striped", "hover", "condensed", "responsive",font_size = 8))


dat2plot2 %>%
  group_by(RDK_colorlum, condition2, RDK_isattended)%>%
  nest()%>%
  mutate(stats = map(data, ~broom::tidy(
    t.test(modulation_evoked ~ 1, data = .)
  ))) %>%
  mutate(
    t_test_bf = map(data, ~{extractBF(ttestBF(x = .$modulation_evoked, data = .,iterations=num.iter,rscale = sqrt(2)/2))})
  )%>%
  mutate(meanval = map(data, ~ mean(.x$modulation_evoked))) %>%
  mutate(std = map(data, ~ sd(.x$modulation_evoked))) %>%
  dplyr::select(-data) %>%
  unnest(cols = c(stats, t_test_bf, meanval, std))%>%
  mutate(BF10 = bf, BF01 = 1/bf)%>%
  dplyr::select(RDK_colorlum,condition2, RDK_isattended, meanval, std,  statistic, parameter, p.value, BF10, BF01)%>%
  mutate(p.value = p.adjust(p.value, method="holm")) %>% # none, holm
  # mutate(p.value = p.adjust(p.value, method="none")) %>% # none, holm
  ungroup()%>%
  mutate(CohensD = `statistic`/sqrt(parameter +1))%>%
  mutate(
    p.value = cell_spec(ifelse(round(p.value,4)<.001,"< .001",round(p.value,4)), 
                        color = ifelse(is.nan(p.value),"blue", ifelse(p.value < .05, "green", "red")),
                        bold = ifelse(is.nan(p.value),F, ifelse(p.value < .05, T,F)),
                        align = "center")
  ) %>%
  arrange(RDK_colorlum,condition2,RDK_isattended)%>%
  kable(escape = F, digits = c(3,3,3,3,3,3,3,3,3), 
        caption = c("peripheral SSVEP | modulation | t-tests for modulation agains zero | Holm-corrected")) %>%
  kable_styling("striped", full_width = T, bootstrap_options = c("striped", "hover", "condensed", "responsive",font_size = 8))


dat2plot2 %>%
  dplyr::select(-amplitude_evoked)%>%
  pivot_wider(names_from = "RDK_isattended", values_from = "modulation_evoked")%>%
  mutate(`attended-notattended` = `attended` -`not attended`, 
         `attended-irrelevant` = `attended` -`irrelevant`,
         `notattended-irrelevant` = `not attended` -`irrelevant`)%>%
  dplyr::select(-c(`attended`:`not attended`))%>%
  pivot_longer(cols=`attended-notattended`:`notattended-irrelevant`, names_to = "contrast", values_to = "amplitude")%>%
  drop_na(amplitude)%>%
  group_by(RDK_colorlum, condition2)%>%
  nest()%>%
  mutate(stats = map(data, ~broom::tidy(
    t.test(amplitude ~ 1, data = .)
  ))) %>%
  mutate(
    t_test_bf = map(data, ~{extractBF(ttestBF(x = .$amplitude, data = .,iterations=num.iter,rscale = sqrt(2)/2))})
  )%>%
  mutate(meanval = map(data, ~ mean(.x$amplitude))) %>%
  mutate(std = map(data, ~ sd(.x$amplitude))) %>%
  ungroup()%>%
  dplyr::select(-data) %>%
  unnest(cols = c(stats, t_test_bf, meanval, std))%>%
  mutate(BF10 = bf, BF01 = 1/bf)%>%
  dplyr::select(RDK_colorlum, condition2, meanval, std,  statistic, parameter, p.value, BF10, BF01)%>%
  # mutate(p.value = p.adjust(p.value, method="holm")) %>% # none, holm
  # mutate(p.value = p.adjust(p.value, method="none")) %>% # none, holm
  ungroup()%>%
  mutate(CohensD = `statistic`/sqrt(parameter +1))%>%
  mutate(
    p.value = cell_spec(ifelse(round(p.value,4)<.001,"< .001",round(p.value,4)), 
                        color = ifelse(is.nan(p.value),"blue", ifelse(p.value < .05, "green", "red")),
                        bold = ifelse(is.nan(p.value),F, ifelse(p.value < .05, T,F)),
                        align = "center")
  ) %>%
  kable(escape = F, digits = c(3,3,3,3,3,3,3,3,3), caption = c("peripheral SSVEP | modulation | contrasts")) %>%
  kable_styling("striped", full_width = T, bootstrap_options = c("striped", "hover", "condensed", "responsive",font_size = 8))

```


## Some post-hoc add on analyses

### General post cue amplitudes across all conditions


**modulation** ~ **POSITION**

<br> 

```{r Stat post_cue all stimuli, message=FALSE, warning=FALSE, include=TRUE}
dat2plot <- DataIn %>%
  filter(RDK_ispresented=="presented")%>%
  group_by(subjects, time, RDK_position2, RDK_colorlum)%>%
  summarise(amplitude_evoked=mean(amplitude_evoked), modulation_evoked=mean(modulation_evoked))%>%
  filter(time == '[0.5 1.5] ')

dat2plot %>%
  group_by(RDK_position2, RDK_colorlum)%>%
  nest()%>%
  mutate(stats = map(data, ~broom::tidy(
    t.test(modulation_evoked ~ 1, data = .)
  ))) %>%
  mutate(
    t_test_bf = map(data, ~{extractBF(ttestBF(x = .$modulation_evoked, data = .,iterations=num.iter,rscale = sqrt(2)/2))})
  )%>%
  mutate(meanval = map(data, ~ mean(.x$modulation_evoked))) %>%
  mutate(std = map(data, ~ sd(.x$modulation_evoked))) %>%
  dplyr::select(-data) %>%
  unnest(cols = c(stats, t_test_bf, meanval, std))%>%
  mutate(BF10 = bf, BF01 = 1/bf)%>%
  dplyr::select(RDK_colorlum, RDK_position2, meanval, std,  statistic, parameter, p.value, BF10, BF01)%>%
  mutate(p.value = p.adjust(p.value, method="holm")) %>% # none, holm
  # mutate(p.value = p.adjust(p.value, method="none")) %>% # none, holm
  ungroup()%>%
  mutate(CohensD = `statistic`/sqrt(parameter +1))%>%
  mutate(
    p.value = cell_spec(ifelse(round(p.value,4)<.001,"< .001",round(p.value,4)), 
                        color = ifelse(is.nan(p.value),"blue", ifelse(p.value < .05, "green", "red")),
                        bold = ifelse(is.nan(p.value),F, ifelse(p.value < .05, T,F)),
                        align = "center")
  ) %>%
  kable(escape = F, digits = c(3,3,3,3,3,3,3,3,3), 
        caption = c("SSVEP | modulation | t-tests for modulation agains zero | Holm-corrected")) %>%
  kable_styling("striped", full_width = T, bootstrap_options = c("striped", "hover", "condensed", "responsive",font_size = 8))


dat2plot %>%
  dplyr::select(-amplitude_evoked)%>%
  pivot_wider(names_from = "RDK_position2", values_from = "modulation_evoked")%>%
  mutate(centerMINUSperi = `center` -`peri`)%>%
  group_by(time, RDK_colorlum)%>%
  nest()%>%
  mutate(stats = map(data, ~broom::tidy(
    t.test(centerMINUSperi ~ 1, data = .)
  ))) %>%
  mutate(
    t_test_bf = map(data, ~{extractBF(ttestBF(x = .$centerMINUSperi, data = .,iterations=num.iter,rscale = sqrt(2)/2))})
  )%>%
  mutate(meanval = map(data, ~ mean(.x$centerMINUSperi))) %>%
  mutate(std = map(data, ~ sd(.x$centerMINUSperi))) %>%
  ungroup()%>%
  dplyr::select(-data, -time) %>%
  unnest(cols = c(stats, t_test_bf, meanval, std))%>%
  mutate(BF10 = bf, BF01 = 1/bf)%>%
  dplyr::select(RDK_colorlum, meanval, std,  statistic, parameter, p.value, BF10, BF01)%>%
  # mutate(p.value = p.adjust(p.value, method="holm")) %>% # none, holm
  # mutate(p.value = p.adjust(p.value, method="none")) %>% # none, holm
  ungroup()%>%
  mutate(CohensD = `statistic`/sqrt(parameter +1))%>%
  mutate(
    p.value = cell_spec(ifelse(round(p.value,4)<.001,"< .001",round(p.value,4)), 
                        color = ifelse(is.nan(p.value),"blue", ifelse(p.value < .05, "green", "red")),
                        bold = ifelse(is.nan(p.value),F, ifelse(p.value < .05, T,F)),
                        align = "center")
  ) %>%
  kable(escape = F, digits = c(3,3,3,3,3,3,3,3,3), caption = c("SSVEP | modulation | center - peri ")) %>%
  kable_styling("striped", full_width = T, bootstrap_options = c("striped", "hover", "condensed", "responsive",font_size = 8))

```

### analysis  [displayed differently] | pre-cue differences

pre-cue differences?

**amplitude** ~ **condition** 

ANOVA_RM: amplitude ~ CONDITION (
                                    attended + irrelevant
                                    attended + not attended
                                    irrelevant + attended
                                    irrelevant + not attended
                                    not attended + attended
                                    not attended + irrelevant
)

- post-hoc t-test contrasting differences between defined levels
- post-hoc t-test difference of post-cue modulation for attended vs unattended color

<br> 

```{r Stat perip stimuli IIb precue, message=FALSE, warning=FALSE, include=TRUE}
dat2plot <- DataIn %>%
  filter(RDK_position2=="peri") %>%
  filter(RDK_ispresented=="presented")%>%
  group_by(subjects, time, RDK_isattended2, RDK_colorlum)%>%
  summarise(amplitude_evoked=mean(amplitude_evoked), modulation_evoked=mean(modulation_evoked))%>%
  filter(time == '[-1 0] ')

dat2plot2 <- DataIn %>%
  mutate(condition2 = case_when(
    (condition == 1 | condition == 2) ~ "peri_att_unatt",
    (condition == 3 | condition == 4) ~ "peri_att_irrel",
    (condition == 5 | condition == 6) ~ "peri_unatt_irrel",
  )) %>%
  filter(RDK_position2=="peri") %>%
  filter(RDK_ispresented=="presented")%>%
  group_by(subjects, time, RDK_isattended, RDK_colorlum, condition2)%>%
  summarise(amplitude_evoked=mean(amplitude_evoked), modulation_evoked=mean(modulation_evoked))%>%
  filter(time == '[-1 0] ')

dat2plot %>%
  group_by(RDK_colorlum, time)%>%
  nest()%>%
  mutate(stats= purrr::map(data, ~broom::tidy(
    anova(aov_ez(id="subjects", dv = "amplitude_evoked", data = ., within = "RDK_isattended2"))
  ))) %>%
  dplyr::select(-data) %>%
  unnest()%>%
  ungroup()%>%
  mutate(
    `p.value` = cell_spec(ifelse(round(`p.value`,4)<.001,"< .001",round(`p.value`,4)), 
                        color = ifelse(is.nan(`p.value`),"blue", ifelse(`p.value` < .05, "green", "red")),
                        bold = ifelse(is.nan(`p.value`),F, ifelse(`p.value` < .05, T,F)),
                        align = "center")
  ) %>%
  dplyr::select(RDK_colorlum, term, `num.Df`, `den.Df`, MSE, `statistic`, ges, `p.value`) %>%
  kable(escape = F, digits = c(3,3,3,3,3,3,3,3,3), caption = c("repeated measures ANOVA for peripheral SSVEP amplitudes")) %>%
  kable_styling("striped", full_width = T, bootstrap_options = c("striped", "hover", "condensed", "responsive",font_size = 8))


dat2plot2 %>%
  group_by(RDK_colorlum, condition2, RDK_isattended)%>%
  nest()%>%
  mutate(stats = map(data, ~broom::tidy(
    t.test(amplitude_evoked ~ 1, data = .)
  ))) %>%
  mutate(
    t_test_bf = map(data, ~{extractBF(ttestBF(x = .$amplitude_evoked, data = .,iterations=num.iter,rscale = sqrt(2)/2))})
  )%>%
  mutate(meanval = map(data, ~ mean(.x$amplitude_evoked))) %>%
  mutate(std = map(data, ~ sd(.x$amplitude_evoked))) %>%
  dplyr::select(-data) %>%
  unnest(cols = c(stats, t_test_bf, meanval, std))%>%
  mutate(BF10 = bf, BF01 = 1/bf)%>%
  dplyr::select(RDK_colorlum,condition2, RDK_isattended, meanval, std,  statistic, parameter, p.value, BF10, BF01)%>%
  mutate(p.value = p.adjust(p.value, method="holm")) %>% # none, holm
  # mutate(p.value = p.adjust(p.value, method="none")) %>% # none, holm
  ungroup()%>%
  mutate(CohensD = `statistic`/sqrt(parameter +1))%>%
  mutate(
    p.value = cell_spec(ifelse(round(p.value,4)<.001,"< .001",round(p.value,4)), 
                        color = ifelse(is.nan(p.value),"blue", ifelse(p.value < .05, "green", "red")),
                        bold = ifelse(is.nan(p.value),F, ifelse(p.value < .05, T,F)),
                        align = "center")
  ) %>%
  arrange(RDK_colorlum,condition2,RDK_isattended)%>%
  kable(escape = F, digits = c(3,3,3,3,3,3,3,3,3), 
        caption = c("peripheral SSVEP | modulation | t-tests for pre-cue amplitudes against zero | Holm-corrected")) %>%
  kable_styling("striped", full_width = T, bootstrap_options = c("striped", "hover", "condensed", "responsive",font_size = 8))


dat2plot2 %>%
  dplyr::select(-modulation_evoked)%>%
  pivot_wider(names_from = "RDK_isattended", values_from = "amplitude_evoked")%>%
  mutate(`attended-notattended` = `attended` -`not attended`, 
         `attended-irrelevant` = `attended` -`irrelevant`,
         `notattended-irrelevant` = `not attended` -`irrelevant`)%>%
  dplyr::select(-c(`attended`:`not attended`))%>%
  pivot_longer(cols=`attended-notattended`:`notattended-irrelevant`, names_to = "contrast", values_to = "amplitude")%>%
  drop_na(amplitude)%>%
  group_by(RDK_colorlum, condition2)%>%
  nest()%>%
  mutate(stats = map(data, ~broom::tidy(
    t.test(amplitude ~ 1, data = .)
  ))) %>%
  mutate(
    t_test_bf = map(data, ~{extractBF(ttestBF(x = .$amplitude, data = .,iterations=num.iter,rscale = sqrt(2)/2))})
  )%>%
  mutate(meanval = map(data, ~ mean(.x$amplitude))) %>%
  mutate(std = map(data, ~ sd(.x$amplitude))) %>%
  ungroup()%>%
  dplyr::select(-data) %>%
  unnest(cols = c(stats, t_test_bf, meanval, std))%>%
  mutate(BF10 = bf, BF01 = 1/bf)%>%
  dplyr::select(RDK_colorlum, condition2, meanval, std,  statistic, parameter, p.value, BF10, BF01)%>%
  # mutate(p.value = p.adjust(p.value, method="holm")) %>% # none, holm
  # mutate(p.value = p.adjust(p.value, method="none")) %>% # none, holm
  ungroup()%>%
  mutate(CohensD = `statistic`/sqrt(parameter +1))%>%
  mutate(
    p.value = cell_spec(ifelse(round(p.value,4)<.001,"< .001",round(p.value,4)), 
                        color = ifelse(is.nan(p.value),"blue", ifelse(p.value < .05, "green", "red")),
                        bold = ifelse(is.nan(p.value),F, ifelse(p.value < .05, T,F)),
                        align = "center")
  ) %>%
  kable(escape = F, digits = c(3,3,3,3,3,3,3,3,3), caption = c("peripheral SSVEP | pre-cue amplitudes | contrasts")) %>%
  kable_styling("striped", full_width = T, bootstrap_options = c("striped", "hover", "condensed", "responsive",font_size = 8))

```

