---
title: "FFT_SSVEP_analysis"
author: "Christopher"
date: "2 7 2024"
output:
  html_document:
    code_folding: hide
    toc: true
    toc_float: true
    toc_depth: 4
    theme: flatly
---

Modelling of ~~raw~~ [*CSD based*] amplitude values from fft-based data
via linear mixed models
via standard anova models

```{r load_package, message = FALSE, warning = FALSE}
rm(list=ls()) # clear environment
library(lme4)
library(readxl)
library(tidyverse)
library(data.table)
library(tidyverse)
library(afex)
library(broom)
library(apa)
library(kableExtra)
library(lmerTest)
library(pbkrtest)
library(effects)
library(visreg)
library(sjPlot)
library(broom.mixed)
library(pander)
library(mediation)
library(multcomp)
library(multcompView)
library(magrittr)
library(multipanelfigure)
library(ggbeeswarm)
library(lsmeans)
library(BayesFactor)
library(ggpubr)
library(gpairs)
library(DescTools)
library(cowplot)
library(ggpol)
library(logspline)

library(brms)

library(bayestestR)

library(rstatix)
library(ggtern)

source('C:/Dropboxdata/Dropbox/work/R-statistics/general_functions/RainCloudPlots/tutorial_R/R_rainclouds.R')
source('C:/Dropboxdata/Dropbox/work/R-statistics/general_functions/RainCloudPlots/tutorial_R/R_rainclouds.R')

source('C:/Dropboxdata/Dropbox/work/R-statistics/examples/Bayesian_rank-based_hypothesis_testing/rankBasedCommonFunctions.R')
source('C:/Dropboxdata/Dropbox/work/R-statistics/examples/Bayesian_rank-based_hypothesis_testing/rankSumSampler.R') # Wilcoxon rank sum function
source('C:/Dropboxdata/Dropbox/work/R-statistics/examples/Bayesian_rank-based_hypothesis_testing/signRankSampler.R') # Wilcoxon signed-rank function
source('C:/Dropboxdata/Dropbox/work/R-statistics/examples/Bayesian_rank-based_hypothesis_testing/spearmanSampler.R')# Spearman's rho function




# broad cluster
# CSD based normalized to pre-cue baseline in %
#  
DATAPath = "data_in/FFT_Amp_data_largeclust_06-14-2024_13-19.csv"
t_baseline = c(-1000, 0)


# broad cluster | smaller central cluster
# CSD based normalized to pre-cue baseline in %
#  
# DATAPath = "data_in/FFT_Amp_data_largeclust_06-24-2024_15-43.csv"
# t_baseline = c(-1000, 0)


# broad cluster | smaller central cluster
# CSD based normalized to pre-cue baseline in %
# for changed experiment starting with participant 22: isoluminant stimuli and lower flicker frequencies
#  
DATAPath = "data_in/FFT_Amp_data_largeclust_allsubs_08-30-2024_11-21.csv"
t_baseline = c(-1000, 0)


# broad cluster | larger central cluster |
# peri: not correct!
# CSD based normalized to pre-cue baseline in %
# for changed experiment starting with participant 22: isoluminant stimuli and lower flicker frequencies
#  
# DATAPath = "data_in/FFT_Amp_data_pericenter_allsubs_07-02-2024_11-46.csv"
# t_baseline = c(-1000, 0)
# 
# broad cluster | very broad central cluster
# CSD based normalized to pre-cue baseline in %
# for changed experiment starting with participant 22: isoluminant stimuli and lower flicker frequencies
# # 
# DATAPath = "data_in/FFT_Amp_data_largecenterclust_allsubs_09-11-2024_14-45.csv"
# t_baseline = c(-1000, 0)



#!!!!!!! relevant
# broad cluster | larger central cluster as in Tango study | peri both clusters but smaller
# CSD based normalized to pre-cue baseline in %
# for changed experiment starting with participant 22: isoluminant stimuli and lower flicker frequencies
DATAPath = "data_in/FFT_Amp_data_CenterTangoStudyPeriSmall_05-23-2025_11-56.csv"
t_baseline = c(-1000, 0)

# broad cluster | larger central cluster as in Tango study | peri only center
# DATAPath = "data_in/FFT_Amp_data_TangoStudyPeriOnlyCenter_11-25-2024_14-17.csv"
# t_baseline = c(-1000, 0)

# # broad cluster | larger central cluster as in Tango study | peri only lateral | in this study shows gain for attended
# DATAPath = "data_in/FFT_Amp_data_TangoStudyPeriOnlyLateral_11-25-2024_14-17.csv"
# t_baseline = c(-1000, 0)


#!!!!!!!


# replication relevant
# broad cluster | larger central cluster as in Tango study | peri both clusters as in Tango study
# CSD based normalized to pre-cue baseline in %
# for changed experiment starting with participant 22: isoluminant stimuli and lower flicker frequencies
# DATAPath = "data_in/FFT_Amp_data_TangoStudy_05-23-2025_11-53.csv"
# t_baseline = c(-1000, 0)




options(scipen=1, digits=7)
```
<style type="text/css">
.main-container {
max-width: 1800px !important;
margin-left: auto;
margin-right: auto;
}
</style>


## Prepare data  
<br>  

1.  Read in data: 
+ `r DATAPath`
+ with pre-cue  [`r toString(t_baseline)`] ms

<br>  

```{r load_data,results = "hide", fig.show = "hide", warning = FALSE}
sub_sample = c(0)
# sub_sample = as.factor(c(26,30, 31,37, 38)) # no ssvep people discarded
sub_sample = as.factor(c(42)) # low trial number


# read in data
DataIn <- read.csv(DATAPath, sep = ";") %>%
  mutate(subjects = as.factor(subjects))%>%
  filter(!subjects %in% sub_sample)
head(DataIn)
str(DataIn)
```
## Illustrate SSVEP Data

### 1a  Illustrate Data as is | center RDKs


plot differently

<br>  

```{r plot_data_st_center_2, results = "hide",  fig.height=5, fig.width=3.5, warning = FALSE}
#evoked raw#### for center

# set overall limits?
dat2plot <- DataIn %>%
  filter(RDK_position2=="center") %>%
  group_by(subjects, time, RDK_isattended, RDK_colorlum)%>%
  summarise(amplitude_evoked=mean(amplitude_evoked), modulation_evoked=mean(modulation_evoked))%>%
  filter(time=='[0.5 1.5] ')
# set limits
yax_limits <- c( min(dat2plot$modulation_evoked), max(dat2plot$modulation_evoked))
yax_limits <- round(yax_limits + c(-1, 1)*diff(yax_limits)*0.1)
yax_limits <- yax_limits + c(-1, 1)*diff(yax_limits)*0.1


dat2plot <- DataIn %>%
  filter(RDK_position2=="center") %>%
  group_by(subjects, time, RDK_isattended, RDK_colorlum)%>%
  summarise(amplitude_evoked=mean(amplitude_evoked), modulation_evoked=mean(modulation_evoked))%>%
  filter(time=='[0.5 1.5] ', RDK_colorlum == 'offset_to_bckgrd')

# set limits
# yax_limits <- c( min(dat2plot$modulation_evoked), max(dat2plot$modulation_evoked))
# yax_limits <- round(yax_limits + c(-1, 1)*diff(yax_limits)*0.1)
# yax_limits <- yax_limits + c(-1, 1)*diff(yax_limits)*0.2
# # yax_limits <- c(-27, 15)

theme_set(theme_bw())
plot1 <- ggplot(dat2plot, aes(x = RDK_isattended, y = modulation_evoked, fill = RDK_isattended)) +
  geom_hline(yintercept=0, show.legend = FALSE) +
  geom_line(aes(group = interaction(subjects,time)),colour = "grey60",alpha = 1,size =0.5) +
  geom_beeswarm(aes(color = RDK_isattended, x = RDK_isattended,
                    group = RDK_isattended), cex=3, size = 5,alpha=1,fill="grey40",shape=21)+
  # geom_point(aes(color = RDK_isattended, x = interaction(time,RDK_isattended),
  #                   group = RDK_isattended), size = 4,alpha=0.4)+
  stat_summary(fun.y=mean, aes(ymin=..y.., ymax=..y.., color =RDK_isattended), geom='errorbar', width=0.9, size=1.5) +
  scale_x_discrete("RDK_isattended", breaks=waiver(), labels = rep(c(""),1,2)) +
  # theme(legend.position="bottom") +
  ylab(expression(paste("amplitude modulation in %")))+
  scale_fill_manual(values=c("steelblue2", "#F03F3F"))+
  scale_color_manual(values=c("steelblue2", "#F03F3F"))+
  #  scale_fill_manual(values=c("#193A3D", "#F03F3F"))+
  # scale_color_manual(values=c("#193A3D", "#F03F3F"))+
  # scale_fill_manual(values=c(rgb2hex(0.0, 153.0, 204.0),rgb2hex(0.0, 77, 102.0)))+
  # scale_color_manual(values=c(rgb2hex(0.0, 153.0, 204.0),rgb2hex(0.0, 77, 102.0)))+
  theme(legend.position="none")+
  # scale_y_continuous(limits=c(-60, 140))
  scale_y_continuous(limits=yax_limits)


plot2 <- ggplot(dat2plot, aes(y = modulation_evoked, fill = RDK_isattended, x = 1)) +
  geom_flat_violin(aes(fill = RDK_isattended),position = position_nudge(x = .1, y = 0), 
                   adjust = 1.3, trim = FALSE, alpha = 1, colour = NA)+
  geom_hline(yintercept=0, show.legend = FALSE) +
  # scale_fill_manual(values=c("#193A3D", "#F03F3F"))+
  # scale_color_manual(values=c("#193A3D", "#F03F3F"))+
  scale_fill_manual(values=c("steelblue2", "#F03F3F"))+
  scale_color_manual(values=c("steelblue2", "#F03F3F"))+
  # scale_fill_manual(values=c(rgb2hex(0.0, 153.0, 204.0),rgb2hex(0.0, 77, 102.0)))+
  # scale_color_manual(values=c(rgb2hex(0.0, 153.0, 204.0),rgb2hex(0.0, 77, 102.0)))+
  theme(axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank())+
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+
  # scale_y_continuous(limits=c(-60, 140))
  scale_y_continuous(limits=yax_limits)



# cowplot::plot_grid(plot1, plot2, plot3, ncol = 3,labels = "AUTO")
plotttitle <- ggdraw() + 
  draw_label("SSVEP mod. | evoked \ncentral RDKs | luminance offset", fontface='bold', size = 10)
plotplots <- ggarrange(plot1, plot2,ncol = 2,common.legend = TRUE,align = "h", widths=c(3,1))

savefig <- multi_panel_figure(columns = 1, rows = 1, panel_label_type = "none", width = 3.5, height = 5, unit = "in")
saveplot <- ggarrange(plotttitle, plotplots, nrow = 2, heights=c(0.2, 1))

savefig %<>%
  fill_panel(saveplot, column = 1, row = 1)
savefig
# save_multi_panel_figure(savefig, "figures/FFT_BeeSwarm_Mod_ALPHA_COL_34subs.eps")




dat2plot <- DataIn %>%
  filter(RDK_position2=="center") %>%
  group_by(subjects, time, RDK_isattended, RDK_colorlum)%>%
  summarise(amplitude_evoked=mean(amplitude_evoked), modulation_evoked=mean(modulation_evoked))%>%
  filter(time=='[0.5 1.5] ', RDK_colorlum == 'isolum__to_bckgrd')


# set limits
# yax_limits <- c( min(dat2plot$modulation_evoked), max(dat2plot$modulation_evoked))
# yax_limits <- round(yax_limits + c(-1, 1)*diff(yax_limits)*0.1)
# yax_limits <- yax_limits + c(-1, 1)*diff(yax_limits)*0.2
# # yax_limits <- c(-27, 15)

theme_set(theme_bw())
plot1 <- ggplot(dat2plot, aes(x = RDK_isattended, y = modulation_evoked, fill = RDK_isattended)) +
  geom_hline(yintercept=0, show.legend = FALSE) +
  geom_line(aes(group = interaction(subjects,time)),colour = "grey60",alpha = 1,size =0.5) +
  geom_beeswarm(aes(color = RDK_isattended, x = RDK_isattended,
                    group = RDK_isattended), cex=3, size = 5,alpha=1,fill="grey40",shape=21)+
  # geom_point(aes(color = RDK_isattended, x = interaction(time,RDK_isattended),
  #                   group = RDK_isattended), size = 4,alpha=0.4)+
  stat_summary(fun.y=mean, aes(ymin=..y.., ymax=..y.., color =RDK_isattended), geom='errorbar', width=0.9, size=1.5) +
  scale_x_discrete("RDK_isattended", breaks=waiver(), labels = rep(c(""),1,2)) +
  # theme(legend.position="bottom") +
  ylab(expression(paste("amplitude modulation in %")))+
  scale_fill_manual(values=c("steelblue2", "#F03F3F"))+
  scale_color_manual(values=c("steelblue2", "#F03F3F"))+
  #  scale_fill_manual(values=c("#193A3D", "#F03F3F"))+
  # scale_color_manual(values=c("#193A3D", "#F03F3F"))+
  # scale_fill_manual(values=c(rgb2hex(0.0, 153.0, 204.0),rgb2hex(0.0, 77, 102.0)))+
  # scale_color_manual(values=c(rgb2hex(0.0, 153.0, 204.0),rgb2hex(0.0, 77, 102.0)))+
  theme(legend.position="none")+
  # scale_y_continuous(limits=c(-60, 140))
  scale_y_continuous(limits=yax_limits)


plot2 <- ggplot(dat2plot, aes(y = modulation_evoked, fill = RDK_isattended, x = 1)) +
  geom_flat_violin(aes(fill = RDK_isattended),position = position_nudge(x = .1, y = 0), 
                   adjust = 1.3, trim = FALSE, alpha = 1, colour = NA)+
  geom_hline(yintercept=0, show.legend = FALSE) +
  # scale_fill_manual(values=c("#193A3D", "#F03F3F"))+
  # scale_color_manual(values=c("#193A3D", "#F03F3F"))+
  scale_fill_manual(values=c("steelblue2", "#F03F3F"))+
  scale_color_manual(values=c("steelblue2", "#F03F3F"))+
  # scale_fill_manual(values=c(rgb2hex(0.0, 153.0, 204.0),rgb2hex(0.0, 77, 102.0)))+
  # scale_color_manual(values=c(rgb2hex(0.0, 153.0, 204.0),rgb2hex(0.0, 77, 102.0)))+
  theme(axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank())+
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+
  # scale_y_continuous(limits=c(-60, 140))
  scale_y_continuous(limits=yax_limits)



# cowplot::plot_grid(plot1, plot2, plot3, ncol = 3,labels = "AUTO")
plotttitle <- ggdraw() + 
  draw_label("SSVEP mod. | evoked \ncentral RDKs | isoluminant to background", fontface='bold', size = 10)
plotplots <- ggarrange(plot1, plot2,ncol = 2,common.legend = TRUE,align = "h", widths=c(3,1))

savefig <- multi_panel_figure(columns = 1, rows = 1, panel_label_type = "none", width = 3.5, height = 5, unit = "in")
saveplot <- ggarrange(plotttitle, plotplots, nrow = 2, heights=c(0.2, 1))

savefig %<>%
  fill_panel(saveplot, column = 1, row = 1)
savefig
# save_multi_panel_figure(savefig, "figures/FFT_BeeSwarm_Mod_ALPHA_COL_34subs.eps")




```


### 2a  Illustrate Data as is | both subsets | general pre-to-post-cue modulation

plot differently

<br>  

```{r plot_data_center_postcue, results = "hide",  fig.height=5, fig.width=3.5, warning = FALSE}
#evoked raw#### for center

# set overall limits?
dat2plot <- DataIn %>%
  filter(RDK_ispresented=="presented", RDK_position1=="center")%>%
  group_by(subjects, time, RDK_colorlum)%>%
  summarise(amplitude_evoked=mean(amplitude_evoked), modulation_evoked=mean(modulation_evoked))%>%
  filter(time == '[0.5 1.5] ')
# set limits
yax_limits <- c( min(dat2plot$modulation_evoked), max(dat2plot$modulation_evoked))
yax_limits <- round(yax_limits + c(-1, 1)*diff(yax_limits)*0.1)
yax_limits <- yax_limits + c(-1, 1)*diff(yax_limits)*0.1




theme_set(theme_bw())
plot1 <- ggplot(dat2plot, aes(x = RDK_colorlum, y = modulation_evoked, fill = RDK_colorlum)) +
  geom_hline(yintercept=0, show.legend = FALSE) +
  # geom_line(aes(group = interaction(subjects,time)),colour = "grey60",alpha = 1,size =0.5) +
  geom_beeswarm(aes(color = RDK_colorlum, x = RDK_colorlum,
                    group = RDK_colorlum), cex=3, size = 5,alpha=1,fill="grey60",shape=21)+
  # geom_point(aes(color = RDK_isattended, x = interaction(time,RDK_isattended),
  #                   group = RDK_isattended), size = 4,alpha=0.4)+
  stat_summary(fun.y=mean, aes(ymin=..y.., ymax=..y.., color =RDK_colorlum), geom='errorbar', width=0.9, size=1.5) +
  scale_x_discrete("RDK position", breaks=waiver(), labels = rep(c(""),1,2)) +
  # theme(legend.position="bottom") +
  ylab(expression(paste("amplitude modulation in %")))+
  scale_fill_manual(values=c("seagreen", "plum4"))+
  scale_color_manual(values=c("seagreen", "plum4"))+
  #  scale_fill_manual(values=c("#193A3D", "#F03F3F"))+
  # scale_color_manual(values=c("#193A3D", "#F03F3F"))+
  # scale_fill_manual(values=c(rgb2hex(0.0, 153.0, 204.0),rgb2hex(0.0, 77, 102.0)))+
  # scale_color_manual(values=c(rgb2hex(0.0, 153.0, 204.0),rgb2hex(0.0, 77, 102.0)))+
  theme(legend.position="none")+
  # scale_y_continuous(limits=c(-60, 140))
  scale_y_continuous(limits=yax_limits)


plot2 <- ggplot(dat2plot, aes(y = modulation_evoked, fill = RDK_colorlum, x = 1)) +
  geom_flat_violin(aes(fill = RDK_colorlum),position = position_nudge(x = .1, y = 0), 
                   adjust = 1.3, trim = FALSE, alpha = 1, colour = NA)+
  geom_hline(yintercept=0, show.legend = FALSE) +
  # scale_fill_manual(values=c("#193A3D", "#F03F3F"))+
  # scale_color_manual(values=c("#193A3D", "#F03F3F"))+
  scale_fill_manual(values=c("seagreen", "plum4"))+
  scale_color_manual(values=c("seagreen", "plum4"))+
  # scale_fill_manual(values=c(rgb2hex(0.0, 153.0, 204.0),rgb2hex(0.0, 77, 102.0)))+
  # scale_color_manual(values=c(rgb2hex(0.0, 153.0, 204.0),rgb2hex(0.0, 77, 102.0)))+
  theme(axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank())+
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+
  # scale_y_continuous(limits=c(-60, 140))
  scale_y_continuous(limits=yax_limits)



# cowplot::plot_grid(plot1, plot2, plot3, ncol = 3,labels = "AUTO")
plotttitle <- ggdraw() + 
  draw_label("SSVEP mod. | evoked \nacross cons | by stimuli brightness",
             fontface='bold', size = 10)
plotplots <- ggarrange(plot1, plot2,ncol = 2,common.legend = TRUE,align = "h", widths=c(3,1))

savefig <- multi_panel_figure(columns = 1, rows = 1, panel_label_type = "none", width = 3.5, height = 5, unit = "in")
saveplot <- ggarrange(plotttitle, plotplots, nrow = 2, heights=c(0.2, 1))

savefig %<>%
  fill_panel(saveplot, column = 1, row = 1)
savefig
# save_multi_panel_figure(savefig, "figures/FFT_BeeSwarm_Mod_ALPHA_COL_34subs.eps")
```

### 2b  Illustrate Data as is | both subsets | general pre-to-post-cue attentional selectivity

plot differently

<br>  

```{r plot_data_center_postcue_att, results = "hide",  fig.height=3.5, fig.width=2.5, warning = FALSE}
#evoked raw#### for center

# set overall limits?
dat2plot <- DataIn %>%
  filter(RDK_ispresented=="presented", RDK_position1=="center")%>%
  group_by(subjects, time, RDK_colorlum,RDK_isattended)%>%
  summarise( modulation_evoked=mean(modulation_evoked))%>%
  filter(time == '[0.5 1.5] ')%>%
  pivot_wider(names_from = RDK_isattended, values_from = modulation_evoked) %>%
  mutate(modulation_evoked = attended - `not attended`)
# set limits
yax_limits <- c( min(dat2plot$modulation_evoked), max(dat2plot$modulation_evoked))
yax_limits <- round(yax_limits + c(-1, 1)*diff(yax_limits)*0.1)
yax_limits <- yax_limits + c(-1, 1)*diff(yax_limits)*0.1




theme_set(theme_bw())
plot1 <- ggplot(dat2plot, aes(x = RDK_colorlum, y = modulation_evoked, fill = RDK_colorlum)) +
  geom_hline(yintercept=0, show.legend = FALSE) +
  # geom_line(aes(group = interaction(subjects,time)),colour = "grey60",alpha = 1,size =0.5) +
  geom_beeswarm(aes(color = RDK_colorlum, x = RDK_colorlum,
                    group = RDK_colorlum), cex=3, size = 5,alpha=1,fill="grey60",shape=21)+
  # geom_point(aes(color = RDK_isattended, x = interaction(time,RDK_isattended),
  #                   group = RDK_isattended), size = 4,alpha=0.4)+
  stat_summary(fun.y=mean, aes(ymin=..y.., ymax=..y.., color =RDK_colorlum), geom='errorbar', width=0.9, size=1.5) +
  scale_x_discrete("RDK luminance", breaks=waiver(), labels = rep(c(""),1,2)) +
  # theme(legend.position="bottom") +
  ylab(expression(paste("amplitude modulation in %")))+
  scale_fill_manual(values=c("seagreen", "plum4"), labels=c("iso", "offset"))+
  scale_color_manual(values=c("seagreen", "plum4"), labels=c("iso", "offset"))+
  #  scale_fill_manual(values=c("#193A3D", "#F03F3F"))+
  # scale_color_manual(values=c("#193A3D", "#F03F3F"))+
  # scale_fill_manual(values=c(rgb2hex(0.0, 153.0, 204.0),rgb2hex(0.0, 77, 102.0)))+
  # scale_color_manual(values=c(rgb2hex(0.0, 153.0, 204.0),rgb2hex(0.0, 77, 102.0)))+
  theme(legend.position="none")+
  # scale_y_continuous(limits=c(-60, 140))
  scale_y_continuous(limits=yax_limits)


plot2 <- ggplot(dat2plot, aes(y = modulation_evoked, fill = RDK_colorlum, x = 1)) +
  geom_flat_violin(aes(fill = RDK_colorlum),position = position_nudge(x = .1, y = 0), 
                   adjust = 1.3, trim = FALSE, alpha = 1, colour = NA)+
  geom_hline(yintercept=0, show.legend = FALSE) +
  # scale_fill_manual(values=c("#193A3D", "#F03F3F"))+
  # scale_color_manual(values=c("#193A3D", "#F03F3F"))+
  scale_fill_manual(values=c("seagreen", "plum4"), labels=c("iso", "offset"))+
  scale_color_manual(values=c("seagreen", "plum4"), labels=c("iso", "offset"))+
  # scale_fill_manual(values=c(rgb2hex(0.0, 153.0, 204.0),rgb2hex(0.0, 77, 102.0)))+
  # scale_color_manual(values=c(rgb2hex(0.0, 153.0, 204.0),rgb2hex(0.0, 77, 102.0)))+
  theme(axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank())+
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+
  # scale_y_continuous(limits=c(-60, 140))
  scale_y_continuous(limits=yax_limits)



# cowplot::plot_grid(plot1, plot2, plot3, ncol = 3,labels = "AUTO")
plotttitle <- ggdraw() + 
  draw_label("SSVEP mod. | evoked \natt. - unatt. | by stimuli brightness",
             fontface='bold', size = 10)
plotplots <- ggarrange(plot1, plot2,ncol = 2,common.legend = TRUE,align = "h", widths=c(3,1))

savefig <- multi_panel_figure(columns = 1, rows = 1, panel_label_type = "none", width = 2.5, height = 3.5, unit = "in")
saveplot <- ggarrange(plotttitle, plotplots, nrow = 2, heights=c(0.2, 1))

savefig %<>%
  fill_panel(saveplot, column = 1, row = 1)
savefig
# save_multi_panel_figure(savefig, "figures/FFT_BeeSwarm_Mod_ALPHA_COL_34subs.eps")
```

### 2c  Direct comparison of pre-cue amplitudes for 26 Hz signal (present in both studies)


<br>  

```{r plot_data_center_pre_cue26Hz, results = "hide",  fig.height=3.5, fig.width=2.5, warning = FALSE}
#evoked raw#### for center

# set overall limits?
dat2plot <- DataIn %>%
  filter(
    RDK_ispresented=="presented", 
    RDK_position1=="center",
    RDK_freq == 26,
    time == '[-1 0] ')%>%
  group_by(subjects, RDK_colorlum)%>%
  summarise( amplitude_evoked=mean(amplitude_evoked))
# set limits
yax_limits <- c( 0, max(dat2plot$amplitude_evoked))
yax_limits <- round(yax_limits + c(-1, 1)*diff(yax_limits)*0.1)
yax_limits <- yax_limits + c(-1, 1)*diff(yax_limits)*0.1




theme_set(theme_bw())
plot1 <- ggplot(dat2plot, aes(x = RDK_colorlum, y = amplitude_evoked, fill = RDK_colorlum)) +
  geom_hline(yintercept=0, show.legend = FALSE) +
  # geom_line(aes(group = interaction(subjects,time)),colour = "grey60",alpha = 1,size =0.5) +
  geom_beeswarm(aes(color = RDK_colorlum, x = RDK_colorlum,
                    group = RDK_colorlum), cex=3, size = 5,alpha=1,fill="grey60",shape=21)+
  # geom_point(aes(color = RDK_isattended, x = interaction(time,RDK_isattended),
  #                   group = RDK_isattended), size = 4,alpha=0.4)+
  stat_summary(fun.y=mean, aes(ymin=..y.., ymax=..y.., color =RDK_colorlum), geom='errorbar', width=0.9, size=1.5) +
  scale_x_discrete("RDK luminance", breaks=waiver(), labels = rep(c(""),1,2)) +
  # theme(legend.position="bottom") +
  ylab(expression(paste("amplitude in ", mu, "V/mm"^2)))+
  scale_fill_manual(values=c("seagreen", "plum4"), labels=c("iso", "offset"))+
  scale_color_manual(values=c("seagreen", "plum4"), labels=c("iso", "offset"))+
  #  scale_fill_manual(values=c("#193A3D", "#F03F3F"))+
  # scale_color_manual(values=c("#193A3D", "#F03F3F"))+
  # scale_fill_manual(values=c(rgb2hex(0.0, 153.0, 204.0),rgb2hex(0.0, 77, 102.0)))+
  # scale_color_manual(values=c(rgb2hex(0.0, 153.0, 204.0),rgb2hex(0.0, 77, 102.0)))+
  theme(legend.position="none")+
  # scale_y_continuous(limits=c(-60, 140))
  scale_y_continuous(limits=yax_limits)


plot2 <- ggplot(dat2plot, aes(y = amplitude_evoked, fill = RDK_colorlum, x = 1)) +
  geom_flat_violin(aes(fill = RDK_colorlum),position = position_nudge(x = .1, y = 0), 
                   adjust = 1.3, trim = FALSE, alpha = 1, colour = NA)+
  geom_hline(yintercept=0, show.legend = FALSE) +
  # scale_fill_manual(values=c("#193A3D", "#F03F3F"))+
  # scale_color_manual(values=c("#193A3D", "#F03F3F"))+
  scale_fill_manual(values=c("seagreen", "plum4"), labels=c("iso", "offset"))+
  scale_color_manual(values=c("seagreen", "plum4"), labels=c("iso", "offset"))+
  # scale_fill_manual(values=c(rgb2hex(0.0, 153.0, 204.0),rgb2hex(0.0, 77, 102.0)))+
  # scale_color_manual(values=c(rgb2hex(0.0, 153.0, 204.0),rgb2hex(0.0, 77, 102.0)))+
  theme(axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank())+
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+
  # scale_y_continuous(limits=c(-60, 140))
  scale_y_continuous(limits=yax_limits)



# cowplot::plot_grid(plot1, plot2, plot3, ncol = 3,labels = "AUTO")
plotttitle <- ggdraw() + 
  draw_label("SSVEP amplitude. | evoked \npre-cue | by stimuli brightness",
             fontface='bold', size = 10)
plotplots <- ggarrange(plot1, plot2,ncol = 2,common.legend = TRUE,align = "h", widths=c(3,1))

savefig <- multi_panel_figure(columns = 1, rows = 1, panel_label_type = "none", width = 2.5, height = 3.5, unit = "in")
saveplot <- ggarrange(plotttitle, plotplots, nrow = 2, heights=c(0.2, 1))

savefig %<>%
  fill_panel(saveplot, column = 1, row = 1)
savefig
# save_multi_panel_figure(savefig, "figures/FFT_BeeSwarm_Mod_ALPHA_COL_34subs.eps")
```

### 2d  Illustrate Data as is | both subsets | attention effects

<br>  

```{r plot_data_ERP_P300, results = "hide",  fig.height=5, fig.width=4, warning = FALSE}
#evoked raw#### for center

# set overall limits?
dat2plot <- DataIn %>%
  filter(RDK_ispresented=="presented", RDK_position1=="center")%>%
  group_by(subjects, time, RDK_colorlum,RDK_isattended)%>%
  summarise( modulation_evoked=mean(modulation_evoked))%>%
  filter(time == '[0.5 1.5] ')
# set limits
yax_limits <- c( min(dat2plot$modulation_evoked), max(dat2plot$modulation_evoked))
yax_limits <- round(yax_limits + c(-1, 1)*diff(yax_limits)*0.1)
yax_limits <- yax_limits + c(-0, 2)*diff(yax_limits)*0.1



theme_set(theme_bw())
plot1 <- ggplot(dat2plot, aes(x = interaction(RDK_isattended,RDK_colorlum), y = modulation_evoked, fill = RDK_isattended)) +
  geom_hline(yintercept=0, show.legend = FALSE) +
  geom_line(aes(group = interaction(subjects,RDK_colorlum)),colour = "grey60",alpha = 1,size =0.5) +
  geom_beeswarm(aes(color = RDK_isattended, x = interaction(RDK_isattended,RDK_colorlum),
                    group = RDK_isattended), cex=2, size = 3,alpha=1,fill="grey60",shape=21)+
  # geom_point(aes(color = RDK_isattended, x = interaction(time,RDK_isattended),
  #                   group = RDK_isattended), size = 4,alpha=0.4)+
  stat_summary(fun.y=mean, aes(ymin=..y.., ymax=..y.., color =RDK_isattended), geom='errorbar', width=0.9, size=1.5) +
  scale_x_discrete("LUMINANCE", breaks=waiver(), labels = c("iso","iso","offset","offset")) +
  # theme(legend.position="bottom") +
  # ylab(expression("amplitude in " * mu * "V/m²"))+
  ylab(expression("modulation in %"))+
  # scale_fill_manual(values=c("#005b8a", "#943826"))+
  # scale_color_manual(values=c("#005b8a", "#943826"))+
  # scale_fill_manual(values=c("seagreen", "plum4"))+
  # scale_color_manual(values=c("seagreen", "plum4"))+
  scale_fill_manual(values=c("steelblue2", "#F03F3F"))+
  scale_color_manual(values=c("steelblue2", "#F03F3F"))+
  #  scale_fill_manual(values=c("#193A3D", "#F03F3F"))+
  # scale_color_manual(values=c("#193A3D", "#F03F3F"))+
  # scale_fill_manual(values=c(rgb2hex(0.0, 153.0, 204.0),rgb2hex(0.0, 77, 102.0)))+
  # scale_color_manual(values=c(rgb2hex(0.0, 153.0, 204.0),rgb2hex(0.0, 77, 102.0)))+
  theme(legend.position="none")+
  # scale_y_continuous(limits=c(-60, 140))
  scale_y_continuous(limits=yax_limits)


plot2 <- ggplot(dat2plot, aes(y = modulation_evoked, fill = RDK_isattended, x = RDK_colorlum)) +
  geom_flat_violin(aes(fill = RDK_isattended, width = 1.5),
                   position = position_nudge(x = -0.2, y = 0), 
                   adjust = 1, trim = FALSE, alpha = 1, colour = NA)+
  geom_hline(yintercept=0, show.legend = FALSE) +
  # scale_fill_manual(values=c("#193A3D", "#F03F3F"))+
  # scale_color_manual(values=c("#193A3D", "#F03F3F"))+
  scale_fill_manual(values=c("steelblue2", "#F03F3F"))+
  scale_color_manual(values=c("steelblue2", "#F03F3F"))+
  # scale_fill_manual(values=c("#005b8a", "#943826"))+
  # scale_color_manual(values=c("#005b8a", "#943826"))+
  # scale_fill_manual(values=c("seagreen", "plum4"))+
  # scale_color_manual(values=c("seagreen", "plum4"))+
  # scale_fill_manual(values=c(rgb2hex(0.0, 153.0, 204.0),rgb2hex(0.0, 77, 102.0)))+
  # scale_color_manual(values=c(rgb2hex(0.0, 153.0, 204.0),rgb2hex(0.0, 77, 102.0)))+
  theme(axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank())+
  # theme(axis.title.x=element_blank(),
  #       axis.text.x=element_blank(),
  #       axis.ticks.x=element_blank())+
  scale_x_discrete("LUMINANCE", breaks=waiver(), labels = c("iso","offset")) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+
  # scale_y_continuous(limits=c(-60, 140))
  scale_y_continuous(limits=yax_limits)



# cowplot::plot_grid(plot1, plot2, plot3, ncol = 3,labels = "AUTO")
plotttitle <- ggdraw() + 
  draw_label("SSVEP modulations", fontface='bold', size = 10)
plotplots <- ggarrange(plot1, plot2,ncol = 2,common.legend = TRUE,align = "h", widths=c(3,1))

savefig <- multi_panel_figure(columns = 1, rows = 1, panel_label_type = "none", width = 4, height = 5, unit = "in")
saveplot <- ggarrange(plotttitle, plotplots, nrow = 2, heights=c(0.2, 1))

savefig %<>%
  fill_panel(saveplot, column = 1, row = 1)
savefig

# save_multi_panel_figure(savefig, "figures/FFT_AttMod_2studies.eps")





```


## Statistical analysis



### Central Stimuli

#### analysis I

**modulation** ~ **COLOR ATTENTION** x **COLOR LUMINANCE**

- mixed design
- t-test post-cue modulation against zero for attended and unattended color
- t-test difference of post-cue modulation for attended vs unattended color

<br> 

```{r Stat central stimuli analysisI, message=FALSE, warning=FALSE, include=TRUE, fig.height=4, fig.width=4.5}
dat2plot <- DataIn %>%
  filter(RDK_position2=="center") %>%
  group_by(subjects, time, RDK_isattended, RDK_colorlum)%>%
  summarise(amplitude_evoked=mean(amplitude_evoked), modulation_evoked=mean(modulation_evoked))%>%
  filter(time == '[0.5 1.5] ')%>%
  ungroup

aovmodel1 <- dat2plot%>%
  aov_ez(id="subjects", dv = "modulation_evoked", data = ., within = c("RDK_isattended"), between = c("RDK_colorlum"),
         include_aov = afex_options("include_aov"))


# display table anova effects
aovmodel1 %>%
  anova()%>%
  tidy()%>%
  mutate(
    `p.value` = cell_spec(ifelse(round(`p.value`,4)<.001,"< .001",round(`p.value`,4)), 
                        color = ifelse(is.nan(`p.value`),"blue", ifelse(`p.value` < .05, "green", "red")),
                        bold = ifelse(is.nan(`p.value`),F, ifelse(`p.value` < .05, T,F)),
                        align = "center")
  ) %>%
  dplyr::select(term, `num.Df`, `den.Df`, MSE, `statistic`, ges, `p.value`) %>%
  dplyr::rename(F=statistic)%>%
  kbl(escape = F, digits = c(5,5,5,5,5,5,5,5,5), caption = c("repeated measures ANOVA for central post-cue modulations")) %>%
  kable_styling("striped", full_width = T, bootstrap_options = c("striped", "hover", "condensed", "responsive",font_size = 8))


#display interaction
emm_ATTXLum <- as.data.frame(emmeans(aovmodel1, ~ RDK_isattended*RDK_colorlum))

# RDK_isattended plot
ggplot(emm_ATTXLum, aes(x = RDK_colorlum, y = emmean, fill = RDK_isattended)) +
  geom_col(position = position_dodge(), width = 0.6) +
  geom_errorbar(aes(ymin = lower.CL, ymax = upper.CL), 
                position = position_dodge(width = 0.6),
                width = 0.2) +
  labs(title = "Interaction: Attention × Luminance",
       y = "Estimated Marginal Means (95% CI)", x = "Color Luminance") +
  theme_minimal()+
  scale_fill_manual(values=c("steelblue2", "#F03F3F"))+
  scale_color_manual(values=c("steelblue2", "#F03F3F"))


#create emmeans object/grid
post_hocs.emmean <- emmeans(aovmodel1, c("RDK_isattended","RDK_colorlum")) # adjust = holm

# report data for post_hocs.RDK_isattended
post_hocs.emmean %>%
  kbl(escape = F, digits = c(3,3,3,3,3,3,3,3,3), 
      caption = c("estimated marginal means | by ATTENTION X LUMINANCE | dv = central SSVEP modulation")) %>%
  kable_styling("striped", full_width = T, bootstrap_options = c("striped", "hover", "condensed", "responsive",font_size = 8))

post_hocs.emmean %>%
contrast(method = "identity",adjust = "FDR")%>%
summary() %>%
  mutate(
    p.value = cell_spec(ifelse(round(p.value,4)<.001,"< .001",round(p.value,4)), 
                        color = ifelse(is.nan(p.value),"blue", ifelse(p.value < .05, "green", "red")),
                        bold = ifelse(is.nan(p.value),F, ifelse(p.value < .05, T,F)),
                        align = "left")
  ) %>%
  # mutate(CohensD = `t.ratio`/sqrt(df+1))%>%
  mutate(`CohensD` =
           summary(eff_size(contrast(post_hocs.emmean,method = "identity",adjust = "FDR"),
                            sigma = sqrt(mean(sigma(aovmodel1$lm)^2)), # RMS of sigma()
                            edf = df.residual(aovmodel1$lm), method = "identity"))$effect.size,
         `lowCI` =
           summary(eff_size(contrast(post_hocs.emmean,method = "identity",adjust = "FDR"),
                            sigma = sqrt(mean(sigma(aovmodel1$lm)^2)), # RMS of sigma()
                            edf = df.residual(aovmodel1$lm), method = "identity"))$lower.CL,
         `highCI` =
           summary(eff_size(contrast(post_hocs.emmean,method = "identity",adjust = "FDR"),
                            sigma = sqrt(mean(sigma(aovmodel1$lm)^2)), # RMS of sigma()
                            edf = df.residual(aovmodel1$lm), method = "identity"))$upper.CL
  )%>%
  kbl(escape = F, digits = c(3,3,3,3,3,3,3,3,3), 
        caption = c("estimated marginal means | by ATTENTION X LUMINANCE | dv = central SSVEP modulation | corrected: FDR")) %>%
  kable_styling("striped", full_width = T, bootstrap_options = c("striped", "hover", "condensed", "responsive",font_size = 8))

# planned comparison
# test by specifying the levels levels(post_hocs.emmean) as.data.frame(post_hocs.emmean)
list.contrasts <- list(
  "iso att vs unatt"=c(1, -1, 0, 0),
  "offset att vs unatt"=c(0, 0, 1, -1),
  "att iso vs offset"=c(1,0,-1,0),
  "unatt iso vs offset"=c(0, 1, 0, -1)
)



post_hocs.emmean %>%
  contrast(method = list.contrasts,adjust = "FDR") %>%
  summary() %>%
  mutate(
    p.value = cell_spec(ifelse(round(p.value,4)<.001,"< .001",round(p.value,4)), 
                        color = ifelse(is.nan(p.value),"blue", ifelse(p.value < .05, "green", "red")),
                        bold = ifelse(is.nan(p.value),F, ifelse(p.value < .05, T,F)),
                        align = "left")
  ) %>%
  # mutate(CohensD = `t.ratio`/sqrt(df+1))%>%
  mutate(`CohensD` =
           summary(eff_size(contrast(post_hocs.emmean, method = list.contrasts,adjust = "FDR"),
                            sigma = sqrt(mean(sigma(aovmodel1$lm)^2)), # RMS of sigma()
                            edf = df.residual(aovmodel1$lm), method = "identity"))$effect.size,
         `lowCI` =
           summary(eff_size(contrast(post_hocs.emmean, method = list.contrasts,adjust = "FDR"),
                            sigma = sqrt(mean(sigma(aovmodel1$lm)^2)), # RMS of sigma()
                            edf = df.residual(aovmodel1$lm), method = "identity"))$lower.CL,
         `highCI` =
           summary(eff_size(contrast(post_hocs.emmean, method = list.contrasts,adjust = "FDR"),
                            sigma = sqrt(mean(sigma(aovmodel1$lm)^2)), # RMS of sigma()
                            edf = df.residual(aovmodel1$lm), method = "identity"))$upper.CL
  )%>%
  kbl(escape = F, digits = c(3,3,3,3,3,3,3,3,3), 
        caption = c("estimated contrasts | by ATTENTION X LUMINANCE | dv = central SSVEP modulation | corrected: FDR")) %>%
  kable_styling("striped", full_width = T, bootstrap_options = c("striped", "hover", "condensed", "responsive",font_size = 8))
```




#### analysis II

**modulation** ~ **COLOR ATTENTION**

conventional analysis with anova and post-hoc t-tests implemented manually

- t-test post-cue modulation against zero for attended and unattended color
- t-test difference of post-cue modulation for attended vs unattended color

<br> 

```{r Stat central stimuli analysisII, message=FALSE, warning=FALSE, include=TRUE}
dat2plot <- DataIn %>%
  filter(RDK_position2=="center") %>%
  group_by(subjects, time, RDK_isattended, RDK_colorlum)%>%
  summarise(amplitude_evoked=mean(amplitude_evoked), modulation_evoked=mean(modulation_evoked))%>%
  filter(time == '[0.5 1.5] ')


aovmodel1 <- dat2plot%>%
  aov_ez(id="subjects", dv = "modulation_evoked", data = ., within = c("RDK_isattended"), between = c("RDK_colorlum"),
         include_aov = afex_options("include_aov"))


# display table anova effects
aovmodel1 %>%
  anova()%>%
  tidy()%>%
  mutate(
    `p.value` = cell_spec(ifelse(round(`p.value`,4)<.001,"< .001",round(`p.value`,4)), 
                        color = ifelse(is.nan(`p.value`),"blue", ifelse(`p.value` < .05, "green", "red")),
                        bold = ifelse(is.nan(`p.value`),F, ifelse(`p.value` < .05, T,F)),
                        align = "center")
  ) %>%
  dplyr::select(term, `num.Df`, `den.Df`, MSE, `statistic`, ges, `p.value`) %>%
  dplyr::rename(F=statistic)%>%
  kbl(escape = F, digits = c(5,5,5,5,5,5,5,5,5), caption = c("Mixed effects ANOVA model for central post-cue modulations")) %>%
  kable_styling("striped", full_width = T, bootstrap_options = c("striped", "hover", "condensed", "responsive",font_size = 8))


dat2plot %>%
  group_by(RDK_isattended, RDK_colorlum)%>%
  nest()%>%
  mutate(stats = map(data, ~broom::tidy(
    t.test(modulation_evoked ~ 1, data = .)
  ))) %>%
  mutate(
    t_test_bf = map(data, ~{extractBF(ttestBF(x = .$modulation_evoked, data = .,iterations=num.iter,rscale = sqrt(2)/2))})
  )%>%
  mutate(meanval = map(data, ~ mean(.x$modulation_evoked))) %>%
  mutate(std = map(data, ~ sd(.x$modulation_evoked))) %>%
  dplyr::select(-data) %>%
  unnest(cols = c(stats, t_test_bf, meanval, std))%>%
  mutate(BF10 = bf, BF01 = 1/bf)%>%
  dplyr::select(RDK_colorlum, RDK_isattended, meanval, std,  statistic, parameter, p.value, BF10, BF01)%>%
  ungroup()%>%
  # group_by(RDK_colorlum)%>%
  mutate(p.value = p.adjust(p.value, method="fdr")) %>% # none, holm
  # mutate(p.value = p.adjust(p.value, method="none")) %>% # none, holm
  ungroup()%>%
  mutate(CohensD = `statistic`/sqrt(parameter +1))%>%
  mutate(
    p.value = cell_spec(ifelse(round(p.value,4)<.001,"< .001",round(p.value,4)), 
                        color = ifelse(is.nan(p.value),"blue", ifelse(p.value < .05, "green", "red")),
                        bold = ifelse(is.nan(p.value),F, ifelse(p.value < .05, T,F)),
                        align = "center")
  ) %>%
  kbl(escape = F, digits = c(3,3,3,3,3,3,3,3,3), 
        caption = c("central SSVEP | modulation | t-tests for modulation agains zero | FDR-corrected")) %>%
  kable_styling("striped", full_width = T, bootstrap_options = c("striped", "hover", "condensed", "responsive",font_size = 8))



dat2plot %>%
  dplyr::select(-amplitude_evoked)%>%
  pivot_wider(names_from = "RDK_isattended", values_from = "modulation_evoked")%>%
  mutate(attendedMINUSunattended = `attended` -`not attended`)%>%
  group_by(time, RDK_colorlum)%>%
  nest()%>%
  mutate(stats = map(data, ~broom::tidy(
    t.test(attendedMINUSunattended ~ 1, data = .)
  ))) %>%
  mutate(
    t_test_bf = map(data, ~{extractBF(ttestBF(x = .$attendedMINUSunattended, data = .,iterations=num.iter,rscale = sqrt(2)/2))})
  )%>%
  mutate(meanval = map(data, ~ mean(.x$attendedMINUSunattended))) %>%
  mutate(std = map(data, ~ sd(.x$attendedMINUSunattended))) %>%
  ungroup()%>%
  dplyr::select(-data, -time) %>%
  unnest(cols = c(stats, t_test_bf, meanval, std))%>%
  mutate(BF10 = bf, BF01 = 1/bf)%>%
  dplyr::select(RDK_colorlum, meanval, std,  statistic, parameter, p.value, BF10, BF01)%>%
  ungroup()%>%
  mutate(p.value = p.adjust(p.value, method="fdr")) %>% # none, holm
  # mutate(p.value = p.adjust(p.value, method="none")) %>% # none, holm
  ungroup()%>%
  mutate(CohensD = `statistic`/sqrt(parameter +1))%>%
  mutate(
    p.value = cell_spec(ifelse(round(p.value,4)<.001,"< .001",round(p.value,4)), 
                        color = ifelse(is.nan(p.value),"blue", ifelse(p.value < .05, "green", "red")),
                        bold = ifelse(is.nan(p.value),F, ifelse(p.value < .05, T,F)),
                        align = "center")
  ) %>%
  kbl(escape = F, digits = c(3,3,3,3,3,3,3,3,3), caption = c("central SSVEP | modulation | attended - unattended ")) %>%
  kable_styling("striped", full_width = T, bootstrap_options = c("striped", "hover", "condensed", "responsive",font_size = 8))

```

#### analysis IIc

**modulation** ~ **COLOR ATTENTION**

control analysis for 26 Hz signal only
conventional analysis with anova and post-hoc t-tests implemented manually

- t-test post-cue modulation against zero for attended and unattended color
- t-test difference of post-cue modulation for attended vs unattended color

<br> 

```{r Stat central stimuli analysisII control 26Hz, message=FALSE, warning=FALSE, include=TRUE}
dat2plot <- DataIn %>%
  filter(RDK_position2=="center", RDK_freq==26) %>%
  group_by(subjects, time, RDK_isattended, RDK_colorlum)%>%
  summarise(amplitude_evoked=mean(amplitude_evoked), modulation_evoked=mean(modulation_evoked))%>%
  filter(time == '[0.5 1.5] ')


aovmodel1 <- dat2plot%>%
  aov_ez(id="subjects", dv = "modulation_evoked", data = ., within = c("RDK_isattended"), between = c("RDK_colorlum"),
         include_aov = afex_options("include_aov"))


# display table anova effects
aovmodel1 %>%
  anova()%>%
  tidy()%>%
  mutate(
    `p.value` = cell_spec(ifelse(round(`p.value`,4)<.001,"< .001",round(`p.value`,4)), 
                        color = ifelse(is.nan(`p.value`),"blue", ifelse(`p.value` < .05, "green", "red")),
                        bold = ifelse(is.nan(`p.value`),F, ifelse(`p.value` < .05, T,F)),
                        align = "center")
  ) %>%
  dplyr::select(term, `num.Df`, `den.Df`, MSE, `statistic`, ges, `p.value`) %>%
  dplyr::rename(F=statistic)%>%
  kbl(escape = F, digits = c(5,5,5,5,5,5,5,5,5), caption = c("Mixed effects ANOVA model for central post-cue modulations 26 Hz only")) %>%
  kable_styling("striped", full_width = T, bootstrap_options = c("striped", "hover", "condensed", "responsive",font_size = 8))


dat2plot %>%
  group_by(RDK_isattended, RDK_colorlum)%>%
  nest()%>%
  mutate(stats = map(data, ~broom::tidy(
    t.test(modulation_evoked ~ 1, data = .)
  ))) %>%
  mutate(
    t_test_bf = map(data, ~{extractBF(ttestBF(x = .$modulation_evoked, data = .,iterations=num.iter,rscale = sqrt(2)/2))})
  )%>%
  mutate(meanval = map(data, ~ mean(.x$modulation_evoked))) %>%
  mutate(std = map(data, ~ sd(.x$modulation_evoked))) %>%
  dplyr::select(-data) %>%
  unnest(cols = c(stats, t_test_bf, meanval, std))%>%
  mutate(BF10 = bf, BF01 = 1/bf)%>%
  dplyr::select(RDK_colorlum, RDK_isattended, meanval, std,  statistic, parameter, p.value, BF10, BF01)%>%
  ungroup()%>%
  # group_by(RDK_colorlum)%>%
  mutate(p.value = p.adjust(p.value, method="fdr")) %>% # none, holm
  # mutate(p.value = p.adjust(p.value, method="none")) %>% # none, holm
  ungroup()%>%
  mutate(CohensD = `statistic`/sqrt(parameter +1))%>%
  mutate(
    p.value = cell_spec(ifelse(round(p.value,4)<.001,"< .001",round(p.value,4)), 
                        color = ifelse(is.nan(p.value),"blue", ifelse(p.value < .05, "green", "red")),
                        bold = ifelse(is.nan(p.value),F, ifelse(p.value < .05, T,F)),
                        align = "center")
  ) %>%
  kbl(escape = F, digits = c(3,3,3,3,3,3,3,3,3), 
        caption = c("central SSVEP 26 Hz only | modulation | t-tests for modulation agains zero | FDR-corrected")) %>%
  kable_styling("striped", full_width = T, bootstrap_options = c("striped", "hover", "condensed", "responsive",font_size = 8))



dat2plot %>%
  dplyr::select(-amplitude_evoked)%>%
  pivot_wider(names_from = "RDK_isattended", values_from = "modulation_evoked")%>%
  mutate(attendedMINUSunattended = `attended` -`not attended`)%>%
  group_by(time, RDK_colorlum)%>%
  nest()%>%
  mutate(stats = map(data, ~broom::tidy(
    t.test(attendedMINUSunattended ~ 1, data = .)
  ))) %>%
  mutate(
    t_test_bf = map(data, ~{extractBF(ttestBF(x = .$attendedMINUSunattended, data = .,iterations=num.iter,rscale = sqrt(2)/2))})
  )%>%
  mutate(meanval = map(data, ~ mean(.x$attendedMINUSunattended))) %>%
  mutate(std = map(data, ~ sd(.x$attendedMINUSunattended))) %>%
  ungroup()%>%
  dplyr::select(-data, -time) %>%
  unnest(cols = c(stats, t_test_bf, meanval, std))%>%
  mutate(BF10 = bf, BF01 = 1/bf)%>%
  dplyr::select(RDK_colorlum, meanval, std,  statistic, parameter, p.value, BF10, BF01)%>%
  ungroup()%>%
  mutate(p.value = p.adjust(p.value, method="fdr")) %>% # none, holm
  # mutate(p.value = p.adjust(p.value, method="none")) %>% # none, holm
  ungroup()%>%
  mutate(CohensD = `statistic`/sqrt(parameter +1))%>%
  mutate(
    p.value = cell_spec(ifelse(round(p.value,4)<.001,"< .001",round(p.value,4)), 
                        color = ifelse(is.nan(p.value),"blue", ifelse(p.value < .05, "green", "red")),
                        bold = ifelse(is.nan(p.value),F, ifelse(p.value < .05, T,F)),
                        align = "center")
  ) %>%
  kbl(escape = F, digits = c(3,3,3,3,3,3,3,3,3), caption = c("central SSVEP 26 Hz only | modulation | attended - unattended ")) %>%
  kable_styling("striped", full_width = T, bootstrap_options = c("striped", "hover", "condensed", "responsive",font_size = 8))

```

#### analysis III

**PRE-CUE AMP** ~ **COLOR LUMINANCE**

- t-test of pre-cue 26 Hz amplitudes between isoluminat colors and colors with offset

<br> 

```{r Stat central stimuli analysisIII, message=FALSE, warning=FALSE, include=TRUE}
dat2plot <- DataIn %>%
  filter(
    RDK_ispresented=="presented", 
    RDK_position1=="center",
    RDK_freq == 26,
    time == '[-1 0] ')%>%
  group_by(subjects, RDK_colorlum)%>%
  summarise( amplitude_evoked=mean(amplitude_evoked))

dat2plot %>%
  ungroup()%>%
  nest() %>%
  mutate(
    stats = map(data, ~ broom::tidy(t.test(amplitude_evoked ~ RDK_colorlum, data = .))),
    t_test_bf = map(data, ~ extractBF(ttestBF(formula = amplitude_evoked ~ RDK_colorlum, 
                                              data = ., iterations = num.iter, rscale = sqrt(2)/2))),
    meanval = map(data, ~ .x %>%
                    group_by(RDK_colorlum) %>%
                    summarise(
                      mean_AMP_Mean = mean(amplitude_evoked, na.rm = TRUE),
                      std_AMP_Mean = sd(amplitude_evoked, na.rm = TRUE)
                    ) %>%
                    pivot_wider(names_from = RDK_colorlum,
                                values_from = c(mean_AMP_Mean, std_AMP_Mean),
                                names_sep = "_")
    ),
    cohens_d = map(data, ~ rstatix::cohens_d(amplitude_evoked ~ RDK_colorlum, data = ., paired = FALSE))
  ) %>%
  unnest(cols = c(stats, cohens_d, t_test_bf, meanval))%>%
  mutate(BF10 = bf, BF01 = 1/bf, 
         M_AMP_iso = mean_AMP_Mean_isolum__to_bckgrd,
         SD_AMP_iso = std_AMP_Mean_isolum__to_bckgrd,
         M_AMP_off = mean_AMP_Mean_offset_to_bckgrd,
         SD_AMP_off = std_AMP_Mean_offset_to_bckgrd,
         diff=estimate,
         CohensD = effsize, t.value=statistic, df = parameter)%>%
  dplyr::select(M_AMP_iso, SD_AMP_iso, M_AMP_off, SD_AMP_off, diff, t.value, df, p.value, CohensD, BF10, BF01)%>%
  mutate(
    p.value = cell_spec(ifelse(round(p.value,4)<.001,"< .001",round(p.value,4)), 
                        color = ifelse(is.nan(p.value),"blue", ifelse(p.value < .05, "green", "red")),
                        bold = ifelse(is.nan(p.value),F, ifelse(p.value < .05, T,F)),
                        align = "center")
  ) %>%
  kbl(escape = F, digits = c(3,3,3,3,3,3,3,3,3), caption = c("central SSVEP | amplitude | pre-cue ")) %>%
  kable_styling("striped", full_width = T, bootstrap_options = c("striped", "hover", "condensed", "responsive",font_size = 8))

```

#### analysis IV

**modulation** ~ **COLOR ATTENTION**

Bayesian analysis via brms to allow inclusion of Bayes Factor estimation for mixed models

```{r Stat central stimuli analysisIV, message=FALSE, warning=FALSE, include=TRUE}
dat2plot <- DataIn %>%
  filter(RDK_position2=="center") %>%
  group_by(subjects, time, RDK_isattended, RDK_colorlum)%>%
  summarise(amplitude_evoked=mean(amplitude_evoked), modulation_evoked=mean(modulation_evoked))%>%
  filter(time == '[0.5 1.5] ')



# Fit the model
# (1 | subjects) accounts for the random intercept per subject
bayesian_model <- brm(
  formula = modulation_evoked ~ RDK_isattended * RDK_colorlum + (1 | subjects), 
  data = dat2plot,
  family = gaussian(),
  prior = set_prior("normal(0, 20)", class = "b"), # Optional: set your priors
  # prior = set_prior("cauchy(0, 0.707)", class = "b"), # medium prior
  chains = 4, iter = 2000, core = 4,
  file = "fit_full_slog.rds",
  save_pars = save_pars(all = TRUE),
  file_refit = "on_change",
  # file_refit = "always",
  # file_refit = "never",
)

# (2 | subjects) fit the prior model only
bayesian_prior_model <- brm(
  formula = modulation_evoked ~ RDK_isattended * RDK_colorlum + (1 | subjects), 
  data = dat2plot,
  family = gaussian(),
  prior = set_prior("normal(0, 20)", class = "b"), # Optional: set your priors
  # prior = set_prior("cauchy(0, 0.707)", class = "b"), # medium prior
  chains = 4, iter = 2000, core = 4,
  file = "fit_full_prior_slog.rds",
  save_pars = save_pars(all = TRUE),
  file_refit = "on_change",
  # file_refit = "always",
  # file_refit = "never",
  sample_prior = "only" # This ignores your actual DV values
)

# (3 | subjects) fit the null model only
bayesian_null_model <- brm(
  formula = modulation_evoked ~ 1 + (1 | subjects), 
  data = dat2plot,
  family = gaussian(),
  prior = set_prior("normal(0, 20)", class = "Intercept"), # Optional: set your priors
  # prior = set_prior("cauchy(0, 0.707)", class = "b"), # medium prior
  chains = 4, iter = 2000, core = 4,
  file = "fit_null_slog.rds",
  save_pars = save_pars(all = TRUE),
  file_refit = "on_change",
  # file_refit = "always",
  # file_refit = "never",
)


# report results for some designed contrasts
# create emmmgrid
bayesian_emm <- emmeans(bayesian_model, ~ RDK_isattended * RDK_colorlum)

# defined contrasts
list.contrasts <- list(
  "iso att vs unatt"=c(1, -1, 0, 0),
  "offset att vs unatt"=c(0, 0, 1, -1),
  "att iso vs offset"=c(1,0,-1,0),
  "unatt iso vs offset"=c(0, 1, 0, -1)
)

# compute contrasts
bayesian_contrasts<-bayesian_emm %>%
  contrast(method = list.contrasts)

bayesian_contrasts %>%
  summary() %>%
    kbl(escape = F, digits = c(3,3,3,3,3,3,3,3,3), 
        caption = c("estimated contrasts | by ATTENTION X LUMINANCE | dv = central SSVEP modulation | BRMs framework")) %>%
  kable_styling("striped", full_width = T, bootstrap_options = c("striped", "hover", "condensed", "responsive",font_size = 8))


# no calculate Bayes factors for these contrasts
# Force the calculation to look at the samples
prior_model <- unupdate(bayesian_model)
prior_emm <- emmeans(prior_model, ~ RDK_isattended * RDK_colorlum)
prior_emm_contrasts <- prior_emm %>%
  contrast(method = list.contrasts)

bayesian_contrasts_BF <- bayesfactor_parameters(bayesian_contrasts, prior = prior_emm_contrasts)

bayesian_contrasts_BF%>%
  as.data.frame() %>%
  mutate(BF10 = exp(log_BF), BF01 = 1/exp(log_BF)) %>%
  # Optional: Round to 2 decimal places unless it's very small
  mutate(BF10 = ifelse(BF10 > 1000, formatC(BF10, format = "e", digits = 3), round(BF10, 3))) %>%
  mutate(BF01 = ifelse(BF01 > 1000, formatC(BF01, format = "e", digits = 3), round(BF01, 3))) %>%
  dplyr::select(contrast, BF10, BF01, -log_BF)%>%
    kbl(escape = F, digits = c(3,3,3,3,3,3,3,3,3), 
        caption = c("estimated contrasts | by ATTENTION X LUMINANCE | dv = central SSVEP modulation | BRMs framework")) %>%
  kable_styling("striped", full_width = T, bootstrap_options = c("striped", "hover", "condensed", "responsive",font_size = 8))




```

#### analysis V

**CENTRAL PRE-CUE AMP** ~ **PRESENCE IN PERIPHERY**

Do we see differences in pre-cue SSVEP amplitudes depending on whether the stimulus of the same color was present in the periphery?

```{r Stat central stimuli analysisV, message=FALSE, warning=FALSE, include=TRUE,  fig.height=3.5, fig.width=4.5,}
dat2plot <- DataIn %>%
  filter(time == '[-1 0] ') %>%
  group_by(subjects, condition) %>%
  mutate(
    color_in_periphery = case_when(
      RDK_id == "RDK1" &
        any(RDK_id == "RDK3" & RDK_ispresented == "presented") ~ "color_present",

      RDK_id == "RDK1" ~ "color_absent",

      RDK_id == "RDK2" &
        any(RDK_id == "RDK4" & RDK_ispresented == "presented") ~ "color_present",

      RDK_id == "RDK2" ~ "color_absent",

      TRUE ~ NA_character_
    )
  ) %>%
  ungroup() %>%
  # dplyr::select(-presented_RDK3, -presented_RDK4)%>%
  filter(RDK_position1=="center")%>%
  group_by(subjects,RDK_colorlum, color_in_periphery)%>%
  summarise(amplitude_evoked=mean(amplitude_evoked))




# plot it
# set overall limits?
# set limits
yax_limits <- c( min(dat2plot$amplitude_evoked), max(dat2plot$amplitude_evoked))
yax_limits <- round(yax_limits + c(-1, 1)*diff(yax_limits)*0.1)
yax_limits <- yax_limits + c(-1, 1)*diff(yax_limits)*0.1




theme_set(theme_bw())
plot1 <- dat2plot %>%
  filter(RDK_colorlum=="offset_to_bckgrd")%>%
  ggplot(., aes(x = color_in_periphery, y = amplitude_evoked, fill = color_in_periphery)) +
  geom_hline(yintercept=0, show.legend = FALSE) +
  geom_line(aes(group = interaction(subjects)),colour = "grey60",alpha = 1,size =0.5) +
  geom_beeswarm(aes(color = color_in_periphery, x = color_in_periphery,
                    group = color_in_periphery), cex=3, size = 4,alpha=1,fill="grey60",shape=21)+
  # geom_point(aes(color = RDK_isattended, x = interaction(time,RDK_isattended),
  #                   group = RDK_isattended), size = 4,alpha=0.4)+
  stat_summary(fun.y=mean, aes(ymin=..y.., ymax=..y.., color =color_in_periphery), geom='errorbar', width=0.9, size=1.5) +
  scale_x_discrete("RDK luminance", breaks=waiver(), labels = rep(c(""),1,2)) +
  # theme(legend.position="bottom") +
  ylab(expression(paste("amplitude modulation in %")))+
  scale_fill_manual(values=c("seagreen", "plum4"))+
  scale_color_manual(values=c("seagreen", "plum4"))+
  #  scale_fill_manual(values=c("#193A3D", "#F03F3F"))+
  # scale_color_manual(values=c("#193A3D", "#F03F3F"))+
  # scale_fill_manual(values=c(rgb2hex(0.0, 153.0, 204.0),rgb2hex(0.0, 77, 102.0)))+
  # scale_color_manual(values=c(rgb2hex(0.0, 153.0, 204.0),rgb2hex(0.0, 77, 102.0)))+
  theme(legend.position="none")+
  # scale_y_continuous(limits=c(-60, 140))
  scale_y_continuous(limits=yax_limits)


plot2 <- dat2plot %>%
  filter(RDK_colorlum=="offset_to_bckgrd")%>%
  ggplot(., aes(y = amplitude_evoked, fill = color_in_periphery, x = 1)) +
  geom_flat_violin(aes(fill = color_in_periphery),position = position_nudge(x = .1, y = 0), 
                   adjust = 1.3, trim = FALSE, alpha = 1, colour = NA)+
  geom_hline(yintercept=0, show.legend = FALSE) +
  # scale_fill_manual(values=c("#193A3D", "#F03F3F"))+
  # scale_color_manual(values=c("#193A3D", "#F03F3F"))+
  scale_fill_manual(values=c("seagreen", "plum4"))+
  scale_color_manual(values=c("seagreen", "plum4"))+
  # scale_fill_manual(values=c(rgb2hex(0.0, 153.0, 204.0),rgb2hex(0.0, 77, 102.0)))+
  # scale_color_manual(values=c(rgb2hex(0.0, 153.0, 204.0),rgb2hex(0.0, 77, 102.0)))+
  theme(axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank())+
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+
  # scale_y_continuous(limits=c(-60, 140))
  scale_y_continuous(limits=yax_limits)


plot3 <- dat2plot %>%
  filter(RDK_colorlum!="offset_to_bckgrd")%>%
  ggplot(., aes(x = color_in_periphery, y = amplitude_evoked, fill = color_in_periphery)) +
  geom_hline(yintercept=0, show.legend = FALSE) +
  geom_line(aes(group = interaction(subjects)),colour = "grey60",alpha = 1,size =0.5) +
  geom_beeswarm(aes(color = color_in_periphery, x = color_in_periphery,
                    group = color_in_periphery), cex=3, size = 4,alpha=1,fill="grey60",shape=21)+
  # geom_point(aes(color = RDK_isattended, x = interaction(time,RDK_isattended),
  #                   group = RDK_isattended), size = 4,alpha=0.4)+
  stat_summary(fun.y=mean, aes(ymin=..y.., ymax=..y.., color =color_in_periphery), geom='errorbar', width=0.9, size=1.5) +
  scale_x_discrete("RDK luminance", breaks=waiver(), labels = rep(c(""),1,2)) +
  # theme(legend.position="bottom") +
  ylab(expression(paste("amplitude modulation in %")))+
  scale_fill_manual(values=c("seagreen", "plum4"))+
  scale_color_manual(values=c("seagreen", "plum4"))+
  #  scale_fill_manual(values=c("#193A3D", "#F03F3F"))+
  # scale_color_manual(values=c("#193A3D", "#F03F3F"))+
  # scale_fill_manual(values=c(rgb2hex(0.0, 153.0, 204.0),rgb2hex(0.0, 77, 102.0)))+
  # scale_color_manual(values=c(rgb2hex(0.0, 153.0, 204.0),rgb2hex(0.0, 77, 102.0)))+
  theme(legend.position="none")+
  # scale_y_continuous(limits=c(-60, 140))
  scale_y_continuous(limits=yax_limits)


plot4 <- dat2plot %>%
  filter(RDK_colorlum!="offset_to_bckgrd")%>%
  ggplot(., aes(y = amplitude_evoked, fill = color_in_periphery, x = 1)) +
  geom_flat_violin(aes(fill = color_in_periphery),position = position_nudge(x = .1, y = 0), 
                   adjust = 1.3, trim = FALSE, alpha = 1, colour = NA)+
  geom_hline(yintercept=0, show.legend = FALSE) +
  # scale_fill_manual(values=c("#193A3D", "#F03F3F"))+
  # scale_color_manual(values=c("#193A3D", "#F03F3F"))+
  scale_fill_manual(values=c("seagreen", "plum4"))+
  scale_color_manual(values=c("seagreen", "plum4"))+
  # scale_fill_manual(values=c(rgb2hex(0.0, 153.0, 204.0),rgb2hex(0.0, 77, 102.0)))+
  # scale_color_manual(values=c(rgb2hex(0.0, 153.0, 204.0),rgb2hex(0.0, 77, 102.0)))+
  theme(axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank())+
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+
  # scale_y_continuous(limits=c(-60, 140))
  scale_y_continuous(limits=yax_limits)



# cowplot::plot_grid(plot1, plot2, plot3, ncol = 3,labels = "AUTO")
plotttitle <- ggdraw() + 
  draw_label("SSVEP amplitude. | evoked \nleft: offset; right: isoluminant",
             fontface='bold', size = 10)
plotplots <- ggarrange(plot1, plot2,plot3, plot4,ncol = 4,common.legend = TRUE,align = "h", widths=c(3,1,3,1))

savefig <- multi_panel_figure(columns = 1, rows = 1, panel_label_type = "none", width = 4.5, height = 3.5, unit = "in")
saveplot <- ggarrange(plotttitle, plotplots, nrow = 2, heights=c(0.2, 1))

savefig %<>%
  fill_panel(saveplot, column = 1, row = 1)
savefig
# save_multi_panel_figure(savefig, "figures/FFT_BeeSwarm_Mod_ALPHA_COL_34subs.eps")


# statistical test
dat2plot %>%
  ungroup()%>%
  group_by(RDK_colorlum)%>%
  nest() %>%
    mutate(
    stats = map(data, ~ rstatix::t_test(amplitude_evoked ~ color_in_periphery, data = ., paired = TRUE, detailed = TRUE)),
    t_test_bf = map(data, ~ extractBF(ttestBF(formula = amplitude_evoked ~ color_in_periphery, 
                                              data = ., iterations = num.iter, rscale = sqrt(2)/2))),
    meanval = map(data, ~ .x %>%
                    group_by(color_in_periphery) %>%
                    summarise(
                      mean_AMP_Mean = mean(amplitude_evoked, na.rm = TRUE),
                      std_AMP_Mean = sd(amplitude_evoked, na.rm = TRUE)
                    ) %>%
                    pivot_wider(names_from = color_in_periphery,
                                values_from = c(mean_AMP_Mean, std_AMP_Mean),
                                names_sep = "_")
    ),
    cohens_d = map(data, ~ rstatix::cohens_d(amplitude_evoked ~ color_in_periphery, data = ., paired = FALSE))
  ) %>%
  unnest(cols = c(stats, t_test_bf, meanval))%>%
  mutate(CohensD = `statistic`/sqrt(df +1))%>%
  mutate(BF10 = bf, BF01 = 1/bf, 
         M_AMP_abs = mean_AMP_Mean_color_absent,
         SD_AMP_abs = std_AMP_Mean_color_absent,
         M_AMP_pres = mean_AMP_Mean_color_present,
         SD_AMP_pres = std_AMP_Mean_color_present,
         diff=estimate,
         t.value=statistic,p.value=p)%>%
  dplyr::select(M_AMP_abs, SD_AMP_abs, M_AMP_pres, SD_AMP_pres, diff, t.value, df, p.value, CohensD, BF10, BF01)%>%
  mutate(
    p.value = cell_spec(ifelse(round(p.value,4)<.001,"< .001",round(p.value,4)), 
                        color = ifelse(is.nan(p.value),"blue", ifelse(p.value < .05, "green", "red")),
                        bold = ifelse(is.nan(p.value),F, ifelse(p.value < .05, T,F)),
                        align = "center")
  ) %>%
  kbl(escape = F, digits = c(3,3,3,3,3,3,3,3,3), caption = c("central SSVEP | amplitude | pre-cue ")) %>%
  kable_styling("striped", full_width = T, bootstrap_options = c("striped", "hover", "condensed", "responsive",font_size = 8))
```

#### analysis VI

**CENTRAL POST-CUE MOD** ~ **PRESENCE IN PERIPHERY**

Do we see differences in post-cue SSVEP modulations depending on whether the stimulus of the same color was present in the periphery?

```{r Stat central stimuli analysisVI, message=FALSE, warning=FALSE, include=TRUE,  fig.height=3.5, fig.width=4.5,}
dat2plot <- DataIn %>%
  filter(time == '[0.5 1.5] ') %>%
  group_by(subjects, condition) %>%
  mutate(
    color_in_periphery = case_when(
      RDK_id == "RDK1" &
        any(RDK_id == "RDK3" & RDK_ispresented == "presented") ~ "color_present",

      RDK_id == "RDK1" ~ "color_absent",

      RDK_id == "RDK2" &
        any(RDK_id == "RDK4" & RDK_ispresented == "presented") ~ "color_present",

      RDK_id == "RDK2" ~ "color_absent",

      TRUE ~ NA_character_
    )
  ) %>%
  ungroup() %>%
  # dplyr::select(-presented_RDK3, -presented_RDK4)%>%
  filter(RDK_position1=="center" & RDK_isattended =="attended")%>%
  group_by(subjects,RDK_colorlum, color_in_periphery)%>%
  summarise(modulation_evoked=mean(modulation_evoked))




# plot it
# set overall limits?
# set limits
yax_limits <- c( min(dat2plot$modulation_evoked), max(dat2plot$modulation_evoked))
yax_limits <- round(yax_limits + c(-1, 1)*diff(yax_limits)*0.1)
yax_limits <- yax_limits + c(-1, 1)*diff(yax_limits)*0.1




theme_set(theme_bw())
plot1 <- dat2plot %>%
  filter(RDK_colorlum=="offset_to_bckgrd")%>%
  ggplot(., aes(x = color_in_periphery, y = modulation_evoked, fill = color_in_periphery)) +
  geom_hline(yintercept=0, show.legend = FALSE) +
  geom_line(aes(group = interaction(subjects)),colour = "grey60",alpha = 1,size =0.5) +
  geom_beeswarm(aes(color = color_in_periphery, x = color_in_periphery,
                    group = color_in_periphery), cex=3, size = 4,alpha=1,fill="grey60",shape=21)+
  # geom_point(aes(color = RDK_isattended, x = interaction(time,RDK_isattended),
  #                   group = RDK_isattended), size = 4,alpha=0.4)+
  stat_summary(fun.y=mean, aes(ymin=..y.., ymax=..y.., color =color_in_periphery), geom='errorbar', width=0.9, size=1.5) +
  scale_x_discrete("RDK luminance", breaks=waiver(), labels = rep(c(""),1,2)) +
  # theme(legend.position="bottom") +
  ylab(expression(paste("amplitude modulation in %")))+
  scale_fill_manual(values=c("seagreen", "plum4"))+
  scale_color_manual(values=c("seagreen", "plum4"))+
  #  scale_fill_manual(values=c("#193A3D", "#F03F3F"))+
  # scale_color_manual(values=c("#193A3D", "#F03F3F"))+
  # scale_fill_manual(values=c(rgb2hex(0.0, 153.0, 204.0),rgb2hex(0.0, 77, 102.0)))+
  # scale_color_manual(values=c(rgb2hex(0.0, 153.0, 204.0),rgb2hex(0.0, 77, 102.0)))+
  theme(legend.position="none")+
  # scale_y_continuous(limits=c(-60, 140))
  scale_y_continuous(limits=yax_limits)


plot2 <- dat2plot %>%
  filter(RDK_colorlum=="offset_to_bckgrd")%>%
  ggplot(., aes(y = modulation_evoked, fill = color_in_periphery, x = 1)) +
  geom_flat_violin(aes(fill = color_in_periphery),position = position_nudge(x = .1, y = 0), 
                   adjust = 1.3, trim = FALSE, alpha = 1, colour = NA)+
  geom_hline(yintercept=0, show.legend = FALSE) +
  # scale_fill_manual(values=c("#193A3D", "#F03F3F"))+
  # scale_color_manual(values=c("#193A3D", "#F03F3F"))+
  scale_fill_manual(values=c("seagreen", "plum4"))+
  scale_color_manual(values=c("seagreen", "plum4"))+
  # scale_fill_manual(values=c(rgb2hex(0.0, 153.0, 204.0),rgb2hex(0.0, 77, 102.0)))+
  # scale_color_manual(values=c(rgb2hex(0.0, 153.0, 204.0),rgb2hex(0.0, 77, 102.0)))+
  theme(axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank())+
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+
  # scale_y_continuous(limits=c(-60, 140))
  scale_y_continuous(limits=yax_limits)


plot3 <- dat2plot %>%
  filter(RDK_colorlum!="offset_to_bckgrd")%>%
  ggplot(., aes(x = color_in_periphery, y = modulation_evoked, fill = color_in_periphery)) +
  geom_hline(yintercept=0, show.legend = FALSE) +
  geom_line(aes(group = interaction(subjects)),colour = "grey60",alpha = 1,size =0.5) +
  geom_beeswarm(aes(color = color_in_periphery, x = color_in_periphery,
                    group = color_in_periphery), cex=3, size = 4,alpha=1,fill="grey60",shape=21)+
  # geom_point(aes(color = RDK_isattended, x = interaction(time,RDK_isattended),
  #                   group = RDK_isattended), size = 4,alpha=0.4)+
  stat_summary(fun.y=mean, aes(ymin=..y.., ymax=..y.., color =color_in_periphery), geom='errorbar', width=0.9, size=1.5) +
  scale_x_discrete("RDK luminance", breaks=waiver(), labels = rep(c(""),1,2)) +
  # theme(legend.position="bottom") +
  ylab(expression(paste("amplitude modulation in %")))+
  scale_fill_manual(values=c("seagreen", "plum4"))+
  scale_color_manual(values=c("seagreen", "plum4"))+
  #  scale_fill_manual(values=c("#193A3D", "#F03F3F"))+
  # scale_color_manual(values=c("#193A3D", "#F03F3F"))+
  # scale_fill_manual(values=c(rgb2hex(0.0, 153.0, 204.0),rgb2hex(0.0, 77, 102.0)))+
  # scale_color_manual(values=c(rgb2hex(0.0, 153.0, 204.0),rgb2hex(0.0, 77, 102.0)))+
  theme(legend.position="none")+
  # scale_y_continuous(limits=c(-60, 140))
  scale_y_continuous(limits=yax_limits)


plot4 <- dat2plot %>%
  filter(RDK_colorlum!="offset_to_bckgrd")%>%
  ggplot(., aes(y = modulation_evoked, fill = color_in_periphery, x = 1)) +
  geom_flat_violin(aes(fill = color_in_periphery),position = position_nudge(x = .1, y = 0), 
                   adjust = 1.3, trim = FALSE, alpha = 1, colour = NA)+
  geom_hline(yintercept=0, show.legend = FALSE) +
  # scale_fill_manual(values=c("#193A3D", "#F03F3F"))+
  # scale_color_manual(values=c("#193A3D", "#F03F3F"))+
  scale_fill_manual(values=c("seagreen", "plum4"))+
  scale_color_manual(values=c("seagreen", "plum4"))+
  # scale_fill_manual(values=c(rgb2hex(0.0, 153.0, 204.0),rgb2hex(0.0, 77, 102.0)))+
  # scale_color_manual(values=c(rgb2hex(0.0, 153.0, 204.0),rgb2hex(0.0, 77, 102.0)))+
  theme(axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank())+
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+
  # scale_y_continuous(limits=c(-60, 140))
  scale_y_continuous(limits=yax_limits)



# cowplot::plot_grid(plot1, plot2, plot3, ncol = 3,labels = "AUTO")
plotttitle <- ggdraw() + 
  draw_label("SSVEP amplitude modulation for attended color | evoked \nleft: offset; right: isoluminant",
             fontface='bold', size = 10)
plotplots <- ggarrange(plot1, plot2,plot3, plot4,ncol = 4,common.legend = TRUE,align = "h", widths=c(3,1,3,1))

savefig <- multi_panel_figure(columns = 1, rows = 1, panel_label_type = "none", width = 4.5, height = 3.5, unit = "in")
saveplot <- ggarrange(plotttitle, plotplots, nrow = 2, heights=c(0.2, 1))

savefig %<>%
  fill_panel(saveplot, column = 1, row = 1)
savefig
# save_multi_panel_figure(savefig, "figures/FFT_BeeSwarm_Mod_ALPHA_COL_34subs.eps")


# statistical test
dat2plot %>%
  ungroup()%>%
  group_by(RDK_colorlum)%>%
  nest() %>%
    mutate(
    stats = map(data, ~ rstatix::t_test(modulation_evoked ~ color_in_periphery, data = ., paired = TRUE, detailed = TRUE)),
    t_test_bf = map(data, ~ extractBF(ttestBF(formula = modulation_evoked ~ color_in_periphery, 
                                              data = ., iterations = num.iter, rscale = sqrt(2)/2))),
    meanval = map(data, ~ .x %>%
                    group_by(color_in_periphery) %>%
                    summarise(
                      mean_AMP_Mean = mean(modulation_evoked, na.rm = TRUE),
                      std_AMP_Mean = sd(modulation_evoked, na.rm = TRUE)
                    ) %>%
                    pivot_wider(names_from = color_in_periphery,
                                values_from = c(mean_AMP_Mean, std_AMP_Mean),
                                names_sep = "_")
    ),
    cohens_d = map(data, ~ rstatix::cohens_d(modulation_evoked ~ color_in_periphery, data = ., paired = FALSE))
  ) %>%
  unnest(cols = c(stats, t_test_bf, meanval))%>%
  mutate(CohensD = `statistic`/sqrt(df +1))%>%
  mutate(BF10 = bf, BF01 = 1/bf, 
         M_AMP_abs = mean_AMP_Mean_color_absent,
         SD_AMP_abs = std_AMP_Mean_color_absent,
         M_AMP_pres = mean_AMP_Mean_color_present,
         SD_AMP_pres = std_AMP_Mean_color_present,
         diff=estimate,
         t.value=statistic,p.value=p)%>%
  dplyr::select(M_AMP_abs, SD_AMP_abs, M_AMP_pres, SD_AMP_pres, diff, t.value, df, p.value, CohensD, BF10, BF01)%>%
  mutate(
    p.value = cell_spec(ifelse(round(p.value,4)<.001,"< .001",round(p.value,4)), 
                        color = ifelse(is.nan(p.value),"blue", ifelse(p.value < .05, "green", "red")),
                        bold = ifelse(is.nan(p.value),F, ifelse(p.value < .05, T,F)),
                        align = "center")
  ) %>%
  kbl(escape = F, digits = c(3,3,3,3,3,3,3,3,3), caption = c("central SSVEP | amplitude | pre-cue ")) %>%
  kable_styling("striped", full_width = T, bootstrap_options = c("striped", "hover", "condensed", "responsive",font_size = 8))
```

#### analysis VII

**CENTRAL POST-CUE MOD** ~ **LUMINANCE**

Do we see general post-cue modulations (irrespective of ATTENTION)?

```{r Stat central stimuli analysisVII, message=FALSE, warning=FALSE, include=TRUE,  fig.height=3, fig.width=4.5,}
dat2plot <- DataIn %>%
  filter(RDK_ispresented=="presented", RDK_position1=="center")%>%
  group_by(subjects, time, RDK_freq, RDK_colorlum,RDK_isattended)%>%
  summarise(amplitude_evoked=mean(amplitude_evoked), modulation_evoked=mean(modulation_evoked))%>%
  filter(time != '[1 2] ')


lmmmodel1 <- dat2plot%>%
  mixed(
    amplitude_evoked ~ RDK_isattended * time * RDK_colorlum + (1 | RDK_freq:subjects), # different intecepts modelled for  freq by sub combinations
    data = .,
    method = "KR",  # Kenward-Roger approximation for p-values
    return = "afex_aov"  # ensures compatibility with emmeans
  )

# display table anova effects
lmmmodel1 %>%
  anova()%>%
  tidy()%>%
  mutate(
    `p.value` = cell_spec(ifelse(round(`p.value`,4)<.001,"< .001",round(`p.value`,4)), 
                        color = ifelse(is.nan(`p.value`),"blue", ifelse(`p.value` < .05, "green", "red")),
                        bold = ifelse(is.nan(`p.value`),F, ifelse(`p.value` < .05, T,F)),
                        align = "center")
  ) %>%
  dplyr::select(term, `num.Df`, `den.Df`, `statistic`, `p.value`) %>%
  kbl(escape = F, digits = c(5,5,5,5,5,5,5,5,5), 
      caption = c("Mixed Model Anova Table (Type 3 tests, KR-method) | central SSVEP pre-cue amplitudes (normalized by mean amplitudes)")) %>%
  kable_styling("striped", full_width = T, bootstrap_options = c("striped", "hover", "condensed", "responsive",font_size = 8))

#display main effects via emmeans
# Main effect of RDK_isattended
emm_TIMEXLUM_lmm <- as.data.frame(emmeans(lmmmodel1, ~ time * RDK_colorlum))

# RDK_isattended plot
# add some more range to the y axis to allow for some more space for error bars and contrasts
y_range <- range(c(emm_TIMEXLUM_lmm$lower.CL, emm_TIMEXLUM_lmm$upper.CL))
y_range <- c(0, max(c(emm_TIMEXLUM_lmm$lower.CL, emm_TIMEXLUM_lmm$upper.CL)))
y_extension <- diff(y_range) * 0.20

saveplot <- ggplot(emm_TIMEXLUM_lmm, aes(x = time, y = emmean, fill = RDK_colorlum)) +
  geom_col(position = position_dodge(), width = 0.6) +
  geom_errorbar(aes(ymin = lower.CL, ymax = upper.CL), width = 0.6, position = position_dodge()) +
  labs(title = "non-sign. Interaction TIME X LUMINANCE",
       y = "Estimated Marginal Means (95% CI)", x = "time windows in s") +
  theme_light() +
  scale_fill_manual(values=c("steelblue2", "#F03F3F"))+
  scale_color_manual(values=c("steelblue2", "#F03F3F"))+
  scale_y_continuous(limits = c(y_range[1], y_range[2] + y_extension))
  # theme(axis.text.x = element_blank())

savefig <- multi_panel_figure(columns = 1, rows = 1, panel_label_type = "none", width = 4.5, height = 3, unit = "in")
savefig %<>%
  fill_panel(saveplot, column = 1, row = 1)
savefig
# save_multi_panel_figure(savefig, "figures/FFT_Center_MargMeans_ATTENTION.eps")


```



